---
title: "220124_frda_signaturesearch"
author: "Jennifer Fisher"
date: "1/24/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# START 
    Goal/Purpose of operations: 
    quick summary 
    
    Finished psedocode on: Date
    
    System which operations were done on: my laptop(on cheaha), lab mac etc... 
    
    GitHub Repo:
    
    Directory of operations: /path
    
    Scripts being edited for operations: filename(s)
    
    Data being used: description and location
    
    Papers and tools: deseq with paper 

# STEPS
### Set working directory 
### load in data

```{r}
library(recount3)
```

```{r}
human_projects<- available_projects()
```


```{r }
#SRP118922
recount3_rse_FRDA <- create_rse(human_projects[(human_projects$project == "SRP118922"),])
```

```{r}
metadata<- as.data.frame(colData(recount3_rse_FRDA))
```

```{r}
metadata$sra.sample_attributes
```

```{r}
metadata$sra.experiment_title
```

```{r}
metadata$sra.experiment_attributes
```
```{r}
hist(metadata$recount_qc.aligned_reads..chry)
```

```{r}
metadata_v2 <- cbind(metadata$rail_id, metadata$external_id, metadata$sra.sample_title)
```

```{r}
#write.csv(metadata_v2, "~/data/FRDA_metadata_recount_Study_info.csv")
```
added more info from https://cob.silverchair-cdn.com/cob/content_public/journal/dmm/10/11/10.1242_dmm.030536/5/dmm030536supp.pdf?Expires=1644405857&Signature=VE~up6~W89~N0bN23Rc9shD12MS2I6gWSlttEyXMFl~q1e3LbvKye3qCfvVYL2pmM8vAxAlFiz2Rj8~b4Pa0aYRot08IYNWmAnTNb6CFAfjtH2wcA6oJMBD2lOEeVJmNlcwSQ7QzbJlZm79tsjxrz8~38hW1auyVDWVK0wtEdmOn8bGpCyqTwWgh~m05Y5pbILJX3RbcFyg4mLsZ0~1PzTxeHhX9rmlf8KANRaDnfUdN3TaLx3f35OonqpOKN1qRj3uw8WukssEHh1qP~dWoS77Ccd~9wl8VLN42nwNCj6jXD8fE-CMxBVsMmEJHNO61EJx07rnBIfbf5~AKPYNsAw__&Key-Pair-Id=APKAIE5G5CRDK6RD3PGA

```{r}
metadata_v3 <- read.csv("~/data/FRDA_metadata_recount_Study_info.csv")
```




### Analysis
quick PCA 
```{r}
counts_FRDA<- assay(recount3_rse_FRDA)
```

```{r}
library(DESeq2)
vst_table <- vst(as.matrix(counts_FRDA))
vst_table_df <- t(vst_table)
pca.FRDA <- prcomp(vst_table_df)
```

```{r}
summary(pca.FRDA )
```

plot disease vs normal 

```{r}
tumor_norm <- ifelse(metadata_v3$disease == "control", "black", "red")
plot(pca.FRDA$x[, 1], pca.FRDA$x[, 2], pch = 20, col = tumor_norm  , main = "PCA of GBM", xlab = "PC1 (13.94%)", ylab = "PC2 (12.52%)", cex.axis = "1.5", cex.lab = "1.5")
legend("topleft", legend = c("FRDA", "normal"), pch = 21, pt.bg = c("red", "black"), col = "black")
```

```{r}
tumor_norm <- ifelse(metadata_v3$sex == "F", "black", "red")
plot(pca.FRDA$x[, 1], pca.FRDA$x[, 2], pch = 20, col = tumor_norm  , main = "PCA of GBM", xlab = "PC1 (13.94%)", ylab = "PC2 (12.52%)", cex.axis = "1.5", cex.lab = "1.5")
legend("topleft", legend = c("Male", "Female"), pch = 21, pt.bg = c("red", "black"), col = "black")
```

```{r}
PC1_samples <- metadata_v3[pca.FRDA$x[,1]> 40,]
PC1_na_samples <- metadata_v3[pca.FRDA$x[,1] < 40,]
```

```{r}
PC1_samples
```

```{r}
PC1_na_samples
```

nothing is standing out as a reason for the large spread beside FRDA which is expected 

DESEq2 (make into a function )
```{r}

  #count-matrix with just counts
  #metadata
  #dds <- DESeqDataSetFromMatrix(countData = GLUT_COUNTS2,
                         #     colData = colD,
                             # design= ~ batch + group)
deseq2_function <- function(dds, file_name, condition,  B, A){
  #dds deseq2 object
  #condition b-TUMOR a-CONTROL 
  set.seed(101)
  dds <- DESeq(dds)
  #resultsNames(dds) # lists the coefficients
  dds_res <- results(dds, c(condition,B,A))
  res_df <- as.data.frame(dds_res)
  #head(EV_GLUT_res_df_ENS)
  file_name <- paste0("~/output/deseq2_frda/",file_name, sep="")
  write.table(res_df, file=file_name, sep=",", row.names =TRUE)
  return(res_df)
}
```

```{r}
dds <- DESeqDataSetFromMatrix(countData = counts_FRDA,
                             colData = metadata_v3,
                              design= ~ disease)

dds_results<- deseq2_function(dds, "deseq2_frda_disease.csv","disease" ,"FRDA", "control")
```

```{r}
dds_results_df<- as.data.frame(dds_results)
```

```{r}
identical(rownames(dds_results_df), recount3_rse_FRDA@rowRanges$gene_id)
```

```{r}
dds_results_mx <- as.matrix(dds_results_df)
```


```{r}
rownames(dds_results_mx)<- recount3_rse_FRDA@rowRanges$gene_name
```



```{r}
dds_results_mx<- dds_results_mx[complete.cases(dds_results_mx),]
```

```{r}
dds_results_mx_sig <- dds_results_mx[dds_results_mx[,6] <0.05 & abs(dds_results_mx[,2]) > 1.5,]
```

#ENSG00000165060.11 FXN

```{r}
dds_results_df[rownames(dds_results_df) == "ENSG00000165060.11",]
```

add pathway analysis here 

Signaturerevesion FRDA genes


```{r}
db_path <- "/home/rstudio/data/lincs_2020.h5"
```

```{r}
upset<-rownames(dds_results_mx_sig)[dds_results_mx_sig[,2] >0]
downset<- rownames(dds_results_mx_sig)[dds_results_mx_sig[,2] <0]
```
```{r}
gene_info_LINCS<- read.table("~/data/LINCS_210914_LEVEL3/geneinfo_beta.txt", sep="\t", header=TRUE)
```

```{r}
upset_v2<- c()
for (i in 1:length(upset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    upset_v2[i]<- gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol]
  }else{
    upset_v2[i]<- NA
  }
  
}
names(upset_v2)<- upset
```

```{r}
downset_v2<- c()
for (i in 1:length(downset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    downset_v2[i]<- gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol]
  }else{
    downset_v2[i]<- NA
  }
  
}
names(downset_v2)<- downset
```

```{r}
downset_v2<- downset_v2[complete.cases(downset_v2)]
upset_v2<- upset_v2[complete.cases(upset_v2)]
```

```{r}
names(upset_v2)<- NULL
names(downset_v2)<- NULL
```


```{r}
set.seed(101)
qsig_lincs_deseq2_res <- qSig(query=list(upset=as.character(upset_v2), downset=as.character(downset_v2)), 
                   gess_method="LINCS", refdb=db_path)
```

```{r}
set.seed(101)
lincs_deseq_FRDA <- gess_lincs(qsig_lincs_deseq2_res, sortby="NCS", tau=FALSE, workers=1)
#result(lincs)
```
```{r}
lincs_deseq_FRDA <- result(lincs_deseq_FRDA)
```

```{r}
write.csv(lincs_deseq_FRDA , "~/output/deseq2_frda/lincs_deseq_gbm_FRDA.csv")
```

```{r}
lincs_deseq_FRDA_res_1HAE <- lincs_deseq_FRDA[lincs_deseq_FRDA$cell == "1HAE",]
```

```{r}
HAE1_taudf <- readRDS("~/data/1HAE_taudf.rds")
```


```{r}
tau_scores<- function(results_df, tau_score_df){
  #download the tau values 
  #scores <- readRDS(tau_score_file)
  results_df$id <- paste(results_df$pert, results_df$cell, results_df$type, sep= "__")
  #print(results_df$id)
  tau_list<- c()
  for (i in 1:nrow(results_df)){
    #print( results_df$id[i])
    #print(colnames(tau_score_df) == results_df$id[i])
    index <- grepl(results_df$pert[i], colnames(tau_score_df))
   scores <- tau_score_df[,colnames(tau_score_df) == results_df$id[i]]
   #print(scores)
      tmpsum <- sum( abs(scores) < abs(results_df$NCS[i]))
      secd<- (tmpsum/length(scores)) *100
      tau<- secd* sign( results_df$NCS[i])
      #print(tau)
   tau_list[i]<- tau
  }
  return(tau_list)
}
```

```{r}
lincs_deseq_FRDA_res_1HAE$jlf_tau <- tau_scores(lincs_deseq_FRDA_res_1HAE , HAE1_taudf)
```
#Tau (τ) that ranges from -100 to +100 


```{r}
lincs_deseq_FRDA_res_1HAE_top <- lincs_deseq_FRDA_res_1HAE[lincs_deseq_FRDA_res_1HAE$WTCS_FDR <0.05 & lincs_deseq_FRDA_res_1HAE$NCS <0,]
```
```{r}
lincs_deseq_FRDA_res_1HAE_top_order <- lincs_deseq_FRDA_res_1HAE_top[order(-lincs_deseq_FRDA_res_1HAE_top$NCS),]
lincs_deseq_FRDA_res_1HAE_top$pert <- factor(lincs_deseq_FRDA_res_1HAE_top$pert, levels = lincs_deseq_FRDA_res_1HAE_top_order$pert)
```

```{r}
library(ggplot2)
 library(viridis)
```

```{r}
p<-ggplot(data=lincs_deseq_FRDA_res_1HAE_top[1:30,] , aes(x=pert, y=NCS, fill=jlf_tau)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]")
ggsave("~/output/deseq2_frda/220208_ggplot_deseq2_tau_frda_candidates.pdf")
```
```{r}
lincs_deseq_frda_res_brain_cells <- lincs_deseq_FRDA[lincs_deseq_FRDA$cell %in% c("1HAE","NEU", "NPC") ,]
```

```{r}
lincs_deseq_frda_res_brain_cells_top <- lincs_deseq_frda_res_brain_cells[lincs_deseq_frda_res_brain_cells$WTCS_FDR <0.05 & lincs_deseq_frda_res_brain_cells$NCS <0,]
```

```{r}
lincs_deseq_frda_res_brain_cells_top_order <- lincs_deseq_frda_res_brain_cells_top [order(-lincs_deseq_frda_res_brain_cells_top$NCS),]
lincs_deseq_frda_res_brain_cells_top$pert <- factor(lincs_deseq_frda_res_brain_cells_top$pert, levels = unique(lincs_deseq_frda_res_brain_cells_top_order$pert))
```
```{r}
top_drugs<- unique(lincs_deseq_FRDA_res_1HAE_top_order$pert)
```

```{r}
lincs_deseq_frda_res_brain_cells_top_order_v2<- lincs_deseq_frda_res_brain_cells_top_order[lincs_deseq_frda_res_brain_cells_top_order$pert %in% top_drugs,]
```

```{r}
g.2<-ggplot(data= lincs_deseq_frda_res_brain_cells_top_order_v2, aes(x=pert, y=NCS, color=cell)) +
  geom_point(stat="identity", size = 3)
g.2 + coord_flip()
```

-79 is the cut off
```{r}
lincs_deseq_FRDA_res_1HAE_top_v2 <- lincs_deseq_FRDA_res_1HAE_top[ abs(lincs_deseq_FRDA_res_1HAE_top$jlf_tau) > 79,]
```

Fibro cell line
```{r}
hyperG_k_res <- dsea_hyperG(drugs = lincs_deseq_FRDA_res_1HAE_top_v2$pert, type = "KEGG", 
                            pvalueCutoff = 1, qvalueCutoff = 1, 
                            minGSSize = 10, maxGSSize = 2000)
hyperG_k_res_v2<- result(hyperG_k_res)
```

```{r}
write.csv(hyperG_k_res_v2, file= "~/output/deseq2_frda/220127_SR_LINCS_FDRA_fibro_cell_drug_pathway_RES.csv" )
```

```{r}
#false discovery rate
hyperG_k_res_v2$logqvalue<- -log(hyperG_k_res_v2$qvalue)
```

```{r}
hyperG_k_res_v2$Description<- factor(hyperG_k_res_v2$Description, levels= hyperG_k_res_v2$Description)
```

```{r}
gbm.2<-ggplot(data=hyperG_k_res_v2[1:30,] , aes(x=Description, y=Count, fill=logqvalue )) +
  geom_bar(stat="identity")
gbm.2 + coord_flip() + ylab("Number of Drugs") + xlab("KEGG Pathways") +labs(fill = "-log(q-value)")
```

latent variable analysis 
  with singature reversion 
  and pathway of drug
normalize count data by tpm
```{r}
Counts_to_tpm <- function(counts, featureLength) {
  # Ensure valid arguments.
  stopifnot(length(featureLength) == nrow(counts))
  # Compute effective lengths of features in each library.
  effLen <- featureLength
  # Process one column at a time.
  tpm <- do.call(cbind, lapply(1:ncol(counts), function(i) {
    rate = log(counts[,i]) - log(effLen)
    denom = log(sum(exp(rate)))
    exp(rate - denom + log(1e6))
  }))
  # Copy the row and column names from the original matrix.
  colnames(tpm) <- colnames(counts)
  rownames(tpm) <- rownames(counts)
  return(tpm)
}
```

```{r}
tpm_table<- Counts_to_tpm(counts_FRDA, recount3_rse_FRDA@rowRanges$bp_length)
```


```{r}
rownames(tpm_table)<- recount3_rse_FRDA@rowRanges$gene_name
```

```{r eval= FALSE}
source("~/script/plier_util.R")
source("~/script/test_LV_differences.R")
```

```{r}
#recount2_gtex_plier <- readRDS("~/data/recount2_gtex_plier.rds")
recount3_plier_frda <- readRDS("~/data/recount3/recount3_plier_frda.rds")
```

```{r eval= FALSE}
#There is a issue with handling genes with zero expression. Best thing to do is to remove the genes
test <- GetOrderedRowNorm(as.matrix(tpm_table),recount3_plier_frda  )
zeros<- rownames(test)[!complete.cases(test)]
tpm_table_v2<- tpm_table[!rownames(tpm_table) %in% zeros,]
```

create the b.matrix 
```{r eval= FALSE}
FRDA.b.matrix <- GetNewDataB(as.matrix(tpm_table_v2), recount3_plier_frda )
```

```{r eval=FALSE}
#saveRDS(FRDA.b.matrix, file= "~/output/TF_L_FRDA/FRDA_recount2_B_MATRIX.rds")
saveRDS(FRDA.b.matrix, file= "~/output/TF_L_FRDA/FRDA_recount3_B_MATRIX.rds")
```
```{r}
library(dplyr )
```

I dont need to use my own function. I can use the mutliplier function because of no covariates 
```{r}
#sampleinfo<- cbind(colnames(GBM.GTEx.b.matrix), as.character(all_metadata$status), as.character(all_metadata$database))
#colnames(sampleinfo) <- c("Sample", "Tumor","database")
#sampleinfo<- as.data.frame(sampleinfo)
#database<- all_metadata$database
#names(database)<- colnames(GBM.GTEx.b.matrix)
colnames(metadata_v3) <- c("X"  ,   "V1"     , "Sample",   "V3" ,     "disease")

LV_test_FRDA_BH <- LVTestWrapper(b.matrix=FRDA.b.matrix , sample.info.df= metadata_v3[,1:5], phenotype.col= "disease", , file.lead= "LV_TCGA_GTEX_T_vs_NT_recount3", plot.dir= "~/output/TF_L_FRDA/", results.dir= "~/output/TF_L_FRDA/", use.bonferroni= FALSE, sig.threshold = 0.05)
#LVTestWrapper()
```
```{r eval=FALSE}
#saveRDS(LV_test_FRDA_BH, file= "~/output/TF_L_FRDA/FRDA_recount2_limma_res.rds")
saveRDS(LV_test_FRDA_BH, file= "~/output/TF_L_FRDA/FRDA_recount3_limma_res.rds")
```

```{r eval=FALSE}
saveRDS(metadata_v3 , file= "~/output/TF_L_FRDA/FRDA_metadata.rds")
```

```{r eval= FALSE}
sig_LVs <- LV_test_FRDA_BH$limma[LV_test_FRDA_BH$limma$adj.P.Val < 0.05,]
```

```{r}
hist(LV_test_FRDA_BH$limma$logFC)
```
.1

```{r}
FRDA_limma_res_sig <- LV_test_FRDA_BH$limma[LV_test_FRDA_BH$limma$adj.P.Val <0.05 & abs(LV_test_FRDA_BH$limma$logFC)> 0.03,]
```

```{r}
FRDA_limma_res_sig$LV
```


```{r}
sig_Z_mt <- recount3_plier_frda$Z[,c(4, 9, 19, 23, 30, 38, 62, 171, 191, 237,310,315)]
colnames(sig_Z_mt) <- FRDA_limma_res_sig$LV
```

```{r}
sig_Z_mt[rownames(sig_Z_mt) == "FXN",]
```
top 100 
```{r}
topgene_1 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,1])][1:35]
topgene_2 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,2])][1:35]
topgene_3 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,3])][1:35]
topgene_4 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,4])][1:35]
topgene_5 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,5])][1:35]
topgene_6 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,6])][1:35]
topgene_7 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,7])][1:35]
topgene_8 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,8])][1:35]
topgene_9 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,9])][1:35]
topgene_10 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,10])][1:35]
topgene_11 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,11])][1:35]
topgene_12 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,12])][1:35]
```

```{r}
topgenes<- unique(c(topgene_1, topgene_2,topgene_3, topgene_4, topgene_5, topgene_6, topgene_7, topgene_8, topgene_9, topgene_10, topgene_11, topgene_12 ))
```
#25- 297
#30-353
#35- 409
#40-466

```{r}
dds_results_mx <- as.matrix(read.csv("~/output/deseq2_frda/deseq2_frda_disease.csv"))
```

```{r}
rownames(dds_results_mx)<- recount3_rse_FRDA@rowRanges$gene_name
```


```{r}
lv_genes_deseq_filtered <- as.data.frame(dds_results_mx[rownames(dds_results_mx) %in% topgenes,])
```

```{r}
uplist<- rownames(lv_genes_deseq_filtered)[lv_genes_deseq_filtered$log2FoldChange > 0]
downlist<- rownames(lv_genes_deseq_filtered)[lv_genes_deseq_filtered$log2FoldChange < 0 ]
```

```{r}
upset<- uplist
upset_v2<- c()
for (i in 1:length(upset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    upset_v2[i]<- gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol]
  }else{
    upset_v2[i]<- NA
  }
  
}
names(upset_v2)<- upset
```

```{r}
downset<- downlist
downset_v2<- c()
for (i in 1:length(downset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    downset_v2[i]<- gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol]
  }else{
    downset_v2[i]<- NA
  }
  
}
names(downset_v2)<- downset
```

```{r}
downset_v2<- downset_v2[complete.cases(downset_v2)]
upset_v2<- upset_v2[complete.cases(upset_v2)]
```

```{r}
names(upset_v2)<- NULL
names(downset_v2)<- NULL
```


```{r}
set.seed(101)
qsig_lincs_transfer_res <- qSig(query=list(upset=as.character(upset_v2), downset=as.character(downset_v2)), 
                   gess_method="LINCS", refdb=db_path)
```

```{r}
set.seed(101)
lincs_transfer_frda <- gess_lincs(qsig_lincs_transfer_res, sortby="NCS", tau=FALSE, workers=1)
#result(lincs)
```

```{r}
lincs_transfer_frda_res <- result(lincs_transfer_frda)
```


```{r}
write.csv(lincs_transfer_frda_res , file= "~/output/TF_L_FRDA/220208_SR_LINCS_FRDA_TRL_RES.csv" )
```


```{r}
lincs_transfer_frda_res_1HAE <- lincs_transfer_frda_res[lincs_transfer_frda_res$cell == "1HAE",]
```

```{r}
lincs_transfer_frda_res_1HAE$jlf_tau <- tau_scores(lincs_transfer_frda_res_1HAE, HAE1_taudf)
```

```{r}
write.csv(lincs_transfer_frda_res_1HAE , file= "~/output/TF_L_FRDA/220208_lincs_transfer_frda_res_1HAE_tau.csv" )
```

```{r}
lincs_transfer_frda_res_1HAE_top <- lincs_transfer_frda_res_1HAE[lincs_transfer_frda_res_1HAE$WTCS_FDR <0.05 & lincs_transfer_frda_res_1HAE$NCS <0,]
```
```{r}
lincs_transfer_frda_res_1HAE_top_order <- lincs_transfer_frda_res_1HAE_top[order(-lincs_transfer_frda_res_1HAE_top$NCS),]
lincs_transfer_frda_res_1HAE_top$pert <- factor(lincs_transfer_frda_res_1HAE_top$pert, levels = lincs_transfer_frda_res_1HAE_top_order$pert)
```


```{r}
#p.2<-ggplot(data=lincs_transfer_frda_res_1HAE_top_order[1:30,] , aes(x=pert, y=NCS)) +
 # geom_bar(stat="identity")
#p.2 + coord_flip()

p<-ggplot(data=lincs_transfer_frda_res_1HAE_top_order , aes(x=pert, y=NCS, fill=jlf_tau)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]")
ggsave("~/output/TF_L_FRDA/220208_ggplot_transfer_learning_tau_frda_candidates.pdf")
```
```{r}
lincs_transfer_frda_res_1HAE_top_v2 <- lincs_transfer_frda_res_1HAE_top[ abs(lincs_transfer_frda_res_1HAE_top$jlf_tau) > 79,]
```

```{r}
hyperG_k_res <- dsea_hyperG(drugs =lincs_transfer_frda_res_1HAE_top_v2$pert, type = "KEGG", 
                            pvalueCutoff = 1, qvalueCutoff = 1, 
                            minGSSize = 10, maxGSSize = 2000)
hyperG_k_res_v2<- result(hyperG_k_res)
```

```{r}
write.csv(hyperG_k_res_v2, file= "~/output/TF_L_FRDA/220208_SR_LINCS_FRDA_tfl_cell_drug_pathway_RES.csv" )
```

```{r}
#false discovery rate
hyperG_k_res_v2$logqvalue<- -log(hyperG_k_res_v2$qvalue)
```

```{r}
hyperG_k_res_v2$Description<- factor(hyperG_k_res_v2$Description, levels= hyperG_k_res_v2$Description)
```

```{r}
gbm.2<-ggplot(data=hyperG_k_res_v2[1:30,] , aes(x=Description, y=Count, fill=logqvalue )) +
  geom_bar(stat="identity")
gbm.2 + coord_flip() + ylab("Number of Drugs") + xlab("KEGG Pathways") +labs(fill = "-log(q-value)")
ggsave("~/output/TF_L_FRDA/220208_ggplot_transfer_learning_tau_frda_candidates_kegg_pathways.pdf")
```

```{r}
hyperG_k_res_v2[hyperG_k_res_v2$ID == "hsa04071",]
```

```{r}
as.character(hyperG_k_res_v2[hyperG_k_res_v2$ID == "hsa04071",8])
```

```{r}
hyperG_go_res <- dsea_hyperG(drugs =lincs_transfer_frda_res_1HAE_top_v2$pert, type = "GO", 
                            pvalueCutoff = 1, qvalueCutoff = 1, 
                            minGSSize = 10, maxGSSize = 2000)
hyperG_go_res_v2<- result(hyperG_go_res)
```


```{r}
write.csv(hyperG_go_res_v2, file= "~/output/TF_L_FRDA/220208_SR_LINCS_FRDA_tfl_cell_drug_go_pathways_RES.csv" )
```

Compare DESeq genes and Lv genes
```{r}
dds_results_df <- as.data.frame(dds_results_mx)
upset<-rownames(dds_results_df)[dds_results_df$log2FoldChange >0]
downset<- rownames(dds_results_df)[dds_results_df$log2FoldChange < 0]

uplist_lv<- rownames(lv_genes_deseq_filtered)[lv_genes_deseq_filtered$log2FoldChange > 0]
downlist_lv<- rownames(lv_genes_deseq_filtered)[lv_genes_deseq_filtered$log2FoldChange < 0 ]
```

```{r}
length(setdiff(upset, uplist_lv)) #13929
length(setdiff( uplist_lv,upset)) #0
```

```{r}
length(setdiff(downset, downlist_lv)) #11434
length(setdiff( downlist_lv,downset)) #60
```

```{r}
length(intersect(upset, uplist_lv))
length(intersect(downset, downlist_lv))
```


### Save Data
### Save Figures
    
# END
    Location of final scripts:
    
    Location of data produced:
    
    Dates when operations were done:
    
## Versions
```{r}
sessionInfo()
```
