---
title: "220302_GBM_drug_report"
author: "Jennifer Fisher"
date: "3/2/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description of analysis 
I will use a dimension reduction method, Pathway-Level Information Extractor (PLIER), to decompose transcript per million (TPM) normalized gene expression profiles from Recount3 into latent variables4,64.  A unique feature of this dimension reduction approach is its penalty for latent variables to reflect annotated pathways4,64. These learned latent variables from over 300,000 human RNA-seq samples from Recount3 will be transferred to disease (GBM IDH-wild type) and control TPM normalized gene expression profiles by matrix multiplication (MultiPLIER)4. To determine the Disease assoicaated Signatures (ie., Latent Variable), I will conduct a differential latent variable analysis via linear regression models (limma)65.  This is a GI1 cell line was used in this analysis.  For transfer learning signature reversion, I will create a gene list with the genes that contribute the most to the DAS (i.e., have the highest weights in the linear gene expression equation) for GBM. Then, I will calculate the gene expression fold change between disease and control to determine if the genes are up or down-regulated in the disease. I will use these up and down-regulated genes as inputs in the gene expression signature reversion method. The LINCS’s signature reversion (SignatureSearch), finds drug candidates with a gene expression perturbation profile (i.e., LINCS, 1,131 cell lines and 41,847 drugs) inverse to the disease profile (i.e., the up -and down-regulated DAGs determined by Aim 1A)32. I will filter drug candidates based on false discovery rates to correct for multiple hypothesis testing and Tau values to identify drugs that are uniquely inverse to the disease signature67. Then, I will rank drug candidates by the bi-directional weighted Kolmogorov-Smirnov statistic, which determines how similar are the disease and drug profiles67.

# Abstract Figure 

# START 

    System which operations were done on: my laptop(on cheaha), lab mac etc... 
    
    GitHub Repo:
    
    Docker Containter: 
    
    Directory of operations: /path
    
    Scripts being edited for operations: filename(s)
    
    Data being used: description and location
    
    Papers and tools: 
    
# Results 

```{r}
fda_marketing_status <- read.delim("~/data/drugsatfda20220302/MarketingStatus.txt")
```

```{r}
frda_product_info <- read.delim("~/data/drugsatfda20220302/Products.txt")
```

```{r}
fda_marketing_status$ID<- paste(fda_marketing_status$ApplNo, fda_marketing_status$ProductNo, sep= "_")
```

```{r}
frda_product_info$ID<- paste(frda_product_info$ApplNo, frda_product_info$ProductNo, sep= "_")
```

```{r}
info <- frda_product_info[frda_product_info$ID == fda_marketing_status$ID[1], 3:9]
for (i in 2:nrow(fda_marketing_status)){
  info_v2 <- frda_product_info[frda_product_info$ID == fda_marketing_status$ID[i], 3:9]
  info <- rbind(info, info_v2)
}
```

```{r}
info$ID[duplicated(info$ID)]
```
remove one 
```{r}
fda_product_info_v2 <- info[- 27986, ]
```

```{r}
fda_product_info_v2$market_status<- rep(NA, nrow(fda_product_info_v2))
for( i in 1:nrow(fda_product_info_v2)){
  fda_product_info_v2$market_status[i]<- fda_marketing_status$MarketingStatusID[ fda_marketing_status$ID == fda_product_info_v2$ID[i]]
}
```
```{r}
fda_marketing_status$ID[duplicated(fda_marketing_status$ID)]
```

```{r}
fda_product_info_v2$market_status_v2 <- ifelse(fda_product_info_v2$market_status == 1, "Prescription", ifelse(fda_product_info_v2$market_status == 2, "Over-the-Counter",  ifelse(fda_product_info_v2$market_status == 3, "Discontinued", "None (Tentative Approval")))
```

```{r}
write.table(fda_product_info_v2,file = "~/data/fda_product_info_df.csv" )
```


```{r}
repurposing_hub_table<- read.delim("~/data/Repurposing_Hub_export.txt")
```

```{r}
FDA_CT_table<- read.csv("~/data/SearchResults.csv")
```

```{r}
fda_approved_LINCS <- repurposing_hub_table$Name[repurposing_hub_table$Phase == "Launched"]
```

```{r}
lincs_deseq_gbm_res_GI1_top <- read.csv("~/output/TF_L_GBM/220207_lincs_transfer_gbm_res_GI1_tau.csv")
```

```{r}
lincs_deseq_gbm_res_GI1_top_order <- lincs_deseq_gbm_res_GI1_top[order(-lincs_deseq_gbm_res_GI1_top$NCS),]
lincs_deseq_gbm_res_GI1_top$pert <- factor(lincs_deseq_gbm_res_GI1_top$pert, levels = lincs_deseq_gbm_res_GI1_top_order$pert)
```

```{r}
lincs_deseq_gbm_res_GI1_top_approved<- lincs_deseq_gbm_res_GI1_top[lincs_deseq_gbm_res_GI1_top$pert %in% fda_approved_LINCS | lincs_deseq_gbm_res_GI1_top$pert== "rucaparib",]
```
  
```{r}
lincs_deseq_gbm_res_GI1_top_approved_tau <-  lincs_deseq_gbm_res_GI1_top_approved[lincs_deseq_gbm_res_GI1_top_approved$jlf_tau < -80  ,]
```

```{r}
library(ggplot2)
library(viridis)
```

```{r}
p<-ggplot(data=lincs_deseq_gbm_res_GI1_top_approved_tau , aes(x=pert, y=NCS, fill=jlf_tau)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]")
ggsave("~/output/TF_L_GBM/220210_ggplot_transfer_tau_gbm_approved_candidates.pdf")
```



```{r}
name<- c()
moa <- c()
targets <- c()
status<- c()
GBM_CT <- c()
NCS <- c()
WTCS_Pval <- c()
Tau<- c()
for (i in 1:nrow(lincs_deseq_gbm_res_GI1_top)){
  name[i] <- as.character(lincs_deseq_gbm_res_GI1_top$pert[i])
  if (lincs_deseq_gbm_res_GI1_top$pert[i] %in% repurposing_hub_table$Name){
    moa[i] <- repurposing_hub_table$MOA[ repurposing_hub_table$Name == lincs_deseq_gbm_res_GI1_top$pert[i]]
    targets[i] <- repurposing_hub_table$Target[ repurposing_hub_table$Name == lincs_deseq_gbm_res_GI1_top$pert[i]]
    status[i] <- repurposing_hub_table$Phase[ repurposing_hub_table$Name == lincs_deseq_gbm_res_GI1_top$pert[i]]
  }else{
    moa[i] <- NA
    targets[i] <- NA
    status[i] <- NA
  }
  
  NCS[i] <- lincs_deseq_gbm_res_GI1_top$NCS[ lincs_deseq_gbm_res_GI1_top$pert== lincs_deseq_gbm_res_GI1_top$pert[i]]
  WTCS_Pval[i] <-  lincs_deseq_gbm_res_GI1_top$WTCS_Pval[ lincs_deseq_gbm_res_GI1_top$pert== lincs_deseq_gbm_res_GI1_top$pert[i]]
  Tau[i] <-  lincs_deseq_gbm_res_GI1_top$jlf_tau[ lincs_deseq_gbm_res_GI1_top$pert== lincs_deseq_gbm_res_GI1_top$pert[i]]
  
  res <- grep( lincs_deseq_gbm_res_GI1_top$pert[i], FDA_CT_table$Interventions, ignore.case=TRUE )
  GBM_CT[i] <- length(res) >0 
}

info_table <- as.data.frame(cbind(name, moa, targets, status, GBM_CT, NCS, WTCS_Pval,Tau ))
```

#cut off -80
```{r}
info_table_v2<- info_table[as.numeric(info_table$Tau) <= -80,]
```


```{r}
table(info_table_v2$status)
```

```{r}
table(info_table_v2$GBM_CT)
```
 looking at using Drug Bank information 
 
note that the database was created by .... 

```{r}
library(RSQLite)
library(DBI)
```
#https://github.com/yduan004/drugbankR/blob/master/R/dbxml_handle.R
```{r}
dbxml2df <- function(xmlfile, version) {
    myxml <- xmlParse(file=xmlfile) 
    rootnode <- xmlRoot(myxml)
    rootsize <- xmlSize(rootnode)
    mycol <- c("drugbank-id", "name", "description", "cas-number", "unii", 
	       "state", "groups", "general-references", "synthesis-reference",
	       "indication", "pharmacodynamics", "mechanism-of-action", "toxicity", 
	       "metabolism", "absorption", "half-life", "protein-binding",
	       "route-of-elimination", "volume-of-distribution", "clearance",
	       "classification", "salts", "synonyms", "products", "international-brands",
	       "mixtures", "packagers", "manufacturers", "prices", "categories",
	       "affected-organisms", "dosages", "atc-codes", "ahfs-codes", "pdb-entries",
	       "fda-label", "msds", "patents", "food-interactions", "drug-interactions",
	       "sequences", "experimental-properties", "external-identifiers", "external-links",
	       "pathways", "reactions", "snp-effects", "snp-adverse-drug-reactions", "targets",
	       "enzymes", "carriers", "transporters", "average-mass", "monoisotopic-mass", 
	       "calculated-properties")
    ## (b) Extract corresponding data in loop and inject into preformatted data.frame 
    message("Extracting data for column names. This may take 20 minutes.")
    df <- as.data.frame(matrix(NA, nrow=rootsize, ncol=length(mycol), dimnames=list(1:rootsize, mycol)))
    for(i in 1:rootsize) {
        tmp <- xmlToDataFrame(rootnode[i], stringsAsFactors = FALSE, collectNames = FALSE)
        v <- as.character(tmp[1,]); names(v) <- colnames(tmp)
        df[i,] <- v[mycol]
    }
    message("Successfully convert DrugBank database (xml file) into dataframe.")
    return(df)
}
```


```{r}
#drug_bank<- dbxml2df("~/data/full database.xml", "5.1.8")
```
 
```{r}
#saveRDS(drug_bank, "~/data/drug_bank_1_5_8_df.RDS")
```
 
```{r}
drug_bank <- readRDS("~/data/drug_bank_1_5_8_df.RDS")
```
 
 
```{r}
colnames(drug_bank)
```

```{r}
drug_bank_v2 <- drug_bank[drug_bank$name %in% info_table_v2$name ,]
```
```{r}
drug_bank_v3 <- drug_bank[tolower(drug_bank$name) %in% info_table_v2$name,]
```

Capivasertib

```{r}
drug_bank_v5 <- drug_bank[drug_bank$name == "Capivasertib" ,]
```

```{r}
drug_bank_gbm_candidates <- rbind(drug_bank_v2, drug_bank_v3, drug_bank_v5)
```

```{r}
#write.table(drug_bank_gbm_candidates, "~/output/TF_L_GBM/220303_drug_canidate_info_drug_bank_1_5_8.csv", sep="@")
```

```{r}
#write.csv2(info_table_v2, "~/output/TF_L_GBM/220303_drug_canidate_LINCS_repurposing_hub.csv")
```


#fda DATABASE

```{r}
info_table_v2
```

```{r}
library(recount3)
library(SummarizedExperiment)
```

```{r }
human_projects<- available_projects()
```

```{r }
#SRP118922
recount3_rse_GBM <- create_rse(human_projects[(human_projects$project == "GBM"),])
```
tcgabiolinks download done by Avery williams 
```{r}
load("/home/rstudio/data/TCGA_GBM_GeneExpression_TCGABIOlinks.rda")
```

```{r}
metadata_gbm<- colData(data)
```

```{r}
 table(metadata_gbm$paper_IDH.status)
```

```{r}
#all primary tumors 
 metadata_gbm$sample_type[ metadata_gbm$paper_IDH.status == "WT"]
```


141 wildtype GBM. mutant IDH are no longer gbm 
```{r}
IDS <- metadata_gbm$barcode[ metadata_gbm$paper_IDH.status == "WT"]
IDS<- IDS[!is.na(IDS)]
#inculde the five nromal samples 
nt<- metadata_gbm$barcode[ metadata_gbm$sample_type == "Solid Tissue Normal"]
IDS<- c(IDS, nt)
```

```{r}
recount_metadata<- colData(recount3_rse_GBM)
recount_metadata<- as.data.frame(recount_metadata)
```

```{r}
recount_1ds<- rownames(recount_metadata)[recount_metadata$tcga.tcga_barcode %in% IDS]
```

```{r}
recount3_count_GBM <- as.data.frame(assay(recount3_rse_GBM))
```

```{r}
recount3_count_GBM<- recount3_count_GBM[,colnames(recount3_count_GBM) %in% recount_1ds]
```

```{r}
#SRP118922
recount3_rse_BRIAN <- create_rse(human_projects[(human_projects$project == "BRAIN"),])
```

```{r}
recount3_count_brain<- assay(recount3_rse_BRIAN)
recount3_count_brain <- as.data.frame(recount3_count_brain)
```

```{r}
#order the tcga data to match recount3 order
recount3_ids <- colnames(recount3_count_GBM)
recount_metadata_sub <- recount_metadata[rownames(recount_metadata) %in% recount3_ids,]
identical(rownames(recount_metadata_sub),recount3_ids)
ids <- recount_metadata_sub$tcga.tcga_barcode 

nam <- 
status<- c()
subtype<- c()
sex<- c()
for (i in 1:length(ids)){
  
nam[i]<- ids[i]
#create tumor/normal col
status[i] <-metadata_gbm$sample_type[metadata_gbm$barcode == ids[i]]
#create subtype col
subtype[i] <-as.character(metadata_gbm$paper_Transcriptome.Subtype[metadata_gbm$barcode == ids[i]])
subtype[i]<- ifelse(is.na(subtype[i]), "NA", subtype[i])
#create sex col 
sex[i]<- metadata_gbm$gender[metadata_gbm$barcode == ids[i]]
}
#create database col
database <- rep("TCGA", 146)
#create metadata 
tcga_gbm_metadata<- as.data.frame(cbind(nam, database, status, subtype, sex))
rownames(tcga_gbm_metadata)<- recount3_ids
tcga_gbm_metadata[1:5,]
```

```{r}
#order the metadata to match recount3 order
metadata_gtex<- as.data.frame(colData(recount3_rse_BRIAN))

#create sex col 
identical (rownames(metadata_gtex), colnames( recount3_count_brain))
nam<- metadata_gtex$external_id
sex<- ifelse(metadata_gtex$gtex.sex == 1, "male", "female")
#create database col
database<- rep ("GTEx",2931 )
#create normal col
status<- rep ("Solid Tissue Normal", 2931)
#create subtype col
subtype<- rep("NA", 2931)
#create metadata 
gtex_metadata<- as.data.frame(cbind(nam, database, status, subtype, sex))
rownames(gtex_metadata)<- rownames(metadata_gtex)
#combine count and metadata
gtex_metadata[1:5,]
```


```{r}
all_metadata <- rbind(tcga_gbm_metadata, gtex_metadata)
rownames(all_metadata)<- c(rownames(tcga_gbm_metadata), rownames(gtex_metadata))
count_table<- cbind(recount3_count_GBM, recount3_count_brain)
```

```{r}
identical(rownames(all_metadata), colnames(count_table))
```

normalize count data by tpm
```{r}
Counts_to_tpm <- function(counts, featureLength) {
  # Ensure valid arguments.
  stopifnot(length(featureLength) == nrow(counts))
  # Compute effective lengths of features in each library.
  effLen <- featureLength
  # Process one column at a time.
  tpm <- do.call(cbind, lapply(1:ncol(counts), function(i) {
    rate = log(counts[,i]) - log(effLen)
    denom = log(sum(exp(rate)))
    exp(rate - denom + log(1e6))
  }))
  # Copy the row and column names from the original matrix.
  colnames(tpm) <- colnames(counts)
  rownames(tpm) <- rownames(counts)
  return(tpm)
}
```


```{r}
gene_info <- as.data.frame(recount3_rse_BRIAN@rowRanges)
```
check to make sure things line up 
```{r}
identical(gene_info$gene_id, rownames(count_table))
```

```{r}
tpm_table<- Counts_to_tpm(count_table, gene_info$bp_length)
```

```{r}
rownames(tpm_table)<- gene_info$gene_name
```

```{r}
tpm_df <- as.data.frame(tpm_table)
```


```{r}
tpm_df[1:5,1:5]
```

```{r}
deseq_results <- read.csv("~/output/deseq2_gbm/Deseq2_gbm_normal_gtx_res.csv", sep=",")
```

```{r}
gene_info$gene_name[1]
identical(gene_info$gene_id, rownames(deseq_results))
```

```{r}
deseq_results$Symbol <- gene_info$gene_name
```


## Overview
table with name moa targets approved clinical trials of NCS and p-avalue and Tau value 

pie chart of moa, targets, aprpoved/phases, clinical trial


diflunisal 
look at the Gene expression of targets
prostanoid receptor antagonist
NSAID used to treat mild to moderate pain, inflammation, osteoarthritis, and rheumatoid arthritis. 
https://go.drugbank.com/drugs/DB00861
Blood Brain Barrier	+	0.8047
several drug interactions (but not with Tmz)

PTGS1, PTGS2
```{r}
library(dplyr)
library(tidyr)
```

```{r}
tpm_sub <- tpm_df[rownames(tpm_df) %in% c("PTGS1", "PTGS2"),]
tpm_sub$genes<- rownames(tpm_sub)
tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
tpm_sub_v2$type <- rep(all_metadata$status, 2)
```

```{r}
deseq_sub <-  deseq_results[ deseq_results$Symbol %in% c("PTGS1", "PTGS2"),]
stat_table <- deseq_sub[,c(7,6)]
stat_table$group1 <- rep("Primary Tumor" , 2)
stat_table$group2 <- rep("Solid Tissue Normal" , 2)
stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "Not Significant")
#stat_table$padj <- 

colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
```

```{r}
library(ggpubr)
```

```{r}
name<- "diflunisal"
ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) +
  geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "p = {padj}", y.position= 205) + labs(title=name,x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
```
PTGS1 deseq2 adjpvalue 0.001813387
PTGS2 WAS NOT SIGNFICANT

```{r}
library(signatureSearch)
library(HDF5Array)
se <- SummarizedExperiment(HDF5Array("~/data/lincs_2020.h5", name="assay"))
```

```{r}
rownames(se) <- HDF5Array("~/data/lincs_2020.h5", name="rownames")
colnames(se) <- HDF5Array("~/data/lincs_2020.h5", name="colnames")
```

```{r}
se_asssay<- assay(se)
```

```{r}
sub <- se_asssay[,grep("diflunisal__GI1__trt_cp", colnames(se))]
up <- sub[sub >= 2  ]
up<- names(up[order(-up)])
down<- sub[ sub <= -2 ]
down <- names(down[order(down)])
```

```{r}
library(gprofiler2)
```

```{r}
downset_pathway_results <- gost(query = down, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
downset_pathway_results<- downset_pathway_results$result
```

```{r}
upset_pathway_results <- gost(query = up, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
upset_pathway_results<- upset_pathway_results$result
```

```{r}
pathway_results<- rbind(upset_pathway_results, downset_pathway_results)
```
```{r}
pathway_results$set<- c(rep("Up", nrow(upset_pathway_results)), rep("Down", nrow(downset_pathway_results)))
```

```{r}
ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value))+geom_tile()+scale_fill_viridis(direction=-1)+theme_classic()+ labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
```




```{r}
drug_analysis <- function(drug_name, target_list,  tpm_df, sample_vector, deseq_results, se, result_path){
  #drug target expression
  tpm_sub <- tpm_df[rownames(tpm_df) %in% target_list,]
  tpm_sub$genes<- rownames(tpm_sub)
  tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
  tpm_sub_v2$type <- rep(sample_vector, nrow(tpm_sub))
  name<- drug_name
  y_max<- max(tpm_sub_v2$tpm) +5
  
  
  deseq_sub <-  deseq_results[ deseq_results$Symbol %in% unique( tpm_sub$genes),]
  stat_table <- deseq_sub[,c(7,6)]
  stat_table$group1 <- rep("Primary Tumor" ,  nrow(tpm_sub))
  stat_table$group2 <- rep("Solid Tissue Normal" ,  nrow(tpm_sub))
  stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "")
  colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
  
  
  file_name<- paste0(result_path, "/", drug_name, "_drug_target_expression_deseq2_padj.png")
  
  ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) + geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "{padj}", y.position= y_max,  size = 3) + labs(title=name,x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
  ggsave(file_name, width = 20, height = 8)
  
  #pathway enrichment
  lincs_name<- paste0(drug_name, "__GI1__trt_cp")
  sub <- se_asssay[,grep(lincs_name, colnames(se))]
  up <- sub[sub >= 2  ]
  up<- names(up[order(-up)])
  down<- sub[ sub <= -2 ]
  down <- names(down[order(down)])
  
  downset_pathway_results <- gost(query = down, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  downset_pathway_results<- downset_pathway_results$result
  
  upset_pathway_results <- gost(query = up, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  upset_pathway_results<- upset_pathway_results$result
  
  pathway_results<- rbind(upset_pathway_results, downset_pathway_results)
  pathway_results$set<- c(rep("Up", nrow(upset_pathway_results)), rep("Down", nrow(downset_pathway_results)))
  file_name<- paste0(result_path, "/", drug_name, "_drug_pathways.csv")
  write.csv2(as.data.frame(pathway_results[,-14]), file_name )
  
  file_name<- paste0(result_path, "/", drug_name, "_drug_pathways.png")
  if(nrow(pathway_results)<50){
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value))+geom_tile()+scale_fill_viridis(direction=-1)+theme_classic()+ labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
    
  }else{
    pathway_results<- pathway_results[pathway_results$source %in% c("KEGG","REAC","GO:MF" ),]
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value)) + geom_tile()+ scale_fill_viridis(direction=-1)+ theme_classic() + labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
  }
  ggsave(file_name, width = 12, height = 14)
  
}
```


```{r}
drug_analysis("diflunisal", c("PTGS1", "PTGS2"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
```

```{r}
drug_analysis("tiagabine", "SLC6A1",  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")

drug_analysis("vemurafenib", c("BRAF", "RAF1"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
drug_analysis("saxagliptin", "DPP4",  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
drug_analysis("nifedipine", c("CACNA1C", "CACNA1D", "CACNA1F", "CACNA1H", "CACNA1S", "CACNA2D1", "CACNB2", "CALM1", "GLRA1", "GLRA3", "GLRB", "KCNA1", "KCNA5", "NR1I2", "TRPM3"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
drug_analysis("spironolactone", c("AR", "CACNA1A", "CACNA1B", "CACNA1C", "CACNA1D", "CACNA1F", "CACNA1G", "CACNA1H", "CACNA1I", "CACNA1S", "CACNA2D1", "CACNA2D2", "CACNA2D3", "CACNB1", "CACNB2", "CACNB3", "CACNB4", "CACNG1", "CYP11B2", "NR3C1", "NR3C2", "PGR", "SHBG"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
drug_analysis("icosapent", c("ACSL3", "ACSL4", "FADS1", "FFAR1", "PPARD", "PPARG", "PTGS1", "PTGS2", "SLC8A1", "TRPV1"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
drug_analysis("pamidronate", "FDPS",  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
```

```{r}
#"DRD1", "DRD2", "DRD3", "DRD4", "DRD5", 
drug_analysis("thioridazine", c("DRD1", "DRD2", "DRD3", "DRD5","HRH1", "HTR1A", "HTR2A", "HTR2C", "HTR6", "HTR7"),  tpm_df, all_metadata$status, deseq_results, se, "~/output/TF_L_GBM/220308_gbm_candidates_plots")
```

looking at ap-1 complex and e2f1 in gbm and diflunisal 
P-1 is a dimer of JUN (JUN, JUNB, and JUND) and FOS (FOS, FOSB, FOSL1/FRA1, and FOSL2/FRA2) families of leucine-zipper proteins
```{r}
tpm_sub <- tpm_df[rownames(tpm_df) %in% c("JUN"  ,  "FOSL1" , "FOS" ,   "JUNB" ,  "JUND" ,  "FOSB" ,  "FOSL2" , "NFATC2" ),]
tpm_sub$genes<- rownames(tpm_sub)
tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
tpm_sub_v2$type <- rep(all_metadata$status, 8)
```

```{r}
deseq_sub <-  deseq_results[ deseq_results$Symbol %in% c("JUN"  ,  "FOSL1" , "FOS" ,   "JUNB" ,  "JUND" ,  "FOSB" ,  "FOSL2" , "NFATC2"),]
stat_table <- deseq_sub[,c(7,6)]
stat_table$group1 <- rep("Primary Tumor" , 8)
stat_table$group2 <- rep("Solid Tissue Normal" , 8)
stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "Not Significant")
#stat_table$padj <- 

colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
```

```{r}
library(ggpubr)
```

```{r}
name<- "diflunisal AP-1 complex genes"
ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) +
  geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "p = {padj}", y.position= 4000) + labs(title=name,x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
```
```{r}
tpm_sub <- tpm_df[rownames(tpm_df) %in% "E2F1",]
tpm_sub$genes<- rownames(tpm_sub)
tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
tpm_sub_v2$type <- rep(all_metadata$status, 1)
```

```{r}
deseq_sub <-  deseq_results[ deseq_results$Symbol %in% "E2F1" ,]
stat_table <- deseq_sub[,c(7,6)]
stat_table$group1 <- rep("Primary Tumor" , 1)
stat_table$group2 <- rep("Solid Tissue Normal" , 1)
stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "Not Significant")
#stat_table$padj <- 

colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
```

```{r}
library(ggpubr)
```

```{r}
name<- "diflunisal E2F1"
ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) +
  geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "p = {padj}", y.position= 250) + labs(title=name,x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
```

```{r}
library(readr)
vemurafenib_drug_pathways <- read_delim("~/output/TF_L_GBM/220308_gbm_candidates_plots/vemurafenib_drug_pathways.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
```

```{r}
library("stringr") 
```


```{r}
pathway_results<- vemurafenib_drug_pathways[vemurafenib_drug_pathways$source %in% c("KEGG", "REAC"),]
pathway_results$p_value <- as.numeric(gsub(",", ".", pathway_results$p_value))
pathway_results<- pathway_results[order(pathway_results$p_value)[1:30],]
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value)) + geom_tile()+ scale_fill_viridis(direction=-1)+ theme_classic() + labs(title="vemurafenib",x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value") + theme(axis.text = element_text(size = 15))  
    #+ scale_y_discrete(labels = function(x) str_wrap(pathway_results$term_name, width = 20))
ggsave("~/output/TF_L_GBM/220308_gbm_candidates_plots/vemurafenib_kegg_reac_top30.png", width = 12, height = 14)
```
```{r}
lincs_deseq_gbm_res_GI1_top <- read.csv("~/output/TF_L_GBM/220207_lincs_transfer_gbm_res_GI1_tau.csv")
```

```{r}
lincs_deseq_gbm_res_GI1_top_approved_tau <-lincs_deseq_gbm_res_GI1_top[lincs_deseq_gbm_res_GI1_top$pert %in% c("fludarabine", "rucaparib", "diflunisal", "tiagabine","thioridazine", "vemurafenib", "vorinostat", "dasatinib", "saxagliptin", "nifedipine", "spironolactone", "lapatinib", "pentoxifylline", "icosapent", "pamidronate", "erlotinib") ,]
lincs_deseq_gbm_res_GI1_top_order <- lincs_deseq_gbm_res_GI1_top_approved_tau[order(-lincs_deseq_gbm_res_GI1_top_approved_tau$NCS),]
```


```{r}
lincs_deseq_gbm_res_GI1_top_order$pert <- factor(lincs_deseq_gbm_res_GI1_top_order$pert, levels =lincs_deseq_gbm_res_GI1_top_order$pert )
p<-ggplot(data=lincs_deseq_gbm_res_GI1_top_order, aes(x=pert, y=NCS, fill=jlf_tau)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]")
ggsave("~/output/TF_L_GBM/220210_ggplot_transfer_tau_gbm_approved_candidates_updated.png")
```

```{r}
tpm_sub <- tpm_df[rownames(tpm_df) %in% c("BRAF", "RAF1" ),]
tpm_sub$genes<- rownames(tpm_sub)
tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
tpm_sub_v2$type <- rep(all_metadata$status, 2)
```

```{r}
deseq_sub <-  deseq_results[ deseq_results$Symbol %in% c("BRAF", "RAF1" ),,]
stat_table <- deseq_sub[,c(7,6)]
stat_table$group1 <- rep("Primary Tumor" , 2)
stat_table$group2 <- rep("Solid Tissue Normal" , 2)
stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "Not Significant")
#stat_table$padj <- 

colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
```

```{r}
library(ggpubr)
```

```{r}
#name<- "diflunisal AP-1 complex genes"
ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) +
  geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "p = {padj}", y.position= 120) + labs(title="vemurafenib",x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
ggsave("~/output/TF_L_GBM/220308_gbm_candidates_plots/vemurafenib_update_drug_targets.png")
```




```{r}
tpm_sub <- tpm_df[rownames(tpm_df) %in% c("SREBF1","SREBF2"),]
tpm_sub$genes<- rownames(tpm_sub)
tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
tpm_sub_v2$type <- rep(all_metadata$status, 2)
```

```{r}
deseq_sub <-  deseq_results[ deseq_results$Symbol %in% c("SREBF1","SREBF2"),]
stat_table <- deseq_sub[,c(7,6)]
stat_table$group1 <- rep("Primary Tumor" , 2)
stat_table$group2 <- rep("Solid Tissue Normal" , 2)
stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "Not Significant")
#stat_table$padj <- 

colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
```

```{r}
library(ggpubr)
```

```{r}
#name<- "SREBP genes"
ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) +
  geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "p = {padj}", y.position= 120) + labs(title="SREBP genes",x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
#ggsave("~/output/TF_L_GBM/220308_gbm_candidates_plots/vemurafenib_update_drug_targets.png")
```


16 total
9- not in clinical trials 
7- in clinical trials 
finish this test 
```{r}
fda_info <- read.table("~/data/fda_product_info_df.csv" )
```

```{r}
FDA_CT_table<- read.csv("~/data/SearchResults.csv")
```

```{r}
repurposing_hub_table<- read.delim("~/data/Repurposing_Hub_export.txt")
```

```{r}
library(HDF5Array)
lincs_samples<- HDF5Array("~/data/lincs_2020.h5", name="colnames")
lincs_samples<- as.vector(lincs_samples)
```

```{r}
lincs_samples_GBM <- lincs_samples[grep("GI1",lincs_samples )]
```

```{r}
library(stringr)
gbm_lincs_drugs <- as.vector(str_split(lincs_samples_GBM,  "__", simplify = TRUE)[,1])
```

```{r}
value <- c()
for (j in 1:685){
    res <- grep(gbm_lincs_drugs [j], FDA_CT_table$Interventions, ignore.case=TRUE )
    #if (res == TRUE){
    #  print(test[j])
    #}
    value[j]<- res
}
table(value)
```


```{r}
fraction<-c()
for (i in 1:10000){
  test <- gbm_lincs_drugs[ sample(x = 1:685,size = 16,replace = FALSE)]
  value <- c()
  
  #tables<- list()
  for (j in 1:16){
    res <- grep(test[j], FDA_CT_table$Interventions, ignore.case=TRUE )
    res <- length(res) >0 
    #if (res == TRUE){
    #  print(test[j])
    #}
    value[j]<- res
  }
  res_table <- cbind(test, value)
  fraction[i]<- table(res_table[,2])["TRUE"]
  #tables[i]<- res_table
  
}
fraction <- ifelse(is.na(fraction), 0, fraction)
fraction_adj <- fraction/16
```



## Drug 1

table with info 

Target expression in normal and tumor tissue (volian plot and table )

pathway analysis of preturbed pathways 
up 
down 

Drugbank info in hyperlink 

Clinical/Literature infromation 

Adverse events info 

PRISM info (table and graph)

### Save Data
### Save Figures
    
# END
    Location of final scripts:
    
    Location of data produced:
    
    Dates when operations were done:
    
## Versions
```{r}
sessionInfo()
```
