---
title: "220503_PRISM_top_candidates_plotting"
author: "Jennifer Fisher"
date: "5/3/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# START 
    Goal/Purpose of operations: 
    The DepMap/PRISM’s primary and secondary pooled drug screens were used to help evaluate if a candidate could be a suitable candidate (if that drug was tested). The primary screen calculated the median of log fold change median fluorescence intensity between replicates of a cell line treated with a drug. The PRISM study considered a cell line as sensitive to a treatment if the median-collapsed fold-change is less than 0.3. The secondary screen calculated the Area under the curve of the dose-response curve from a 4-parameter logistic curve. While the PRISM study did not provide a cut-off for sensitivity, lower AUC values were considered more sensitive, and we compared the AUC values of a drug candidate to the AUC of temozolomide, the standard treatment of GBM (~0.90).
    
    Finished psedocode on: 
    220503
    
    System which operations were done on:
    my laptop
    
    GitHub Repo:
    Transfer_Learning_R03
    
    Docker:
    rstudio_tf_dr_v3
    
    Directory of operations:
    /home - docker
    
    Scripts being edited for operations: 
    NA
    
    Data being used: 
    PRISM/DEPMAP data downloaded from depmap.org data explore tool. 220503- download data
    /output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/
    
    Papers and tools:
    NA

# STEPS
### Set working directory 
### load in data
```{r}
library(readr)
tiagabine_1_test<- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/tiagabine (BRDBRD-K60160658-003-11-2) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
colnames(tiagabine_1_test)[2]<- "logfoldchange"
colnames(tiagabine_1_test)[4]<- "cell_line"
```

### Analysis

```{r}
library(ggplot2)
library(cowplot)
```

```{r}
tiagabine_1_test_v2 <- tiagabine_1_test[order(tiagabine_1_test$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
tiagabine_1_test_v2$cell_line <- factor(tiagabine_1_test_v2$cell_line, levels= as.character(tiagabine_1_test_v2$cell_line))

ggplot(tiagabine_1_test_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal()
```

```{r}
ggplot(tiagabine_1_test_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal()
```


```{r}
p2 <- ggplot(tiagabine_1_test_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(tiagabine_1_test_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
tiagabine_secondary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/tiagabine AUC (PRISM Repurposing Secondary Screen)  tiagabine log2 fold change Drug sensitivity.csv")
colnames(tiagabine_secondary)[2]<- "logfoldchange"
colnames(tiagabine_secondary)[3]<- "AUC"
colnames(tiagabine_secondary)[5]<- "cell_line"
```

```{r}
ggplot(tiagabine_secondary, aes(x=logfoldchange, y= AUC))+geom_point()+ geom_text(
    label=tiagabine_secondary$cell_line, nudge_x = 0.005, nudge_y = 0.005, 
    check_overlap = T) + xlab("PRISM Primary Screen log(fold change)") + ylab("PRISM Secondary Screen AUC") + geom_vline(xintercept = 0.3) +geom_hline(yintercept = 0.9) +theme_minimal()
```

```{r}
vemurafenib_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/vemurafenib (BRDBRD-K56343971-001-10-6) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
colnames(vemurafenib_primary)[2]<- "logfoldchange"
colnames(vemurafenib_primary)[4]<- "cell_line"
```

```{r}
vemurafenib_primary_v2 <- vemurafenib_primary[order(vemurafenib_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
vemurafenib_primary_v2$cell_line <- factor(vemurafenib_primary_v2$cell_line, levels= as.character(vemurafenib_primary_v2$cell_line))

```

```{r}
p2 <- ggplot(vemurafenib_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(vemurafenib_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
vemurafenib_secondary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/vemurafenib (BRDBRD-K56343971-001-14-8) AUC Drug sensitivity AUC (PRISM Repurposing Secondary Screen) 19Q4 vs vemurafenib (BRDBRD-K56343971-001-10-6) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```

```{r}
colnames(vemurafenib_secondary)[2]<- "logfoldchange"
colnames(vemurafenib_secondary)[3]<- "AUC"
colnames(vemurafenib_secondary)[5]<- "cell_line"
```

```{r}
ggplot(vemurafenib_secondary, aes(x=logfoldchange, y= AUC))+geom_point()+ geom_text(
    label=vemurafenib_secondary$cell_line, nudge_x = 0.005, nudge_y = 0.005, 
    check_overlap = T) + xlab("PRISM Primary Screen log(fold change)") + ylab("PRISM Secondary Screen AUC") + geom_vline(xintercept = 0.3) +geom_hline(yintercept = 0.9) +theme_minimal()
```


```{r}
saxagliptin_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/saxagliptin (BRDBRD-A81513827-001-03-6) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```

```{r}
colnames(saxagliptin_primary)[2]<- "logfoldchange"
colnames(saxagliptin_primary)[4]<- "cell_line"
```

```{r}
saxagliptin_primary_v2 <- saxagliptin_primary[order(saxagliptin_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
saxagliptin_primary_v2$cell_line <- factor(saxagliptin_primary_v2$cell_line, levels= as.character(saxagliptin_primary_v2$cell_line))
```

```{r}
p2 <- ggplot(saxagliptin_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(saxagliptin_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
saxagliptin_secondary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/saxagliptin (BRDBRD-A81513827-001-03-6) AUC Drug sensitivity AUC (PRISM Repurposing Secondary Screen) 19Q4 vs saxagliptin (BRDBRD-A81513827-001-03-6) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(saxagliptin_secondary)[2]<- "logfoldchange"
colnames(saxagliptin_secondary)[3]<- "AUC"
colnames(saxagliptin_secondary)[5]<- "cell_line"
```

```{r}
ggplot(saxagliptin_secondary, aes(x=logfoldchange, y= AUC))+geom_point()+ geom_text(
    label=saxagliptin_secondary$cell_line, nudge_x = 0.005, nudge_y = 0.005, 
    check_overlap = T) + xlab("PRISM Primary Screen log(fold change)") + ylab("PRISM Secondary Screen AUC") + geom_vline(xintercept = 0.3) +geom_hline(yintercept = 0.9) +theme_minimal()
```
```{r}
spironolactone_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/spironolactone (BRDBRD-K90027355-001-13-3) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(spironolactone_primary)[2]<- "logfoldchange"
colnames(spironolactone_primary)[4]<- "cell_line"
```

```{r}
spironolactone_primary_v2 <- spironolactone_primary[order(spironolactone_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
spironolactone_primary_v2$cell_line <- factor(spironolactone_primary_v2$cell_line, levels= as.character(spironolactone_primary_v2$cell_line))
```

```{r}
p2 <- ggplot(spironolactone_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(spironolactone_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
spironolactone_secondary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/spironolactone (BRDBRD-K90027355-001-13-3) AUC Drug sensitivity AUC (PRISM Repurposing Secondary Screen) 19Q4 vs spironolactone (BRDBRD-K90027355-001-13-3) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(spironolactone_secondary)[2]<- "logfoldchange"
colnames(spironolactone_secondary)[3]<- "AUC"
colnames(spironolactone_secondary)[5]<- "cell_line"
```

```{r}
ggplot(spironolactone_secondary, aes(x=logfoldchange, y= AUC))+geom_point()+ geom_text(
    label=spironolactone_secondary$cell_line, nudge_x = 0.005, nudge_y = 0.005, 
    check_overlap = T) + xlab("PRISM Primary Screen log(fold change)") + ylab("PRISM Secondary Screen AUC") + geom_vline(xintercept = 0.3) +geom_hline(yintercept = 0.9) +theme_minimal()
```


```{r}
icosapent_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/icosapent (BRDBRD-K47192521-001-05-4) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(icosapent_primary )[2]<- "logfoldchange"
colnames(icosapent_primary )[4]<- "cell_line"
```

```{r}
icosapent_primary_v2 <- icosapent_primary [order(icosapent_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
icosapent_primary_v2$cell_line <- factor(icosapent_primary_v2$cell_line, levels= as.character(icosapent_primary_v2$cell_line))
```

```{r}
p2 <- ggplot(icosapent_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(icosapent_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```
```{r}
pamidronate_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/pamidronate (BRDBRD-K58513245-304-02-7) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(pamidronate_primary )[2]<- "logfoldchange"
colnames(pamidronate_primary )[4]<- "cell_line"
```

```{r}
pamidronate_primary_v2 <- pamidronate_primary[order(pamidronate_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
pamidronate_primary_v2$cell_line <- factor(pamidronate_primary_v2$cell_line, levels= as.character(pamidronate_primary_v2$cell_line))
```

```{r}
p2 <- ggplot(pamidronate_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(pamidronate_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

also need to plot tmz
```{r}
temozolomide_primary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/temozolomide (BRDBRD-K32107296-001-16-9) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```


```{r}
colnames(temozolomide_primary )[2]<- "logfoldchange"
colnames(temozolomide_primary)[4]<- "cell_line"
```

```{r}
temozolomide_primary_v2 <- temozolomide_primary[order(temozolomide_primary$logfoldchange),]
#tiagabine_1_test_v2$cell_line <- as.factor(tiagabine_1_test_v2$cell_line)
temozolomide_primary_v2$cell_line <- factor(temozolomide_primary_v2$cell_line, levels= as.character(temozolomide_primary_v2$cell_line))
```

```{r}
p2 <- ggplot(temozolomide_primary_v2, aes(x=logfoldchange, y= cell_line))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)
p1 <- ggplot(temozolomide_primary_v2, aes(x=logfoldchange)) + geom_density(alpha=.2, fill="#440154FF") +theme_minimal() +  theme(
    axis.title.x = element_blank(),
  )+ geom_vline(xintercept = 0.3)
plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
temozolomide_secondary <- read_csv("~/output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/temozolomide (BRDBRD-K32107296-001-16-9) AUC Drug sensitivity AUC (PRISM Repurposing Secondary Screen) 19Q4 vs temozolomide (BRDBRD-K32107296-001-16-9) log2 fold change Drug sensitivity (PRISM Repurposing Primary Screen) 19Q4.csv")
```

```{r}
colnames(temozolomide_secondary)[2]<- "logfoldchange"
colnames(temozolomide_secondary)[3]<- "AUC"
colnames(temozolomide_secondary)[5]<- "cell_line"
```

```{r}
ggplot(temozolomide_secondary, aes(x=logfoldchange, y= AUC))+geom_point()+ geom_text(
    label=temozolomide_secondary$cell_line, nudge_x = 0.00008, nudge_y = 0.00008, 
    check_overlap = T) + xlab("PRISM Primary Screen log(fold change)") + ylab("PRISM Secondary Screen AUC") + geom_vline(xintercept = 0.3) +theme_minimal()
```


PRISM primary result differences between the three methods

```{r}
library(readr)
primary_screen <- read_csv("~/data/DEPMAP_PRISM_220228/primary-screen-replicate-collapsed-logfold-change.csv")
sample_info <- read_csv("~/data/DEPMAP_PRISM_220228/sample_info.csv")
primary_screen_treatment_info <- read_csv("~/data/DEPMAP_PRISM_220228/primary-screen-replicate-collapsed-treatment-info.csv")
```
different order

```{r}
names_vector<- c()
for ( i in 2:ncol(primary_screen)){
  names_vector[i] <- primary_screen_treatment_info$name[ grep(colnames(primary_screen)[i], primary_screen_treatment_info$column_name)]
}
```

```{r}
good_id <- c()
for (i in 1:nrow(primary_screen)){
  good_id[i]<- nchar(primary_screen[i,1]) == 10 
}

```

```{r}
table(good_id)
```
```{r}
primary_screen_v2 <- primary_screen[good_id,]
```


```{r}
cell_vector<- c()
for ( i in 1:nrow(primary_screen_v2)){
  cell_vector[i] <-sample_info$stripped_cell_line_name[ grep(primary_screen_v2[i,1], sample_info$DepMap_ID)]
}
```

```{r}
primary_screen_v3<-  as.matrix(primary_screen_v2[,-1])
rownames(primary_screen_v3)<- cell_vector
```


```{r}
colnames(primary_screen_v3) <- names_vector[-1]
```

```{r}
test2<- as.data.frame.table(primary_screen_v3, responseName = "log_fold_change")
```


filter by gbm cell lines

```{r}
#table(sample_info$Subtype)
gbm_sample_info <- sample_info[sample_info$Subtype == "Glioblastoma",]
```


```{r}
primary_gbm_res <- test2[test2$Var1 %in% gbm_sample_info$stripped_cell_line_name,]
```


deseq2 only 
```{r}
primary_gbm_deseq2<- primary_gbm_res[primary_gbm_res$Var2 %in% c("suprofen", "trandolapril", "felbamate", "pralidoxime", "abiraterone", "ethotoin", "floxuridine", "vardenafil", "moxifloxacin", "nimodipine", "diltiazem"),]
```

```{r}
unique(primary_gbm_deseq2$Var2)
```

```{r}
primary_gbm_deseq2$method <- rep("DESeq2", nrow(primary_gbm_deseq2))
```

limma- only 
```{r}
primary_gbm_limma<- primary_gbm_res[primary_gbm_res$Var2 %in% c("lonafarnib", "dabrafenib", "apremilast", "rivastigmine", "crizotinib", "ixazomib", "imatinib", "sulfasalazine", "maraviroc", "amiodarone"),]
```

```{r}
unique(primary_gbm_limma$Var2)
```

```{r}
primary_gbm_limma$method <- rep("limma", nrow(primary_gbm_limma))
```

tf-only 
```{r}
primary_gbm_tfl<- primary_gbm_res[primary_gbm_res$Var2 %in% c("fludarabine", "tiagabine", "vemurafenib", "dasatinib", "nifedipine", "spironolactone", "lapatinib", "pentoxifylline", "erlotinib"),]
```
 nifedipine not in prism
```{r}
unique(primary_gbm_tfl$Var2)
```

```{r}
primary_gbm_tfl$method <- rep("Transfer Learning", nrow(primary_gbm_tfl))
```

deseq2/tf 
```{r}
primary_gbm_deseq2_tfl<- primary_gbm_res[primary_gbm_res$Var2 %in% c("diflunisal", "rucaparib"),]
```
 nifedipine not in prism
```{r}
unique(primary_gbm_deseq2_tfl$Var2)
```

```{r}
primary_gbm_deseq2_tfl$method <- rep("Transfer Learning and DESeq2", nrow(primary_gbm_deseq2_tfl))
```


limma/tf
```{r}
primary_gbm_limma_tfl<- primary_gbm_res[primary_gbm_res$Var2 %in% c("vorinostat", "thioridazine", "saxagliptin", "icosapent"),]
```
 nifedipine not in prism
```{r}
unique(primary_gbm_limma_tfl$Var2)
```

```{r}
primary_gbm_limma_tfl$method <- rep("Transfer Learning and limma", nrow(primary_gbm_limma_tfl))
```

all 
```{r}
primary_gbm_all<- primary_gbm_res[primary_gbm_res$Var2 %in% c("pamidronate"),]
```
 nifedipine not in prism
```{r}
unique(primary_gbm_all$Var2)
```

```{r}
primary_gbm_all$method <- rep("ALL", nrow(primary_gbm_all))
```

TMZ
```{r}
primary_gbm_tmz<- primary_gbm_res[primary_gbm_res$Var2 %in% c("temozolomide"),]
```
 nifedipine not in prism
```{r}
unique(primary_gbm_tmz$Var2)
```

```{r}
primary_gbm_tmz$method <- rep("TMZ Treatment", nrow(primary_gbm_tmz))
```

```{r}
primary_gbm_candidates <- rbind(primary_gbm_deseq2, primary_gbm_limma, primary_gbm_tfl, primary_gbm_deseq2_tfl, primary_gbm_limma_tfl, primary_gbm_all, primary_gbm_tmz)
```

```{r}
library(ggplot2)
library(viridis)
```


```{r}
primary_gbm_candidates$Var2 <- factor(primary_gbm_candidates$Var2, levels=unique(primary_gbm_candidates$Var2))
ggplot(primary_gbm_candidates, aes(x=log_fold_change, y= Var2))+ geom_violin(aes(fill=method)) +geom_vline(xintercept = -1) +scale_fill_viridis_d()+ theme_minimal()
```

```{r}
primary_gbm_candidates_v2 <- rbind(primary_gbm_deseq2, primary_gbm_limma, primary_gbm_tfl,  primary_gbm_tmz)
```
```{r}
primary_gbm_candidates_v2$Var2 <- factor(primary_gbm_candidates_v2$Var2, levels=unique(primary_gbm_candidates_v2$Var2))
ggplot(primary_gbm_candidates_v2, aes(x=log_fold_change, y= Var2))+ geom_violin(aes(fill=method)) +theme_minimal()
```

look to see how many gbm cell lines are senstive
```{r}
primary_gbm_candidates$Sensitive <- primary_gbm_candidates$log_fold_change < 0.3
```

```{r}
table(primary_gbm_candidates$Sensitive)
```
```{r}
drug_fraction <- c()
drug_list <- as.vector(unique(primary_gbm_candidates$Var2))
for (i in 1:length(drug_list)){
  cells <- primary_gbm_candidates$Sensitive[primary_gbm_candidates$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
```

```{r}
hist(drug_fraction)
```

```{r}
drug_senstive_precentage <- data.frame(drug_fraction, drug_list)
```

```{r}
ggplot(drug_senstive_precentage, aes( drug_fraction, drug_list ))+ geom_point()
```

```{r}
deseq2<- c("suprofen", "trandolapril", "felbamate", "pralidoxime", "abiraterone", "ethotoin", "floxuridine", "vardenafil", "moxifloxacin", "nimodipine", "diltiazem")
limma<- c("lonafarnib", "dabrafenib", "apremilast", "rivastigmine", "crizotinib", "ixazomib", "imatinib", "sulfasalazine", "maraviroc", "amiodarone")
transfer_learning<- c("fludarabine", "tiagabine", "vemurafenib", "dasatinib", "nifedipine", "spironolactone", "lapatinib", "pentoxifylline", "erlotinib")
limma_transfer_learning<- c("vorinostat", "thioridazine", "saxagliptin", "icosapent")
deseq2_transfer_learning <- c("diflunisal", "rucaparib")

```

```{r}
drug_senstive_precentage$method<- ifelse(drug_senstive_precentage$drug_list %in% deseq2, "DESeq2", ifelse(
  drug_senstive_precentage$drug_list %in% limma, "limma", ifelse(
    drug_senstive_precentage$drug_list %in% transfer_learning, "Transfer Learning", ifelse(
      drug_senstive_precentage$drug_list %in% limma_transfer_learning, "limma and Transfer Learning", ifelse(
        drug_senstive_precentage$drug_list %in% deseq2_transfer_learning, "DESeq2 and Transfer Learning", ifelse(
         drug_senstive_precentage$drug_list == "pamidronate", "ALL", "temozolomide"
        )
      )
    )
  )
) )
```


```{r}
drug_senstive_precentage$drug_list<- factor(drug_senstive_precentage$drug_list,levels= drug_senstive_precentage$drug_list[order(drug_senstive_precentage$drug_fraction)])
ggplot(drug_senstive_precentage, aes( drug_fraction, drug_list, fill=method ))+ geom_bar(stat="identity")
```

```{r}
drug_senstive_precentage_v2 <- drug_senstive_precentage[! drug_senstive_precentage$drug_list == "temozolomide",]
ggplot(drug_senstive_precentage_v2, aes( drug_fraction, drug_list, fill=method ))+  geom_bar(stat="identity", color = "black")+ scale_fill_viridis_d()+ geom_vline(xintercept = 0.75)+  xlab("PRISM Primary Screen log(fold change)") + ylab("Drug Candidates (All Methods)")
```

```{r}
primary_gbm_res$Sensitive <- primary_gbm_res$log_fold_change < 0.3
drug_fraction <- c()
drug_list <- as.vector(unique(primary_gbm_res$Var2))
for (i in 1:length(drug_list)){
  cells <- primary_gbm_res$Sensitive[primary_gbm_res$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list)
```

```{r}
table(drug_senstive_precentage_all_drugs$drug_fraction >= 0.75)
```

```{r}
drug_senstive_precentage_all_drugs$tmz <-drug_senstive_precentage_all_drugs$drug_fraction >= 0.75
```

```{r}
drug_senstive_precentage_all_drugs<- drug_senstive_precentage_all_drugs[!drug_senstive_precentage_all_drugs$drug_list == "temozolomide",]
```



```{r}
drug_senstive_precentage_all_drugs_tfl<- drug_senstive_precentage_all_drugs[!drug_senstive_precentage_all_drugs$drug_list %in% c("fludarabine", "tiagabine", "vemurafenib", "dasatinib", "nifedipine", "spironolactone", "lapatinib", "pentoxifylline", "erlotinib", "vorinostat", "thioridazine", "saxagliptin", "icosapent","diflunisal", "rucaparib", "pamidronate"),]
number_of_drugs<- c()
for ( i in 1:10000){
  test3 <- table(drug_senstive_precentage_all_drugs_tfl$tmz[sample(1:nrow(drug_senstive_precentage_all_drugs_tfl), 15)])
  number_of_drugs[i]<- test3[names(test3) == TRUE]
}
```

```{r}
hist(number_of_drugs)
```

```{r}
t.test(mu=11, number_of_drugs)
```

```{r}

drug_senstive_precentage_all_drugs_limma <- drug_senstive_precentage_all_drugs[drug_senstive_precentage_all_drugs$drug_list %in%c("lonafarnib", "dabrafenib", "apremilast", "rivastigmine", "crizotinib", "ixazomib", "imatinib", "sulfasalazine", "maraviroc", "amiodarone", "vorinostat", "thioridazine", "saxagliptin", "icosapent", "pamidronate"),]

drug_senstive_precentage_all_drugs_deseq2 <- drug_senstive_precentage_all_drugs[drug_senstive_precentage_all_drugs$drug_list %in%c("suprofen", "trandolapril", "felbamate", "pralidoxime", "abiraterone", "ethotoin", "floxuridine", "vardenafil", "moxifloxacin", "nimodipine", "diltiazem", "diflunisal", "rucaparib", "pamidronate"),]

```


```{r}
number_of_drugs_v2 <- c()
for ( i in 1:10000){
  test3 <- table(drug_senstive_precentage_all_drugs_tfl$tmz[sample(1:nrow(drug_senstive_precentage_all_drugs_tfl), 14)])
  number_of_drugs_v2[i]<- test3[names(test3) == TRUE]
}
```

```{r}
hist(number_of_drugs_v2)
```

```{r}
t.test(mu=9, number_of_drugs_v2, alternative = "less")
```

```{r}
hist(drug_senstive_precentage_all_drugs$drug_fraction)
```



```{r}
drug_senstive_precentage$bi_method<- grepl("Transfer Learning",drug_senstive_precentage$method)
```

```{r}
ggplot(drug_senstive_precentage, aes( drug_fraction, drug_list, fill=bi_method ))+ geom_bar(stat="identity") +geom_vline(xintercept = 0.75)
```

```{r}
drug_senstive_precentage$bi_method<- grepl("DES",drug_senstive_precentage$method)
```

```{r}
ggplot(drug_senstive_precentage, aes( drug_fraction, drug_list, fill=bi_method ))+ geom_bar(stat="identity")
```

```{r}
drug_senstive_precentage$bi_method<- grepl("limma",drug_senstive_precentage$method)
```

```{r}
ggplot(drug_senstive_precentage, aes( drug_fraction, drug_list, fill=bi_method ))+ geom_bar(stat="identity") 
```

```{r}
drug_senstive_precentage$drug_list
```


### Save Data
### Save Figures
NA
    
# END
    Location of final scripts:
    /script
    
    Location of data produced:
    na
    
    Dates when operations were done:
    220503
    
## Versions
```{r}
sessionInfo()
```
