---
title: "220503_PRISM_top_candidates_plotting"
author: "Jennifer Fisher"
date: "5/3/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# START 
    Goal/Purpose of operations: 
    The DepMap/PRISM’s primary  pooled drug screens were used to help evaluate if a candidate could be a suitable candidate (if that drug was tested). The primary screen calculated the median of log fold change median fluorescence intensity between replicates of a cell line treated with a drug. The PRISM study considered a cell line as sensitive to a treatment if the median-collapsed fold-change is less than 0.3. 
    
    Finished psedocode on: 
    220503
    
    System which operations were done on:
    my laptop
    
    GitHub Repo:
    Transfer_Learning_R03
    
    Docker:
    rstudio_cancer_dr
    
    Directory of operations:
    /home - docker
    
    Scripts being edited for operations: 
    NA
    
    Data being used: 
    PRISM/DEPMAP data downloaded from depmap.org data explore tool. 220503- download data
    /output/TF_L_GBM/220503_PRISM_DEPMAP_candidate_data/
    
    Papers and tools:
    NA

# STEPS
### Set working directory 
### load in data

```{r}
primary_gbm_res <- read.csv(file= "~/output/220808_prism_gbm_candidates.csv" )
```

```{r}
library(readr)
cell_gbm_info<- read_csv("~/data/DEPMAP_PRISM_220228/cell-line-selector_gbm_top_ten.csv")
```

remove the odd names
```{r}
cell_gbm_info<- cell_gbm_info[, -c(1:3, 5)]
```

```{r}
library(tidyr)
```

```{r}
cell_gbm_info_longer <- pivot_longer(cell_gbm_info, c(2:12), names_to = "drug", values_to = "log2change")
```
removing the extra info in the drug stuff 
```{r}
cell_gbm_info_longer$drug <- sub(" .*", "", cell_gbm_info_longer$drug)
```
remove NAs from the logfold change data
```{r}
cell_gbm_info_longer_v2 <- cell_gbm_info_longer[ ! is.na(cell_gbm_info_longer$log2change),]
```

### Analysis

```{r}
library(ggplot2)
library(cowplot)
```
```{r}
library(viridis)
library(circlize)
library(ComplexHeatmap)
```


```{r}
p2 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, y= drug, color= drug))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) 

p1 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, fill= drug)) + geom_density(alpha=.5) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)

plot_grid(p1, p2, ncol = 1, align = "v")
```
```{r}
cell_gbm_info_longer_v2$tmz_cell<- ifelse(cell_gbm_info_longer_v2$displayName %in% c("A172", "GB1","KNS81", "SF295", "YH13", "YKG1"), "TMZ_RES", "TMZ_Sen")
```


```{r}
gbm_candidate_prism_plot_tmz <- function(cell_line_info, drug){
  
  cell_gbm_info_longer_v2<- cell_line_info[cell_line_info$drug %in% c(drug, "temozolomide"),]
    
  #cell_gbm_info_longer_v2$shape <- ifelse(cell_gbm_info_longer_v2$tmz_cell== "TMZ_RES", 19, 17)
  cell_gbm_info_longer_v2$tmz_cell<- factor(cell_gbm_info_longer_v2$tmz_cell, levels= c("TMZ_Sen", "TMZ_RES" ))
  p2 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, y= displayName, color= drug, shape= tmz_cell))+ geom_point(stat = "identity", size = 4) +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) + theme(text = element_text(size = 12,  face="bold"))

  p1 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, fill= drug)) + geom_density(alpha=.5) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3) + theme(text = element_text(size = 12,  face="bold"))

  plot_grid(p1+ scale_fill_manual( values=c("#440154FF","#228C8DFF")), p2+ scale_color_manual( values= c("#440154FF","#228C8DFF") ), ncol = 1, align = "v") 
}
```


```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "simvastatin")
```
```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "pamidronate")
```

```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "floxuridine")
```

```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "nimodipine")
```


```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "vardenafil")
```
```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "moxifloxacin")
```
```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "diltiazem")
```
```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "diflunisal")
```
```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "saxagliptin")
```

```{r}
gbm_candidate_prism_plot_tmz(cell_gbm_info_longer_v2, "icosapent")
```


want to determine if there is a difference between groups and drug repesonse

```{r}
#mgmt methylation
cell_gbm_info_longer_v2$MGMT_METH<-  ifelse(cell_gbm_info_longer_v2$`MGMT Methylation (1kb upstream TSS) MGMT_10_131264504_131265504` >0.5, "Hyper methylation (>0.5)", "Hypo methylation (=< 0.5)")

drugs<- unique(cell_gbm_info_longer_v2$drug)
mgmt<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$MGMT_METH),]
  #groups<- 
  test<- as.vector(as.data.frame(cell_line_info[,18]))
    x<- test[cell_line_info$MGMT_METH == "Hyper methylation (>0.5)",1]
    y<- test[!cell_line_info$MGMT_METH == "Hyper methylation (>0.5)",1]
    x<- as.numeric(unlist(x))
    y<- as.numeric(unlist(y))
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided") 
       mgmt[i]<- res$p.value
    }
}
```
```{r}
#egfr COPY NUMBER
cell_gbm_info_longer_v2$EGFR_copy <- ifelse(cell_gbm_info_longer_v2$`EGFR (ERBB1, ERBB) Copy Number 22Q2 Public` >2, "Copy Number > 2", "Copy Number =< 2")

egfr_amp<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$EGFR_copy ),]
  #groups<- 
  test<- as.vector(as.data.frame(cell_line_info[,18]))
    x<- test[cell_line_info$EGFR_copy  == "Copy Number > 2",1]
    y<- test[!cell_line_info$EGFR_copy  == "Copy Number > 2",1]
    x<- as.numeric(unlist(x))
    y<- as.numeric(unlist(y))
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided") 
       egfr_amp[i]<- res$p.value
    }else{
      print(i)
    }
    
}
#note most of the gbm cell lines have no egfr amplication
```

```{r}
#table(cell_gbm_info_longer_v2$Gender)
sex<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$Gender ),]
  #groups<- 
  test<- as.vector(as.data.frame(cell_line_info[,18]))
    x<- test[cell_line_info$Gender  == "Male",1]
    y<- test[!cell_line_info$Gender  == "Male",1]
    x<- as.numeric(unlist(x))
    y<- as.numeric(unlist(y))
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided") 
       sex[i]<- res$p.value
    }else{
      print(i)
    }
    
}
```

```{r}
#tmz non-senssitive cell lines (0.3=> logfoldchange in PRISM)
#A172
#GB1
#KNS81
#SF295
#YH13
#YKG1

cell_gbm_info_longer_v2$tmz_cell<- ifelse(cell_gbm_info_longer_v2$displayName %in% c("A172", "GB1","KNS81", "SF295", "YH13", "YKG1"), "TMZ_RES", "TMZ_Sen")

tmz<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$tmz_cell ),]
  #groups<- 
  test<- as.vector(as.data.frame(cell_line_info[,18]))
    x<- test[cell_line_info$tmz_cell  == "TMZ_RES",1]
    y<- test[!cell_line_info$tmz_cell  == "TMZ_RES",1]
    x<- as.numeric(unlist(x))
    y<- as.numeric(unlist(y))
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided") 
       tmz[i]<- res$p.value
    }else{
      print(i)
    }
    
}
```


```{r}
drugs<- unique(cell_gbm_info_longer_v2$drug)
index<- c(3,4,10,11,12)
test_res<- matrix(nrow= 11, ncol= 5)
for( i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  for(j in 1:5){
    test<- cell_line_info[,c(index[j], 18)]
    groups<- test[,1]== 1
    x<- test[groups,2]
    y<- test[!groups,2]
    x<- as.numeric(unlist(x))
    y<- as.numeric(unlist(y))
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided") 
      test_res[i,j]<- res$p.value
    }else{
      res<- NA
      test_res[i,j]<-res
    }
  }
} 
rownames(test_res)<- drugs
colnames(test_res)<- colnames(cell_gbm_info_longer_v2)[index]
test_res<- cbind(test_res, sex, tmz,  mgmt)
```

```{r}
test_res_filter_1<- test_res< 0.05
#p-value for the MGMT promotor
test_res_filter_2<- test_res< 0.16795666
```

```{r}
gbm_candidate_prism_plot_two_groups <- function(cell_line_info, drug, info_index, divider= 0, group1="Normal", group2= "Mutation" ){
  
  #index_col <- grepl(colnames(cell_line_info), info)
  cell_gbm_info_longer_v2<- cell_line_info[cell_line_info$drug == drug,]
  
  a <- ifelse(cell_gbm_info_longer_v2[,info_index] ==divider , 19, 17)
  cell_gbm_info_longer_v2$test <- ifelse(cell_gbm_info_longer_v2[,info_index] ==divider , group1, group2)
  #print(a)
  #nam <- colnames(cell_gbm_info_longer_v2)[info_index]
  #cell_gbm_info_longer_v2[,info_index]<- as.factor(cell_gbm_info_longer_v2[,info_index])
  #print(cell_gbm_info_longer_v2[,info_index])
  p2 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, y= displayName, color= test))+ geom_point(stat = "identity", shape = a, size = 4) +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) 
  #+ theme(axis.text.y = element_text( color = a))

  p1 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, fill= test)) + geom_density(alpha=.5) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)

  plot_grid(p1+ scale_fill_manual( values=c("#440154FF","#228C8DFF")), p2+ scale_color_manual( values= c("#440154FF","#228C8DFF") ), ncol = 1, align = "v")
  
}
```

```{r}
#pten pamidronate
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "pamidronate", 12 )
```

```{r}
#Sex
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "vardenafil", 14, divider= "Male", group1="Male", group2= "Female")
```

```{r}
cell_gbm_info_longer_v2<- cell_gbm_info_longer_v2[,c(1:18, 20,21, 19)]
```

different p-value threshold because of low poer. DO NOT TRUST THIS DATA
```{r}
#"EGFR_copy"
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "diflunisal", 21, divider= "TMZ_RES", group1="TMZ Resistant", group2= "TMZ Sensitive")
```
if they are reistant to tmz it looks reistant here. 

```{r}
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "icosapent", 21, divider= "TMZ_RES", group1="TMZ Resistant", group2= "TMZ Sensitive")
```




```{r}
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "floxuridine", 19, divider= "Hyper methylation (>0.5)", group1="Hyper methylation (>0.5)", group2= "Hypo methylation (=< 0.5)")
```


```{r}
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "moxifloxacin", 14, divider= "Male", group1="Male", group2= "Female")
```

```{r}
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "icosapent", 14, divider= "Male", group1="Male", group2= "Female")
```


```{r}
#pten 
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "moxifloxacin", 12 )
```


```{r}
#"TP53 (LFS1, p53) Mutation 22Q2 Public
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "pamidronate", 3 )
```


```{r}
#"TP53 (LFS1, p53) Mutation 22Q2 Public
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "floxuridine", 3 )
```

```{r}
#"RB1 (PPP1R130, RB, OSRC) Mutation 22Q2 Public" 
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "moxifloxacin", 10 )
```

```{r}
#"RB1 (PPP1R130, RB, OSRC) Mutation 22Q2 Public" 
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "moxifloxacin", 10 )
```

```{r}
#"MTOR (FRAP1, FLJ44809, RAPT1, RAFT1, FRAP, FRAP2) Mutation 22Q2 Public"   
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "moxifloxacin", 11 )
```

```{r}
#"MTOR (FRAP1, FLJ44809, RAPT1, RAFT1, FRAP, FRAP2) Mutation 22Q2 Public"   
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "pamidronate", 11 )
```
```{r}
#"MTOR (FRAP1, FLJ44809, RAPT1, RAFT1, FRAP, FRAP2) Mutation 22Q2 Public"   
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "temozolomide", 11 )
```

```{r}
#"MTOR (FRAP1, FLJ44809, RAPT1, RAFT1, FRAP, FRAP2) Mutation 22Q2 Public"   
gbm_candidate_prism_plot_two_groups(cell_gbm_info_longer_v2, "simvastatin", 11 )
```

linear regression stuff with methylation of MGMT and efgr amplication


```{r}
egfr_copy_p<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$`EGFR (ERBB1, ERBB) Copy Number 22Q2 Public` ),]
  #groups<- 
  test<- as.data.frame(cell_line_info[,c(5, 18)])
  res <- lm(log2change ~ `EGFR (ERBB1, ERBB) Copy Number 22Q2 Public`, test)
  egfr_copy_p[i]<- summary(res)$coefficients[,4][2] 
  
}
```


```{r}
mgmt_methy_p<- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug == drugs[i],]
  #test<- cell_line_info[,c(index[j], 18)]
  cell_line_info<- cell_line_info[!is.na(cell_line_info$`MGMT Methylation (1kb upstream TSS) MGMT_10_131264504_131265504` ),]
  #groups<- 
  test<- as.data.frame(cell_line_info[,c(2, 18)])
  res <- lm(log2change ~ `MGMT Methylation (1kb upstream TSS) MGMT_10_131264504_131265504`, test)
  mgmt_methy_p[i]<- summary(res)$coefficients[,4][2] 
  
}
```

```{r}
test_res <- cbind(test_res, egfr_copy_p, mgmt_methy_p)
```

```{r}
gbm_candidate_prism_plot_cont <- function(cell_line_info, drug, info_index, title ){
  
  #index_col <- grepl(colnames(cell_line_info), info)
  cell_gbm_info_longer_v2<- cell_line_info[cell_line_info$drug == drug,]


  nam <- colnames(cell_gbm_info_longer_v2)[info_index]
  #cell_gbm_info_longer_v2[,info_index]<- as.factor(cell_gbm_info_longer_v2[,info_index])
  #print(cell_gbm_info_longer_v2[,info_index])
  p2 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change, y= displayName, color= get(nam)))+ geom_point(stat = "identity", size= 4) +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3)+ labs(color=title) 
  #+ theme(axis.text.y = element_text( color = a))

  p1 <- ggplot(cell_gbm_info_longer_v2, aes(x=log2change)) + geom_density(alpha=.5) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)
  
  legend <- get_legend(p2)
  p2<- p2 + theme(legend.position='none')
  ggdraw(plot_grid(plot_grid(p1, p2, ncol=1, align='v'),
                 plot_grid(NULL, legend, ncol=1),
                 rel_widths=c(1, 0.2)))
  
}
```

```{r}
gbm_candidate_prism_plot_cont(cell_gbm_info_longer_v2, "moxifloxacin", 2, "MGMT Promoter Methylation(0-1)" )
```
```{r}
gbm_candidate_prism_plot_cont(cell_gbm_info_longer_v2, "floxuridine", 2, "MGMT Promoter Methylation(0-1)" )
```

```{r}
gbm_candidate_prism_plot_cont(cell_gbm_info_longer_v2, "floxuridine", 5, "EGFR Copy Number" )
```

```{r}
gbm_candidate_prism_plot_cont(cell_gbm_info_longer_v2, "moxifloxacin", 5, "EGFR Copy Number" )
```
```{r}
gbm_candidate_prism_plot_cont(cell_gbm_info_longer_v2, "nimodipine", 5, "EGFR Copy Number" )
```


change the tmz resistant test
compare the log2fold changes of the resistnat cells lines between drugs not within a drug. 
```{r}

cell_gbm_info_longer_v3<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$tmz_cell =="TMZ_RES", ]

tmz_v2 <- c()
for (i in 1:length(drugs)){
  cell_line_info<- cell_gbm_info_longer_v3[cell_gbm_info_longer_v3$drug %in% c(drugs[i], "temozolomide"),]
   #simvastain does have the A172 cell line so 
    # only keep cell lines with duplicated
  paired_cell_lines<- cell_line_info$displayName[duplicated(cell_line_info$displayName)]
  cell_line_info<- cell_line_info[cell_line_info$displayName %in% paired_cell_lines,]
  test<- as.vector(as.data.frame(cell_line_info[,17:18]))
  x<- test[test$drug  == drugs[i],2]
  y<- test[!test$drug ==  drugs[i],2]
  x<- as.numeric(unlist(x))
  y<- as.numeric(unlist(y))
   
    if(length(x) > 1 & length(y) > 1 ){
      res <- wilcox.test(x,y,alternative = "two.sided", paired = TRUE) 
       tmz_v2[i]<- res$p.value
    }else{
      print(i)
    }
    
}
```


```{r}
#replace the old tmz resistant p-values with the new p-values
colnames(test_res)
tmz_v2[1]<- 1 # for temzolomide
test_res[,7]<- tmz_v2
```



```{r}
#plot.data$stars <- cut(plot.data$p.value, breaks=c(-Inf, 0.001, 0.01, 0.05, Inf), label=c("***", "**", "*", "")) 
test_res_t <- t(test_res)
rownames(test_res_t)<- c("TP53 Mutation - Wilcox", "EGFR Mutation - Wilcox" , "RB1 Mutation - Wilcox", "MTOR Mutation - Wilcox", "PTEN Mutation - Wilcox", "Sex - Wilcox", "TMZ-Resistant - Wilcox Paired", "MGMT Promoter Methylation (high vs low) - Wilcox", "EGFR Copy Number - linear regression", "MGMT Promoter Methylation- linear regression"  )                                         
col_fun = colorRamp2(c(0,  1), c("blue", "white"))
Heatmap(test_res_t, nam= "p-value of biomarker and PRISM Drug Response", col = col_fun, column_names_rot = 45,
               clustering_distance_rows= "euclidean",
               clustering_distance_columns=  "euclidean",
               clustering_method_rows = "ward.D2" ,
               clustering_method_columns="ward.D2", 
        cell_fun = function(j, i, x, y, w, h, fill) {
        if(test_res_t[i, j] < 0.05) {
            grid.text("*", x, y)
        } else if(test_res_t[i, j] < 0.2) {
          grid.text("?", x, y)
      }})
```


top 5 

```{r}
cell_gbm_info_longer_v3<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug %in% c("pamidronate", "nimodipine", "moxifloxacin", "saxagliptin", "icosapent", "temozolomide"),]
```



```{r}
p2 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, y= drug, color= drug))+ geom_point(stat = "identity") +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) 

p1 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, fill= drug)) + geom_density(alpha=.2) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)

plot_grid(p1, p2, ncol = 1, align = "v")
```

```{r}
cell_gbm_info_longer_v3<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug %in% c("pamidronate", "nimodipine","temozolomide"),]
```



```{r}
cell_gbm_info_longer_v3$drug<- factor(cell_gbm_info_longer_v3$drug , levels= c("pamidronate", "temozolomide", "nimodipine"))
p2 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, y= displayName, color= drug))+ geom_point(stat = "identity", size= 4) +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) + theme(text = element_text(size = 20,  face="bold"))+ scale_color_manual(values = c("#F1605DFF" ,"gold","#721F81FF"))

p1 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, fill= drug)) + geom_density(alpha=.8) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)+ theme(text = element_text(size = 20,  face="bold")) + scale_fill_manual(values = c("#F1605DFF" ,"gold","#721F81FF"))

plot_grid(p1, p2, ncol = 1, align = "v")
```



```{r}
cell_gbm_info_longer_v3<- cell_gbm_info_longer_v2[cell_gbm_info_longer_v2$drug %in% c("saxagliptin", "icosapent","temozolomide"),]
```



```{r}
cell_gbm_info_longer_v3$drug<- factor(cell_gbm_info_longer_v3$drug , levels= c("saxagliptin", "temozolomide", "icosapent"))
p2 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, y= displayName, color= drug))+ geom_point(stat = "identity", size= 4) +theme_minimal() + xlab("PRISM Primary Screen log(fold change)") + ylab("GBM Cell Lines") + geom_vline(xintercept = 0.3) + theme(text = element_text(size = 20,  face="bold"))+ scale_color_brewer(palette = "Set2")

p1 <- ggplot(cell_gbm_info_longer_v3, aes(x=log2change, fill= drug)) + geom_density(alpha=.8) +theme_minimal() +  theme(
    axis.title.x = element_blank())+ geom_vline(xintercept = 0.3)+ theme(text = element_text(size = 20,  face="bold")) + scale_fill_brewer(palette = "Set2")

plot_grid(p1, p2, ncol = 1, align = "v")
```




make adjustment to the alluvial plot to plot with FDA approved or not 

download the compound info from LINCS
```{r}
source("/home/rstudio/script/functions_cancer_signature_reversion_JLF.R")
library(ggalluvial)
library(stringr)
library(matrixStats)
lincs_commpound_info <- read.delim("~/data/LINCS_210914_LEVEL3/compoundinfo_beta.txt")
```


gbm
```{r}
lincs_limma_gbm_res_GI1_fda_approved<- read_csv( "~/output/limma_gbm/220808_SR_LINCS_GBM_top_RES_all.csv")
lincs_deseq2_gbm_res_GI1_fda_approved <- read_csv( "~/output/deseq2_gbm/220928_SR_LINCS_GBM_DESEQ2_RES_all.csv")
lincs_tfl_gbm_res_GI1_fda_approved <- read_csv( "~/output/TF_L_GBM/220808_SR_LINCS_GBM_top_RES_all.csv")
```

```{r}
drug_moa_target_plotting_ct_info(lincs_tfl_gbm_res_GI1_fda_approved ,lincs_commpound_info=lincs_commpound_info, "TLF", "GBM", "~/output/candidate_moa_target_plots/221117" )

#for limma and deseq2 there is inverse in the color for the plots going to adjust here via !
lincs_limma_gbm_res_GI1_fda_approved$GBM_CT<- !lincs_limma_gbm_res_GI1_fda_approved$GBM_CT
drug_moa_target_plotting_ct_info(lincs_limma_gbm_res_GI1_fda_approved ,lincs_commpound_info=lincs_commpound_info, "limma", "GBM", "~/output/candidate_moa_target_plots/221117" )
lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT<- !lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT
drug_moa_target_plotting_ct_info(lincs_deseq2_gbm_res_GI1_fda_approved ,lincs_commpound_info=lincs_commpound_info, "deseq2", "GBM", "~/output/candidate_moa_target_plots/221117" )

#fix the logical after plotting
lincs_limma_gbm_res_GI1_fda_approved$GBM_CT<- !lincs_limma_gbm_res_GI1_fda_approved$GBM_CT
lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT<- !lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT
```
PRISM plotting

```{r}
prism_gbm_cell_lines <- read.csv("~/output/220808_prism_gbm_candidates.csv")
```

```{r}
non_fda_candidate_list<- c(lincs_tfl_gbm_res_GI1_fda_approved$pert[!lincs_tfl_gbm_res_GI1_fda_approved$clinical_trial_GBM], lincs_limma_gbm_res_GI1_fda_approved$pert[!lincs_limma_gbm_res_GI1_fda_approved$GBM_CT], lincs_deseq2_gbm_res_GI1_fda_approved$pert[!lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT])
non_fda_candidate_list<- unique(non_fda_candidate_list)
```


```{r }
primary_gbm_res_sub <-prism_gbm_cell_lines[ prism_gbm_cell_lines$Var2 %in% non_fda_candidate_list,]
#write.csv(primary_gbm_res_sub , file= "~/output/TF_L_GBM/220808_prism_tfl_candidates_gbm.csv" )
```



```{r }
drug_list <- as.vector(unique(primary_gbm_res_sub$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_gbm_res_sub$Sensitive[primary_gbm_res_sub$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)

drug_senstive_precentage_all_drugs$drug_list<- factor(drug_senstive_precentage_all_drugs$drug_list, levels= unique(drug_senstive_precentage_all_drugs$drug_list[order(drug_senstive_precentage_all_drugs$drug_fraction)]))
ggplot(drug_senstive_precentage_all_drugs, aes( drug_fraction, drug_list, fill= test ))+ geom_bar(stat="identity",  color= "black") + scale_fill_viridis_d() + ylab("Drug Candidates") + xlab("Fraction of Sensitive Cell Lines") +labs(fill = "75% of Cell line are Sensitive")
#ggsave("~/output/TF_L_GBM/220808_ggplot_TFL_candidates_prism_screen1_sensitive_cell_lines.png")
```

```{r}
  tfl_drugs1 <-lincs_tfl_gbm_res_GI1_fda_approved$pert[!lincs_tfl_gbm_res_GI1_fda_approved$clinical_trial_GBM] 
  deseq2_drugs1<- lincs_deseq2_gbm_res_GI1_fda_approved$pert[!lincs_deseq2_gbm_res_GI1_fda_approved$GBM_CT]
  limma_drugs1 <- lincs_limma_gbm_res_GI1_fda_approved$pert[!lincs_limma_gbm_res_GI1_fda_approved$GBM_CT]

  tfl_drugs <- grepl(paste(tfl_drugs1 ,collapse="|"), drug_senstive_precentage_all_drugs$drug_list) 
  deseq2_drugs<- grepl(paste(deseq2_drugs1,collapse="|"), drug_senstive_precentage_all_drugs$drug_list)
  limma_drugs <- grepl(paste(limma_drugs1 ,collapse="|"), drug_senstive_precentage_all_drugs$drug_list)
  
  #shared by all methods or two methods
  all_drugs <- tfl_drugs & deseq2_drugs & limma_drugs
  
  deseq_tfl <- tfl_drugs & deseq2_drugs 
  deseq_tfl<- ifelse(all_drugs ==TRUE, FALSE, deseq_tfl)
  
  deseq_limma <- limma_drugs & deseq2_drugs 
  deseq_limma <- ifelse(all_drugs ==TRUE, FALSE, deseq_limma )
  
  limma_tfl<- limma_drugs & tfl_drugs 
  limma_tfl <- ifelse(all_drugs ==TRUE, FALSE, limma_tfl )
  
  
  #only indivudal methods
  tfl<- setdiff(tfl_drugs1,  c(limma_drugs1, deseq2_drugs1) )
  tfl<- grepl(paste(tfl,collapse="|"), drug_senstive_precentage_all_drugs$drug_list)
  
  limma<- setdiff(limma_drugs1,  c(tfl_drugs1, deseq2_drugs1) )
  limma<- grepl(paste(limma,collapse="|"), drug_senstive_precentage_all_drugs$drug_list)
  
  deseq<- setdiff(deseq2_drugs1,  c(tfl_drugs1,limma_drugs1) )
  deseq<- grepl(paste(deseq,collapse="|"), drug_senstive_precentage_all_drugs$drug_list)
  
  
  #set groups for each node
  #this will match node color
  group <- rep(NA, length(tfl))
  group <- ifelse(tfl, "Transfer Learning", group)
  group <- ifelse(limma_tfl, "limma and Transfer Learning", group)
  group<- ifelse(limma, "limma", group)
  group<- ifelse(deseq_limma, "DESeq2 and limma", group)
  group<- ifelse(deseq, "DESeq2", group)
  group<- ifelse(deseq_tfl, "DESeq2 and Transfer Learning", group)
  group<- ifelse(all_drugs, "All Methods", group)
  
drug_senstive_precentage_all_drugs$method<- factor(group, levels= c("All Methods","DESeq2 and Transfer Learning",  "DESeq2","DESeq2 and limma", "limma", "limma and Transfer Learning", "Transfer Learning" ))

ggplot(drug_senstive_precentage_all_drugs, aes( drug_fraction, drug_list, fill= method ))+ geom_bar(stat="identity",  color= "black") + scale_fill_viridis_d() + ylab("Drug Candidates") + xlab("Fraction of Sensitive Cell Lines") +labs(fill = "Method(s)")  +scale_fill_manual(values=c("All Methods"="#FDE725FF","DESeq2 and Transfer Learning" ="#8FD744FF", "DESeq2"="#35B779FF", "DESeq2 and limma"= "#21908CFF", "limma"= "#31688EFF", "limma and Transfer Learning"= "#443A83FF", "Transfer Learning" = "#440154FF"))+ geom_vline(xintercept = 0.75, size= 5) + theme(text = element_text(size = 60,  face="bold"))
 ggsave("~/output/gbm_plots/221117_top_candidate_PRISM_plot.png", width = 49, height= 25) 
```



```{r}
gbm_drugs <- unique(c(lincs_limma_gbm_res_GI1_fda_approved$pert, lincs_deseq2_gbm_res_GI1_fda_approved$pert, lincs_tfl_gbm_res_GI1_fda_approved$pert))
```


```{r}
  limma_rank <-rep(NA, length(gbm_drugs))
  deseq2_rank<-rep(NA, length(gbm_drugs))
  tfl_rank<-rep(NA, length(gbm_drugs))
for (i in 1:length(gbm_drugs)){
  if(length(grep(gbm_drugs[i], lincs_limma_gbm_res_GI1_fda_approved$pert)) == 1){
    limma_rank[i] <-grep(gbm_drugs[i], lincs_limma_gbm_res_GI1_fda_approved$pert)
  }else{
    limma_rank[i] <- NA
  }
  if(length(grep(gbm_drugs[i], lincs_deseq2_gbm_res_GI1_fda_approved$pert)) == 1){
    deseq2_rank[i] <-grep(gbm_drugs[i], lincs_deseq2_gbm_res_GI1_fda_approved$pert)
  }else{
    deseq2_rank[i] <-NA
  }
  if( length(grep(gbm_drugs[i], lincs_tfl_gbm_res_GI1_fda_approved$pert)) == 1){
    tfl_rank[i] <-grep(gbm_drugs[i], lincs_tfl_gbm_res_GI1_fda_approved$pert)
  }else{
    tfl_rank[i] <-NA
  }
}

```

```{r}
method_ranks<- cbind(limma_rank, deseq2_rank, tfl_rank)
drug_ranks<- rowMedians(method_ranks,na.rm= TRUE)
```

```{r}
  tfl_drugs1 <-lincs_tfl_gbm_res_GI1_fda_approved$pert
  deseq2_drugs1<- lincs_deseq2_gbm_res_GI1_fda_approved$pert
  limma_drugs1 <- lincs_limma_gbm_res_GI1_fda_approved$pert

  tfl_drugs <- grepl(paste(tfl_drugs1 ,collapse="|"), gbm_drugs) 
  deseq2_drugs<- grepl(paste(deseq2_drugs1,collapse="|"), gbm_drugs)
  limma_drugs <- grepl(paste(limma_drugs1 ,collapse="|"), gbm_drugs)
  
  #shared by all methods or two methods
  all_drugs <- tfl_drugs & deseq2_drugs & limma_drugs
  
  deseq_tfl <- tfl_drugs & deseq2_drugs 
  deseq_tfl<- ifelse(all_drugs ==TRUE, FALSE, deseq_tfl)
  
  deseq_limma <- limma_drugs & deseq2_drugs 
  deseq_limma <- ifelse(all_drugs ==TRUE, FALSE, deseq_limma )
  
  limma_tfl<- limma_drugs & tfl_drugs 
  limma_tfl <- ifelse(all_drugs ==TRUE, FALSE, limma_tfl )
  
  
  #only indivudal methods
  tfl<- setdiff(tfl_drugs1,  c(limma_drugs1, deseq2_drugs1) )
  tfl<- grepl(paste(tfl,collapse="|"), gbm_drugs)
  
  limma<- setdiff(limma_drugs1,  c(tfl_drugs1, deseq2_drugs1) )
  limma<- grepl(paste(limma,collapse="|"), gbm_drugs)
  
  deseq<- setdiff(deseq2_drugs1,  c(tfl_drugs1,limma_drugs1) )
  deseq<- grepl(paste(deseq,collapse="|"), gbm_drugs)
  
  
  #set groups for each node
  #this will match node color
  group <- rep(NA, length(tfl))
  group <- ifelse(tfl, "Transfer Learning", group)
  group <- ifelse(limma_tfl, "limma and Transfer Learning", group)
  group<- ifelse(limma, "limma", group)
  group<- ifelse(deseq_limma, "DESeq2 and limma", group)
  group<- ifelse(deseq, "DESeq2", group)
  group<- ifelse(deseq_tfl, "DESeq2 and Transfer Learning", group)
  group<- ifelse(all_drugs, "All Methods", group)
  
```


```{r eval=FALSE}
clinical_trial_GBM <- read_csv("~/data/SearchResults.csv")
```

```{r}
all_cand<- data.frame(gbm_drugs, drug_ranks, group)
```

clinical_trial_check
```{r eval=FALSE}
all_cand$ct <- clinical_trial_check(as.character(all_cand$gbm_drugs), clinical_trial_GBM)
```


get targets
```{r}
colnames(lincs_deseq2_gbm_res_GI1_fda_approved)<- NULL
colnames(lincs_tfl_gbm_res_GI1_fda_approved)<- NULL
rownames(lincs_deseq2_gbm_res_GI1_fda_approved)<- NULL
rownames(lincs_tfl_gbm_res_GI1_fda_approved)<- NULL
all_gbm_drugs<- unlist(c(lincs_limma_gbm_res_GI1_fda_approved$pert, lincs_deseq2_gbm_res_GI1_fda_approved[,2], lincs_tfl_gbm_res_GI1_fda_approved[,2]))
gbm_drug_target<- unlist(c(lincs_limma_gbm_res_GI1_fda_approved[,14], lincs_deseq2_gbm_res_GI1_fda_approved[,14], lincs_tfl_gbm_res_GI1_fda_approved[,14]))

gbm_targets<- as.data.frame(cbind(all_gbm_drugs, gbm_drug_target))
```

```{r}
gbm_targets<- unique(gbm_targets)
```

```{r}
identical(gbm_targets$all_gbm_drugs, all_cand$gbm_drugs)
```


```{r}
all_cand$t_gn_sym<- gbm_targets$gbm_drug_target
```


```{r}
colnames(all_cand)[1]<- "pert"
```

```{r}
all_cand<- all_cand[order(all_cand$drug_ranks),]
```

```{r}
drug_moa_target_plotting_all_info(all_cand, lincs_commpound_info=lincs_commpound_info, "all", "gbm", file_path_header= "~/output/candidate_moa_target_plots/221128" )
```

update the target plots

```{r}
deseq_results <- read.csv("~/output/deseq2_gbm/220927_deseq2_gbm_normal_gtx_res.csv", sep=",")
```

```{r}
tpm_df <- readRDS("~/output/recount3_gbm_gtex_tpm_df.rds")
metadata <- readRDS("~/output/recount3_gbm_gtex_metadata.rds")
```

```{r}
library(recount3)
human_projects<- available_projects()
#get a random project data
test<- create_rse(human_projects[(human_projects$project == "SRP118922"),])
gene_info <- test@rowRanges
rm(test)
```
```{r}
dim(as.data.frame(gene_info))
```

```{r}
identical(gene_info$gene_id, rownames(deseq_results))
```

```{r}
deseq_results$Symbol<- gene_info$gene_name
```

```{r}
library(ggpubr)
drug_target_analysis( "pamidronate" , c("FDPS"), as.data.frame(tpm_df) , metadata$status, deseq_results, "~/output/gbm_plots/")
drug_target_analysis( "icosapent" , c("ACSL3", "ACSL4", "FADS1", "FFAR1", "PPARD", "PPARG", "PTGS1", "PTGS2", "SLC8A1", "TRPV1"), as.data.frame(tpm_df) , metadata$status, deseq_results, "~/output/gbm_plots/")

drug_target_analysis( "nimodipine" , c("AHR", "CACNA1C", "CACNA1D", "CACNA1F", "CACNA1S", "CACNB1","CACNB2", "CACNB3", "CACNB4", "CFTR", "NR3C2" ), as.data.frame(tpm_df) , metadata$status, deseq_results, "~/output/gbm_plots/")

drug_target_analysis( "saxagliptin" , c("DPP4" ), as.data.frame(tpm_df) , metadata$status, deseq_results, "~/output/gbm_plots/")

```


### Save Data
### Save Figures
NA
    
# END
    Location of final scripts:
    /script
    
    Location of data produced:
    na
    
    Dates when operations were done:
    220901
    
## Versions
```{r}
sessionInfo()
```
