---
title: "220607_PAAD_SignatureSearch"
author: "Jennifer Fisher"
date: "6/7/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# START 
    Goal/Purpose of operations: 
    quick summary 
    
    Finished psedocode on: Date
    
    System which operations were done on: my laptop(on cheaha), lab mac etc... 
    
    GitHub Repo:
    
    Directory of operations: /path
    
    Scripts being edited for operations: filename(s)
    
    Data being used: description and location
    
    Papers and tools: deseq with paper 

# STEPS
### Set working directory 
### load in data
```{r}
library(recount3)
library(SummarizedExperiment)
```

```{r }
human_projects<- available_projects()
```

```{r }
#SRP118922
recount3_rse_PAAD<- create_rse(human_projects[(human_projects$project == "PAAD"),])
```
```{r}
#SRP118922
recount3_rse_PANCREAS<- create_rse(human_projects[(human_projects$project == "PANCREAS"),])
```
```{r}
PAAD_counts<- assay(recount3_rse_PAAD)
PAAD_metadata<- as.data.frame(colData(recount3_rse_PAAD))
PANCREAS_counts<- assay(recount3_rse_PANCREAS)
PANCREAS_metadata<- as.data.frame(colData(recount3_rse_PANCREAS))
```



PANCREAS cancer vs normal 
things to add to metadata- database, tumor/normal, subtype, sex

```{r}
#order the tcga data to match recount3 order
recount3_ids <- colnames(PAAD_counts)
recount_metadata_sub <-PAAD_metadata[rownames(PAAD_metadata) %in% recount3_ids,]
identical(rownames(recount_metadata_sub),recount3_ids)
ids <- recount_metadata_sub$tcga.tcga_barcode 

nam <- c()
status<- c()
sex<- c()
for (i in 1:length(ids)){
  
nam[i]<- ids[i]
#create tumor/normal col
status[i] <-PAAD_metadata$tcga.cgc_sample_sample_type[PAAD_metadata$tcga.tcga_barcode == ids[i]]
#create sex col 
sex[i]<- PAAD_metadata$tcga.cgc_case_gender[PAAD_metadata$tcga.tcga_barcode == ids[i]]
}
#create database col
database <- rep("TCGA", length(sex))
#create metadata 
tcga_paad_metadata<- as.data.frame(cbind(nam, database, status,  sex))
rownames(tcga_paad_metadata) <- recount3_ids
tcga_paad_metadata[1:5,]
```
```{r}
#order the metadata to match recount3 order

#create sex col 
identical (rownames(PANCREAS_metadata), colnames( PANCREAS_counts))
nam<- PANCREAS_metadata$external_id
sex<- ifelse(PANCREAS_metadata$gtex.sex == 1, "male", "female")
#create database col
database<- rep ("GTEx",length(sex) )
#create normal col
status<- rep ("Solid Tissue Normal", length(sex))


#create metadata 
gtex_metadata<- as.data.frame(cbind(nam, database, status, sex))
rownames(gtex_metadata)<- rownames(PANCREAS_metadata)
#combine count and metadata
gtex_metadata[1:5,]
```

```{r}
all_metadata <- rbind(tcga_paad_metadata, gtex_metadata)
rownames(all_metadata)<- c(rownames(tcga_paad_metadata), rownames(gtex_metadata))
count_table<- cbind(PAAD_counts, PANCREAS_counts)
```

```{r}
identical(rownames(all_metadata), colnames(count_table))
```
```{r}
library(signatureSearch)
library(HDF5Array)
se <- SummarizedExperiment(HDF5Array("~/data/lincs_2020.h5", name="assay"))
```

```{r}
rownames(se) <- HDF5Array("~/data/lincs_2020.h5", name="rownames")
colnames(se) <- HDF5Array("~/data/lincs_2020.h5", name="colnames")
```

```{r}
db_path <- "~/data/lincs_2020.h5"
```

the other tumor class...
#grep("NEUROENDOCRINE",recount3_rse_PAAD@colData$tcga.cgc_case_other_histological_diagnosis, ignore.case = TRUE)
```{r}
id_list <-recount3_rse_PAAD@colData$external_id[ grep("NEUROENDOCRINE",recount3_rse_PAAD@colData$tcga.cgc_case_other_histological_diagnosis, ignore.case = TRUE)]
all_metadata_v2<- all_metadata[! all_metadata$nam %in% id_list ,]
count_table_v2<- count_table[, !all_metadata$nam %in% id_list ]
```

remove recurrent tumors
```{r}
all_metadata_v3<- all_metadata_v2[!all_metadata_v2$status == "Metastatic",]
count_table_v3<- count_table_v2[, !all_metadata_v2$status == "Metastatic"]
```


### Analysis
#### Deseq2
deseq2 with raw counts
DESEq2 (make into a function )

```{r}
library(DESeq2)
```


```{r}
dds_paad_normal <- DESeqDataSetFromMatrix(countData = count_table_v3,
                              colData = all_metadata_v3,
                              design= ~ database + status)
```


```{r}

  #count-matrix with just counts
  #metadata
  #dds <- DESeqDataSetFromMatrix(countData = GLUT_COUNTS2,
                         #     colData = colD,
                             # design= ~ batch + group)
deseq2_function <- function(dds, file_name, condition,  B, A){
  #dds deseq2 object
  #condition b-TUMOR a-CONTROL 
  dds <- DESeq(dds)
  #resultsNames(dds) # lists the coefficients
  dds_res <- results(dds, c(condition,B,A))
  res_df <- as.data.frame(dds_res)
  #head(EV_GLUT_res_df_ENS)
  file_name <- paste0("~/output/pancreas_cancer/deseq2_res/",file_name, sep="")
  write.table(res_df, file=file_name, sep=",", row.names =TRUE)
  return(res_df)
}
```

```{r eval= FALSE}
deseq2_paad_normal <- deseq2_function(dds_paad_normal, "Deseq2_paad_normal_gtx_res.csv", "status", "Primary Tumor", "Solid Tissue Normal")
```
signaturesearch 
Genes
```{r}
#SRP118922
library(recount3)
human_projects<- available_projects()
test<- create_rse(human_projects[(human_projects$project == "SRP118922"),])
gene_info <- test@rowRanges
rm(test)
```

```{r}
dim(as.data.frame(gene_info))
```

```{r}
identical(gene_info$gene_id, rownames(deseq2_paad_normal))
```

```{r}
deseq2_paad_normal$Symbol<- gene_info$gene_name
```

```{r}
deseq2_paad_normal<- deseq2_paad_normal[complete.cases(deseq2_paad_normal),]
deseq_results_sig <- deseq2_paad_normal[deseq2_paad_normal$padj < 0.05 & abs(deseq2_paad_normal$log2FoldChange) > 2,]
```

```{r}
downset<- deseq_results_sig$Symbol[order(deseq_results_sig$log2FoldChange)] [1:500]
upset<- deseq_results_sig$Symbol[order(-deseq_results_sig$log2FoldChange)] [1:500]
```



```{r}
#upset<-deseq_results_sig$Symbol[deseq_results_sig$log2FoldChange >0]
#downset<- deseq_results_sig$Symbol[deseq_results_sig$log2FoldChange <0]
```
```{r}
gene_info_LINCS<- read.table("~/data/LINCS_210914_LEVEL3/geneinfo_beta.txt", sep="\t", header=TRUE)
```

```{r}
upset_v2<- c()
for (i in 1:length(upset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    upset_v2[i]<- gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol]
  }else{
    upset_v2[i]<- NA
  }
  
}
names(upset_v2)<- upset
```

```{r}
downset_v2<- c()
for (i in 1:length(downset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    downset_v2[i]<- gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol]
  }else{
    downset_v2[i]<- NA
  }
  
}
names(downset_v2)<- downset
```

```{r}
downset_v2<- downset_v2[complete.cases(downset_v2)]
upset_v2<- upset_v2[complete.cases(upset_v2)]
```

```{r}
#double check that they didn't overlap 
 intersect(downset_v2, upset_v2)
```


```{r}
names(upset_v2)<- NULL
names(downset_v2)<- NULL
```
```{r}
deseq_paad_list<- list(up= upset_v2, down= downset_v2)
```

```{r}
saveRDS(deseq_paad_list,"~/output/pancreas_cancer/deseq2_res/SR_gene_list_paad_deseq2.rds")
```


```{r}
set.seed(101)
qsig_lincs_deseq2_res <- qSig(query=list(upset=as.character(upset_v2), downset=as.character(downset_v2)), 
                   gess_method="LINCS", refdb=db_path)
```


```{r}
set.seed(101)
lincs_deseq_gbm <- gess_lincs(qsig_lincs_deseq2_res, sortby="NCS")
#result(lincs)
```



```{r}
lincs_deseq_paad_res <- result(lincs_deseq_gbm)
```

```{r}
write.csv(lincs_deseq_paad_res, file= "~/output/pancreas_cancer/deseq2_res/220602_SR_LINCS_PAAD_DESEQ2_RES.csv" )
```

```{r}
lincs_deseq_paad_res_YAPC <- lincs_deseq_paad_res[lincs_deseq_paad_res$cell == "YAPC",]
```
tau 
```{r}
YAPC_taudf <- readRDS("~/data/YAPC_taudf.rds")
```


```{r}
tau_scores<- function(results_df, tau_score_df){
  #download the tau values 
  #scores <- readRDS(tau_score_file)
  results_df$id <- paste(results_df$pert, results_df$cell, results_df$type, sep= "__")
  #print(results_df$id)
  tau_list<- c()
  for (i in 1:nrow(results_df)){
    #print( results_df$id[i])
    #print(colnames(tau_score_df) == results_df$id[i])
    index <- grepl(results_df$pert[i], colnames(tau_score_df))
   scores <- tau_score_df[,colnames(tau_score_df) == results_df$id[i]]
   #print(scores)
      tmpsum <- sum( abs(scores) < abs(results_df$NCS[i]))
      secd<- (tmpsum/length(scores)) *100
      tau<- secd* sign( results_df$NCS[i])
      #print(tau)
   tau_list[i]<- tau
  }
  return(tau_list)
}
```

```{r}
tau_test<- tau_scores(lincs_deseq_paad_res_YAPC , YAPC_taudf)
```

```{r}
lincs_deseq_paad_res_YAPC$jlf_tau<- tau_test
```

```{r}
lincs_deseq_paad_res_YAPC_top <- lincs_deseq_paad_res_YAPC[lincs_deseq_paad_res_YAPC$NCS < 0 & lincs_deseq_paad_res_YAPC$WTCS_FDR < 0.05 & lincs_deseq_paad_res_YAPC$jlf_tau< -80,]
```

clinical trials
```{r}
fda_info <- read.table("~/data/fda_product_info_df.csv" )
fda_approve <- fda_info[fda_info$market_status_v2 %in% c("Over-the-Counter", "Prescription" ),]
```

```{r}
FDA_APPROVAL_CHECK<- function(drug_list){
  return_list <- c()
  for (i in 1:length(drug_list)){
    test <- grep( drug_list[i], fda_approve$ActiveIngredient, ignore.case= TRUE)
    if (length(test)>0 ){
      return_list[i] <- TRUE
    }else{
      return_list[i] <- FALSE
    }
    if (nchar(drug_list[i])< 3){
      return_list[i] <- FALSE
    }
  }
  names(return_list)<- drug_list
  return(return_list)
}
```
```{r}
lincs_deseq_paad_res_YAPC_top$fda_approved<- FDA_APPROVAL_CHECK(lincs_deseq_paad_res_YAPC_top$pert)
```

double checking the direction of signature


```{r}
clinical_trial_PAAD <- read_csv("~/data/SearchResults_PAAD.csv")
```

```{r}
clinical_trial_check<- function(drug_list, clinical_trial_info){
    return_list <- c()
  for (i in 1:length(drug_list)){
    test <- grep( drug_list[i], clinical_trial_info$Interventions, ignore.case= TRUE)
    if (length(test)>0 ){
      return_list[i] <- TRUE
    }else{
      return_list[i] <- FALSE
    }
    if (nchar(drug_list[i])< 3){
      return_list[i] <- FALSE
    }
  }
  names(return_list)<- drug_list
  return(return_list)
}
```

```{r}
lincs_deseq_paad_res_YAPC_top$clinical_trial_PAAD <- clinical_trial_check(lincs_deseq_paad_res_YAPC_top$pert, clinical_trial_PAAD)
```

iq is wrongly classified as approved in clinical trail 

```{r}
lincs_deseq_paad_res_YAPC_top_fda<- lincs_deseq_paad_res_YAPC_top[lincs_deseq_paad_res_YAPC_top$fda_approved,]
#lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD<- ifelse(lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD, "star", "")

lincs_deseq_paad_res_YAPC_top_fda_order <- lincs_deseq_paad_res_YAPC_top_fda[order(-lincs_deseq_paad_res_YAPC_top_fda$NCS),]
lincs_deseq_paad_res_YAPC_top_fda$pert <- factor(lincs_deseq_paad_res_YAPC_top_fda$pert, levels = lincs_deseq_paad_res_YAPC_top_fda_order$pert)
p<-ggplot(data=lincs_deseq_paad_res_YAPC_top_fda, aes(x=pert, y=NCS, fill=jlf_tau, shape= clinical_trial_PAAD)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1) + geom_point(aes(y = NCS - 0.15), position = position_dodge(0.9), size= 4, show.legend = TRUE)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]", shape= "Clinical Trials")

ggsave("~/output/pancreas_cancer/deseq2_res/220421_ggplot_deseq2_tau_paad_approved_candidates.png")
```

```{r}
#lincs_deseq_paad_res_YAPC_top 
write.csv(lincs_deseq_paad_res_YAPC_top , file= "~/output/pancreas_cancer/deseq2_res/220602_SR_LINCS_PAAD_DESEQ2_RES_tau.csv" )
```

pathways

```{r}

hyperG_k_res <- dsea_hyperG(drugs = lincs_deseq_paad_res_YAPC_top_fda$pert, type = "KEGG", pvalueCutoff = 1, qvalueCutoff = 1,  minGSSize = 10, maxGSSize = 2000)
hyperG_k_res_v2<- result(hyperG_k_res)
```

```{r}
#false discovery rate
hyperG_k_res_v2$logqvalue<- -log(hyperG_k_res_v2$qvalue)
```

```{r}
hyperG_k_res_v2$Description<- factor(hyperG_k_res_v2$Description, levels= hyperG_k_res_v2$Description)
```

```{r}
library(viridis)
```

```{r}
gbm.2<-ggplot(data=hyperG_k_res_v2[1:30,] , aes(x=Description, y=Count, fill=logqvalue )) +
  geom_bar(stat="identity") + scale_fill_viridis()
gbm.2 + coord_flip() + ylab("Number of Drugs") + xlab("KEGG Pathways") +labs(fill = "-log(q-value)")
```
no kegg pathways are signficant

```{r}
write.csv(hyperG_k_res_v2 , file= "~/output/pancreas_cancer/deseq2_res/220602_SR_LINCS_PAAD_DESEQ2_PATHWAY.csv" )
```


LINCS pathway & Drug targets
```{r}
drug_analysis <- function(drug_name, target_list,  tpm_df, sample_vector, deseq_results, se, cell_lincs= "__GI1__trt_cp", result_path){
  #drug target expression
  tpm_sub <- tpm_df[rownames(tpm_df) %in% target_list,]
  tpm_sub$genes<- rownames(tpm_sub)
  tpm_sub_v2 <- tpm_sub %>%
  pivot_longer(!genes, names_to = "sample", values_to = "tpm")
  tpm_sub_v2$type <- rep(sample_vector, nrow(tpm_sub))
  name<- drug_name
  y_max<- max(tpm_sub_v2$tpm) +5
  
  
  deseq_sub <-  deseq_results[ deseq_results$Symbol %in% unique( tpm_sub$genes),]
  stat_table <- deseq_sub[,c(7,6)]
  stat_table$group1 <- rep("Primary Tumor" ,  nrow(tpm_sub))
  stat_table$group2 <- rep("Solid Tissue Normal" ,  nrow(tpm_sub))
  stat_table$padj <- ifelse(stat_table$padj < 0.05, formatC(stat_table$padj, format = "e", digits = 2), "")
  colnames(stat_table)<- c("genes", "padj" ,  "group1" ,"group2")
  
  
  file_name<- paste0(result_path, "/", drug_name, "_drug_target_expression_deseq2_padj.png")
  
  ggplot(tpm_sub_v2, aes(x=genes, y=tpm, color=type)) + geom_boxplot()+ stat_pvalue_manual(stat_table, x="genes" , label = "{padj}", y.position= y_max,  size = 3) + labs(title=name,x="Drug Targets", y = "Gene Expression (TPM)", color= "Sample Type") + scale_colour_manual(values =  c("#440154FF","#228C8DFF"), aesthetics = c("colour", "fill"))+theme_classic()
  ggsave(file_name, width = 20, height = 8)
  
  #pathway enrichment
  lincs_name<- paste0(drug_name, cell_lincs)
  sub <- se[,grep(lincs_name, colnames(se))]
  up <- sub[sub >= 2  ]
  up<- names(up[order(-up)])
  down<- sub[ sub <= -2 ]
  down <- names(down[order(down)])
  #print(down)
  downset_pathway_results <- gost(query = down, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  downset_pathway_results<- downset_pathway_results$result
  
  upset_pathway_results <- gost(query = up, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  upset_pathway_results<- upset_pathway_results$result
  
  pathway_results<- rbind(upset_pathway_results, downset_pathway_results)
  pathway_results$set<- c(rep("Up", nrow(upset_pathway_results)), rep("Down", nrow(downset_pathway_results)))
  file_name<- paste0(result_path, "/", drug_name, "_drug_pathways.csv")
  write.csv2(as.data.frame(pathway_results[,-14]), file_name )
  
  file_name<- paste0(result_path, "/", drug_name, "_drug_pathways.png")
  
  #making adjustments here
  #pathway_results$set <- factor(pathway_results$set, levels = c("up", "down"))
  
  if(nrow(pathway_results)<50){
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value))+geom_tile()+scale_fill_viridis(direction=-1)+theme_classic()+ labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
    
  }else{
    pathway_results<- pathway_results[pathway_results$source %in% c("KEGG","REAC","GO:MF" ),]
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value)) + geom_tile()+ scale_fill_viridis(direction=-1)+ theme_classic() + labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
  }
  ggsave(file_name, width = 12, height = 14)
  
}
```

```{r}
Counts_to_tpm <- function(counts, featureLength) {
  # Ensure valid arguments.
  stopifnot(length(featureLength) == nrow(counts))
  # Compute effective lengths of features in each library.
  effLen <- featureLength
  # Process one column at a time.
  tpm <- do.call(cbind, lapply(1:ncol(counts), function(i) {
    rate = log(counts[,i]) - log(effLen)
    denom = log(sum(exp(rate)))
    exp(rate - denom + log(1e6))
  }))
  # Copy the row and column names from the original matrix.
  colnames(tpm) <- colnames(counts)
  rownames(tpm) <- rownames(counts)
  return(tpm)
}
```


```{r}
gene_info <- as.data.frame(recount3_rse_PANCREAS@rowRanges)
```

```{r}
tpm_table<- Counts_to_tpm(count_table_v3, gene_info$bp_length)
```

```{r}
rownames(tpm_table)<- gene_info$gene_name
```

```{r}
tpm_df <- as.data.frame(tpm_table)
```

```{r}
library(tidyr)
```
```{r}
se_asssay<- assay(se)
```

```{r}
library(gprofiler2)
```

```{r}

drug_analysis( "moxifloxacin", c("TOP2A"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/deseq2_res/220602_candidate_plot/")

drug_analysis( "zaleplon", c("GABRA1"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/deseq2_res/220602_candidate_plot/")

drug_analysis( "pseudoephedrine", c("SLC6A2", "SLC6A3", ),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/deseq2_res/220602_candidate_plot/")

```


PRISM

```{r}
library(readr)
primary_screen <- read_csv("~/data/DEPMAP_PRISM_220228/primary-screen-replicate-collapsed-logfold-change.csv")
sample_info <- read_csv("~/data/DEPMAP_PRISM_220228/sample_info.csv")
primary_screen_treatment_info <- read_csv("~/data/DEPMAP_PRISM_220228/primary-screen-replicate-collapsed-treatment-info.csv")
```
different order

```{r}
names_vector<- c()
for ( i in 2:ncol(primary_screen)){
  names_vector[i] <- primary_screen_treatment_info$name[ grep(colnames(primary_screen)[i], primary_screen_treatment_info$column_name)]
}
```

```{r}
good_id <- c()
for (i in 1:nrow(primary_screen)){
  good_id[i]<- nchar(primary_screen[i,1]) == 10 
}

```

```{r}
table(good_id)
```
```{r}
primary_screen_v2 <- primary_screen[good_id,]
```


```{r}
cell_vector<- c()
for ( i in 1:nrow(primary_screen_v2)){
  cell_vector[i] <-sample_info$stripped_cell_line_name[ grep(as.character(primary_screen_v2[i,1]), sample_info$DepMap_ID)]
}
```

```{r}
primary_screen_v3<-  as.matrix(primary_screen_v2[,-1])
rownames(primary_screen_v3)<- cell_vector
```


```{r}
colnames(primary_screen_v3) <- names_vector[-1]
```

```{r}
test2<- as.data.frame.table(primary_screen_v3, responseName = "log_fold_change")
```

```{r}
test2$Sensitive <- test2$log_fold_change < 0.3
```

filter by PANCREAS cancer cell lines

```{r}
#table(sample_info$Subtype)
sample_info<- as.data.frame(sample_info)
paad_sample_info <- sample_info[grep("Ductal Adenocarcinoma", sample_info$Subtype),]
```


```{r}
primary_paad_res <- test2[test2$Var1 %in% as.vector(paad_sample_info$stripped_cell_line_name),]
```


```{r}
primary_paad_res_sub <-primary_paad_res[ primary_paad_res$Var2 %in% lincs_deseq_paad_res_YAPC_top_fda$pert,]
```


```{r}
write.csv(primary_paad_res_sub , file= "~/output/pancreas_cancer/deseq2_res/220602_prism_deseq2_candidates.csv" )
```


```{r}
library(ggplot2)
library(viridis)
```


```{r}
primary_paad_res_sub$Var2 <- factor(primary_paad_res_sub$Var2, levels=unique(primary_paad_res_sub$Var2[order(-primary_paad_res_sub$log_fold_change)]))
ggplot(primary_paad_res_sub, aes(x=log_fold_change, y= Var2))+ geom_violin() +geom_vline(xintercept = 0.3)  + ylab("Drug Candidates") + xlab("log fold change")
ggsave("~/output/pancreas_cancer/deseq2_res/220602_ggplot_deseq2_candidates_prism_screen1.png")
```
```{r}
drug_list <- as.vector(unique(primary_paad_res_sub$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res_sub$Sensitive[primary_paad_res_sub$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
drug_senstive_precentage_all_drugs$drug_list<- factor(drug_senstive_precentage_all_drugs$drug_list, levels= unique(drug_senstive_precentage_all_drugs$drug_list[order(drug_senstive_precentage_all_drugs$drug_fraction)]))
ggplot(drug_senstive_precentage_all_drugs, aes( drug_fraction, drug_list, fill= test ))+ geom_bar(stat="identity") + scale_fill_viridis_d() + ylab("Drug Candidates") + xlab("Fraction of Sensitive Cell Lines") +labs(fill = "75% of Cell line are Sensitive")
ggsave("~/output/pancreas_cancer/deseq2_res/220602_ggplot_deseq2_candidates_prism_screen1_sensitive_cell_lines.png")
```

```{r}
#clinical trials -testing

clinical_trial_testing<- function(seed, cell_line,number_sig_drugs, fraction_clinical_drugs, CT_DATA){
  FDA_CT_table<- CT_DATA
  library(HDF5Array)
  lincs_samples<- HDF5Array("~/data/lincs_2020.h5", name="colnames")
  lincs_samples<- as.vector(lincs_samples)

  lincs_samples_GBM <- lincs_samples[grep(cell_line,lincs_samples )]
  library(stringr)
  gbm_lincs_drugs <- as.vector(str_split(lincs_samples_GBM,  "__", simplify = TRUE)[,1])
  
  gbm_lincs_drugs<- gbm_lincs_drugs[FDA_APPROVAL_CHECK(gbm_lincs_drugs)]
  set.seed(seed)
  fraction<-c()
  for (i in 1:10000){
    test <- gbm_lincs_drugs[ sample(x = 1:length(gbm_lincs_drugs),size = number_sig_drugs ,replace = FALSE)]
    value2 <- c()
    
    #tables<- list()
    for (k in 1:number_sig_drugs){
      res <- grep(test[k], FDA_CT_table$Interventions, ignore.case=TRUE )
      res <- as.logical(length(res) > 0 )
     # print(res)
      #if (res == TRUE){
        #print(test[j])
      #}
      #print(j)
      #print(res)
      #print(length(res))
      #print(res)
      value2[k] <- res
    }
    res_table <- cbind(test, value2)
    fraction[i]<- table(res_table[,2])["TRUE"]
    #tables[i]<- res_table
    
  }
  fraction <- ifelse(is.na(fraction), 0, fraction)
  fraction_adj <- fraction/number_sig_drugs
  #hist(fraction_adj)
  #print(fraction_adj)
  
  plot_data<- as.data.frame(cbind(1:10000, fraction_adj))
  plot <- ggplot(plot_data, aes(x=fraction_adj)) + geom_histogram() + geom_vline(xintercept = fraction_clinical_drugs)
  
  print(plot)

  return(wilcox.test(fraction_adj,mu= fraction_clinical_drugs , alternative="less" ))
  #return(fraction_adj)
}
```

```{r}
#x<- 4/31
deseq2_CT_test_res <- clinical_trial_testing(101, "YAPC", 23, 0.08695652 , clinical_trial_PAAD)
```


```{r}
drug_list <- as.vector(unique(primary_paad_res$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res$Sensitive[primary_paad_res$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
```


```{r}
#Prism testing
PRISM_testing<- function(seed, cell_line, drugs, drug_senstive_precentage_all_drugs){
  
  #check all drugs for fda approval
  library(HDF5Array)
  lincs_samples<- HDF5Array("~/data/lincs_2020.h5", name="colnames")
  lincs_samples<- as.vector(lincs_samples)

  lincs_samples_GBM <- lincs_samples[grep(cell_line,lincs_samples )]
  library(stringr)
  gbm_lincs_drugs <- as.vector(str_split(lincs_samples_GBM,  "__", simplify = TRUE)[,1])
  
  gbm_lincs_drugs<- gbm_lincs_drugs[FDA_APPROVAL_CHECK(gbm_lincs_drugs)]
  
   #get the median number of cell lines senestive to drugs for sigficant drug list 
  test_median <- median(drug_senstive_precentage_all_drugs$drug_fraction[ drug_senstive_precentage_all_drugs$drug_list %in% drugs ] )
  
  print(test_median)
  
  number_sig_drugs<- length(drugs)
  # do that again 10,000 times 
  set.seed(seed)
  fraction<-c()
  for (i in 1:10000){
    test <- gbm_lincs_drugs[ sample(x = 1:length(gbm_lincs_drugs),size = number_sig_drugs ,replace = FALSE)]
    fraction[i] <- median(drug_senstive_precentage_all_drugs$drug_fraction[ drug_senstive_precentage_all_drugs$drug_list %in% test ] )

    }
  #fraction <- ifelse(is.na(fraction), 0, fraction)
  #fraction_adj <- fraction
  #hist(fraction_adj)
  #print(fraction_adj)
  
  plot_data<- as.data.frame(cbind(1:10000, fraction))
  plot <- ggplot(plot_data, aes(x=fraction)) + geom_histogram() + geom_vline(xintercept = test_median)+ labs( x = "median fraction of sensitive cell lines") + annotate("text", x=(test_median + 0.1) , y=800, label= test_median)
  
  print(plot)

  return(wilcox.test(fraction, mu= test_median , alternative="less" ))
  #return(fraction_adj)
}
```

```{r}
deseq2_PRISM_test<- PRISM_testing(101,"YAPC", lincs_deseq_paad_res_YAPC_top_fda$pert, drug_senstive_precentage_all_drugs)
```
```{r}
deseq2_PRISM_test
```


#### limma
limma with tpm counts
normalize count data by tpm

```{r}
TPM <- log2(as.matrix(tpm_df) + 1)

```


```{r}
TestLVDifferencesJLF <- function(b.matrix, phenotype, blocking,
                              use.bonferroni = FALSE) {
  # This function tests for differential expression of PLIER-derived latent
  # variables between groups specified by the phenotype argument
  # using limma. Examples include different disease groups or disease v. 
  # control. It takes the B matrix from a PLIER model and a factor vector with 
  # the group labels. It will reorder the phenotype vector if control.phenotype
  # is specified. The resulting p-values are Benjamini-Hochberg corrected by 
  # default or Bonferroni corrected if use.bonferroni = TRUE
  # 
  # Args:
  #   b.matrix: a B matrix (latent variables are rows, samples are columns) 
  #             from a PLIER model. Can be the B element of the list 
  #             returned by PLIER::PLIER or the output of GetNewDataB
  #   phenotype: a named factor vector that contains group labels to be used
  #              for contrasts
  #   blocking: a names facotor vector that contains group labels to be used for blocking
  #   use.bonferroni: logical - should bonferroni correction be used? if FALSE
  #                   (default), will use "BH"
  #   
  # Returns:
  #   A limma::topTable, where the first column is the latent variable name and
  #   all pathways are returned (without filtering or sorting)
  
  ## error-handling ##
  
  if (is.null(names(phenotype))) {
    stop("phenotype should be a named factor vector -- the names ensure that
         the vector is correctly ordered")
  }
  if (is.null(names(blocking))) {
    stop("blocking should be a named factor vector -- the names ensure that
         the vector is correctly ordered")
  }  
  # no names should be "missing"
  check.names <- all(colnames(b.matrix) %in% names(phenotype)) & 
    all(names(phenotype) %in% colnames(b.matrix)) 
  
  if (!check.names) {
    stop("Some sample(s) is missing from colnames(b.matrix) or 
         names(phenotype)")
  }
  
  # the phenotype labels should be in the same order as the b.matrix samples
  ordered.phenotype <- as.factor(phenotype[colnames(b.matrix)])
  
  # the blocking labels should be in the same order as the b.matrix samples
  ordered.blocking <- as.factor(blocking[colnames(b.matrix)])
  
  # get contrasts (all pairwise)  
  num.levels <- length(levels(ordered.phenotype))
  contrast.vector <- c()
  for (lvl in levels(ordered.phenotype)[1:(num.levels - 1)]) {
    for (lvl.2 in levels(ordered.phenotype)[2:num.levels]) {
      if (lvl != lvl.2) {
        contrast.vector <- append(contrast.vector, paste(lvl, lvl.2, sep = "-"))
      }
    }
  }
  contrast.vector <- paste(contrast.vector, collapse = ", ")
  
  # prep design matrix
  design <- model.matrix(~ 0+ ordered.phenotype+ ordered.blocking )
  colnames(design)[seq_len(nlevels(ordered.phenotype))] <- levels(ordered.phenotype)
  
  
  
  
  #colnames(design) <- levels(ordered.phenotype)
  
  # fit linear model
  fit <- limma::lmFit(b.matrix, design)
  contrast.matrix <-
    eval(parse(
      text = paste0(
        'limma::makeContrasts(', contrast.vector, ', levels = design)')))
  fit2 <- limma::contrasts.fit(fit, contrast.matrix)
  fit2 <- limma::eBayes(fit2)
  
  # extract results as a data.frame
  if (use.bonferroni) {  # if specified, use Bonferroni correction
    limma.result <- limma::topTable(fit2, number = nrow(b.matrix),
                                    adjust.method = "bonferroni", 
                                    sort.by = "none")
  } else {  # calculate FDR
    limma.result <- limma::topTable(fit2, number = nrow(b.matrix),
                                    adjust.method = "BH", sort.by = "none")
  }
  
  # want feature (latent variable) names as column
  limma.result <- tibble::rownames_to_column(limma.result, var = "LV")
  
  return(limma.result)
  
}
```



```{r}
LVTestWrapperJLF_v2 <- function(b.matrix,
                          sample.info.df,
                          phenotype.col,
                          blocking,
                          file.lead,
                          plot.dir = "plots",
                          results.dir = "results",
                          use.bonferroni = FALSE,
                          significant.only = FALSE,
                          sig.threshold = 0.05) {
  # A wrapper function for TestLVDifferences and BoxplotDiffLV; does the 
  # reshaping required for plotting. Produces the following files: 1) tsv of the
  # differential expression results 2) a long form of the B matrix joined with
  # the sample information (sample.info.df) and 3) a PDF of boxplots
  # 
  # Args:
  #   b.matrix: a B matrix (latent variables are rows, samples are columns) 
  #             from a PLIER model. Can be the B element of the list 
  #             returned by PLIER::PLIER or the output of GetNewDataB
  #   sample.info.df: a long form data.frame that contains sample information,
  #                   sample names that match the B matrix sample identifiers
  #                   must be in a "Sample" column & it also must contain
  #                   the factor to group by for testing differential expression
  #                   (DE) and plotting
  #   phenotype.col: the column name of the column in sample.info.df to be used
  #                  for DE and plotting; character
  #   file.lead: string that designates the "beginning" of filenames
  #   plot.dir: plot directory where the boxplots PDF should be saved
  #   results.dir: results directory for DE results and reshaped B data.frame
  #   use.bonferroni: logical - should bonferroni correction be used for DE? 
  #                   if FALSE (default), will use "BH"
  #   significant.only: logical - should only differentially expressed LVs be
  #                     plotted? if FALSE (default), all will be plotted
  #   sig.threshold: the adj. P cutoff to be used if only plotting significant 
  #                  results; default is 0.05
  #                  
  # Returns:
  #   A list with the following elements
  #       limma: the results from TestLVDifferences 
  #       b.df: sample.b.df, prior to any filtering for plotting (if applicable)
  # 
  #   the following files are written by this function (see above):
  #     1) <results.dir>/<file.lead>_LV_limma_results.tsv
  #     2) <results.dir>/<file.lead>_B_long_sample_info.tsv
  #     3) <plot.dir>/<file.lead>_LV_boxplots.pdf
  
  `%>%` <- dplyr::`%>%`
  
  # error-handling
  # we need to join by "Sample" column for boxplots
  if (!("Sample" %in% colnames(sample.info.df))) {
    stop("'Sample' must be a column in sample.info.df")
  }
  # phenotype.col needs to be in column names
  if (!(phenotype.col %in% colnames(sample.info.df))) {
    stop("phenotype.col must be a column name in sample.info.df")
  }
  
  # initialize list to hold results to be returned
  return.list <- list()
  
  #### Differential Expression ####
  # get the named vector to use as the phenotype for testing differential 
  # expression
  phenotype.vector <- as.factor(make.names(sample.info.df[[phenotype.col]]))
  names(phenotype.vector) <- sample.info.df$Sample
  # test itself
  limma.df <- TestLVDifferencesJLF(b.matrix = b.matrix,
                                phenotype = phenotype.vector,
                                blocking= blocking,
                                use.bonferroni = use.bonferroni)
  # write to file
  dlve.file <- file.path(results.dir, 
                         paste0(file.lead, "_limma_results.tsv"))
  readr::write_tsv(limma.df, path = dlve.file)
  # add to list to be returned
  return.list[["limma"]] <- limma.df
  
  #### Reshape & join with sample information ####
  b.df <- reshape2::melt(b.matrix)
  #print(b.df)
  colnames(b.df) <- c("LV", "Sample", "Value")
  sample.b.df <- dplyr::inner_join(b.df, sample.info.df, by = "Sample")
  #long.file <- file.path(results.dir, 
                         #paste0(file.lead, "_B_long_sample_info.tsv"))
  #readr::write_tsv(sample.b.df, long.file)
  # add to list to be returned
  return.list[["b.df"]] <- sample.b.df
  
  #### Plotting ####
  plot.file <- file.path(plot.dir,
                         paste0(file.lead, "_boxplots.pdf"))
  
  # if we only want significant LVs plotted, filter sample.b.df using the
  # adj.P.Val cutoff sig.threshold
  if (significant.only) {
    sig.lvs <- limma.df$LV[which(limma.df$adj.P.Val < sig.threshold)]
    sample.b.df <- sample.b.df %>%
      dplyr::filter(LV %in% sig.lvs)
  }
  
 # BoxplotDiffLV(tidy.b.df = sample.b.df, 
              #  phenotype.column = phenotype.col,
             #   pdf.path = plot.file)
  
  
  return(return.list)
}
```

```{r}
source("~/script/test_LV_differences.R")
library(dplyr)
```


LVTestWrapperJLF <- function(b.matrix,
                          sample.info.df,
                          phenotype.col,
                          blocking,
                          file.lead,
                          plot.dir = "plots",
                          results.dir = "results",
                          use.bonferroni = FALSE,
                          significant.only = FALSE,
                          sig.threshold = 0.05)
                          

                          
```{r}
sampleinfo<- cbind(colnames(TPM), as.character(all_metadata_v3$status), as.character(all_metadata_v3$database))
colnames(sampleinfo) <- c("Sample", "Tumor","database")
sampleinfo<- as.data.frame(sampleinfo)
database<- all_metadata_v3$database
names(database)<- colnames(TPM)

limma_gene_TCGA_BH <- LVTestWrapperJLF_v2(b.matrix=TPM , sample.info.df= sampleinfo, phenotype.col= "Tumor", blocking= database, file.lead= "220601_limma_TCGA_GTEX_T_vs_NT_pancreas_cancer", plot.dir= "~/output/limma_gbm/", results.dir= "~/output/pancreas_cancer/limma_res/", use.bonferroni= FALSE, sig.threshold = 0.05)
```


```{r eval=FALSE}
saveRDS(limma_gene_TCGA_BH , file= "~/output/pancreas_cancer/limma_res/220601_PAAD_GTEX_gene_limma_res.rds")
```

signaturesearch 

```{r}
limma_res <- limma_gene_TCGA_BH$limma
```

```{r}
limma_results<- limma_res[complete.cases(limma_res),]
limma_results_sig <- limma_results[limma_results$adj.P.Val < 0.05 & abs(limma_results$logFC) > 1.5,]
```

```{r}
downset<- limma_results_sig$LV[ limma_results_sig$logFC < -1.5]
upset<- limma_results_sig$LV[limma_results_sig$logFC > 1.5]
```


```{r}
upset_v2<- c()
for (i in 1:length(upset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    upset_v2[i]<- gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol]
  }else{
    upset_v2[i]<- NA
  }
  
}
names(upset_v2)<- upset
```

```{r}
downset_v2<- c()
for (i in 1:length(downset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    downset_v2[i]<- gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol]
  }else{
    downset_v2[i]<- NA
  }
  
}
names(downset_v2)<- downset
```

```{r}
downset_v2<- downset_v2[complete.cases(downset_v2)]
upset_v2<- upset_v2[complete.cases(upset_v2)]
```

```{r}
#double check that they didn't overlap 
 intersect(downset_v2, upset_v2)
```

```{r}
length(downset_v2)
length(upset_v2)
```

```{r}
names(upset_v2)<- NULL
names(downset_v2)<- NULL
```

```{r}
limma_paad_list<- list(up= upset_v2, down= downset_v2)
```

```{r}
saveRDS(limma_paad_list,"~/output/pancreas_cancer/limma_res/SR_gene_list_paad_limma.rds")
```


```{r}
set.seed(101)
qsig_lincs_limma_pancreas_res <- qSig(query=list(upset=as.character(upset_v2), downset=as.character(downset_v2)), 
                   gess_method="LINCS", refdb=db_path)
```


```{r}
set.seed(101)
library(parallel)
lincs_limma_pancreas <- gess_lincs(qsig_lincs_limma_pancreas_res, sortby="NCS", tau=FALSE)
#result(lincs)
```



```{r}
lincs_limma_pancreas_res <- result(lincs_limma_pancreas)
```

```{r}
write.csv(lincs_limma_pancreas_res, file= "~/output/pancreas_cancer/limma_res/220601_SR_LINCS_PANCREAS_LIMMA_RES.csv" )
```

```{r}
lincs_limma_pancreas_res_YAPC <- lincs_limma_pancreas_res[lincs_limma_pancreas_res$cell == "YAPC",]
```
tau 


```{r}
tau_test<- tau_scores(lincs_limma_pancreas_res_YAPC, YAPC_taudf)
```

```{r}
lincs_limma_pancreas_res_YAPC$jlf_tau<- tau_test
```

```{r}
write.csv(lincs_limma_pancreas_res_YAPC, file= "~/output/pancreas_cancer/limma_res/220601_lincs_limma_pancreas_res_YAPC_tau.csv" )
```

```{r}
lincs_limma_pancreas_res_YAPC_top <- lincs_limma_pancreas_res_YAPC[lincs_limma_pancreas_res_YAPC$NCS < 0 & lincs_limma_pancreas_res_YAPC$WTCS_FDR < 0.05 & lincs_limma_pancreas_res_YAPC$jlf_tau< -80,]
```

clinical trials

```{r}
lincs_limma_pancreas_res_YAPC_top$fda_approved<- FDA_APPROVAL_CHECK(lincs_limma_pancreas_res_YAPC_top$pert)
```


```{r}
lincs_limma_pancreas_res_YAPC_top$clinical_trial_PAAD <- clinical_trial_check(lincs_limma_pancreas_res_YAPC_top$pert, clinical_trial_PAAD)
```


```{r}
lincs_limma_pancreas_res_YAPC_top_fda<- lincs_limma_pancreas_res_YAPC_top[lincs_limma_pancreas_res_YAPC_top$fda_approved,]
#lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD<- ifelse(lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD, "star", "")

lincs_limma_pancreas_res_YAPC_top_fda_order <- lincs_limma_pancreas_res_YAPC_top_fda[order(-lincs_limma_pancreas_res_YAPC_top_fda$NCS),]
lincs_limma_pancreas_res_YAPC_top_fda$pert <- factor(lincs_limma_pancreas_res_YAPC_top_fda$pert, levels = lincs_limma_pancreas_res_YAPC_top_fda_order$pert)
p<-ggplot(data=lincs_limma_pancreas_res_YAPC_top_fda, aes(x=pert, y=NCS, fill=jlf_tau, shape= clinical_trial_PAAD)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1) + geom_point(aes(y = NCS - 0.15), position = position_dodge(0.9), size= 4, show.legend = TRUE)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]", shape= "Clinical Trials")

ggsave("~/output/pancreas_cancer/limma_res/220421_ggplot_limma_tau_paad_approved_candidates_top_30.png")
```

```{r}
#lincs_deseq_paad_res_YAPC_top 
write.csv(lincs_limma_pancreas_res_YAPC_top , file= "~/output/pancreas_cancer/limma_res/220602_SR_LINCS_PAAD_limma_RES_tau.csv" )
```

pathways

```{r}

hyperG_k_res <- dsea_hyperG(drugs = lincs_limma_pancreas_res_YAPC_top_fda$pert, type = "KEGG", pvalueCutoff = 1, qvalueCutoff = 1,  minGSSize = 10, maxGSSize = 2000)
hyperG_k_res_v2<- result(hyperG_k_res)
```

```{r}
#false discovery rate
hyperG_k_res_v2$logqvalue<- -log(hyperG_k_res_v2$qvalue)
```

```{r}
hyperG_k_res_v2$Description<- factor(hyperG_k_res_v2$Description, levels= hyperG_k_res_v2$Description)
```

```{r}
gbm.2<-ggplot(data=hyperG_k_res_v2[1:30,] , aes(x=Description, y=Count, fill=logqvalue )) +
  geom_bar(stat="identity") + scale_fill_viridis()
gbm.2 + coord_flip() + ylab("Number of Drugs") + xlab("KEGG Pathways") +labs(fill = "-log(q-value)")
```
no kegg pathways are signficant

```{r}
write.csv(hyperG_k_res_v2 , file= "~/output/pancreas_cancer/limma_res/220602_SR_LINCS_PAAD_limma_PATHWAY.csv" )
```


LINCS pathway & Drug targets


```{r}
#drug_analysis(drug_name, target_list,  tpm_df, sample_vector, deseq_results, se, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/deseq2_res/220602_candidate_plot/")

drug_analysis( "tigecycline", c("Y_RNA" ),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/limma_res/220602_candidate_plot/")


```


PRISM

```{r}
primary_paad_res_sub <-primary_paad_res[ primary_paad_res$Var2 %in% lincs_limma_pancreas_res_YAPC_top_fda$pert,]
```


```{r}
write.csv(primary_paad_res_sub , file= "~/output/pancreas_cancer/limma_res/220602_prism_limma_candidates.csv" )
```

```{r}
primary_paad_res_sub <-primary_paad_res[ primary_paad_res$Var2 %in% lincs_limma_pancreas_res_YAPC_top_fda$pert,]
```

```{r}
primary_paad_res_sub$Var2 <- factor(primary_paad_res_sub$Var2, levels=unique(primary_paad_res_sub$Var2[order(-primary_paad_res_sub$log_fold_change)]))
#primary_paad_res_sub$Var2 <- factor(primary_paad_res_sub$Var2, levels=unique(primary_paad_res_sub$Var2))
ggplot(primary_paad_res_sub, aes(x=log_fold_change, y= Var2))+ geom_violin() +geom_vline(xintercept = 0.3)  + ylab("Drug Candidates") + xlab("log fold change")
ggsave("~/output/pancreas_cancer/limma_res/220602_ggplot_limma_candidates_prism_screen1.png")
```

```{r}
drug_list <- as.vector(unique(primary_paad_res_sub$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res_sub$Sensitive[primary_paad_res_sub$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
drug_senstive_precentage_all_drugs$drug_list<- factor(drug_senstive_precentage_all_drugs$drug_list, levels= unique(drug_senstive_precentage_all_drugs$drug_list[order(drug_senstive_precentage_all_drugs$drug_fraction)]))
ggplot(drug_senstive_precentage_all_drugs, aes( drug_fraction, drug_list, fill= test ))+ geom_bar(stat="identity") + scale_fill_viridis_d() + ylab("Drug Candidates") + xlab("Fraction of Sensitive Cell Lines") +labs(fill = "75% of Cell line are Sensitive")
ggsave("~/output/pancreas_cancer/limma_res/220602_ggplot_limma_candidates_prism_screen1_sensitive_cell_lines.png")
```



```{r}
drug_list <- as.vector(unique(primary_paad_res$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res$Sensitive[primary_paad_res$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
```


```{r}
limma_PRISM_test<- PRISM_testing(101,"YAPC", lincs_limma_pancreas_res_YAPC_top_fda$pert, drug_senstive_precentage_all_drugs)
```
```{r}
limma_PRISM_test
```

```{r}
table(lincs_limma_pancreas_res_YAPC_top_fda$clinical_trial_PAAD)
```


```{r}
limma_CT_test_res <- clinical_trial_testing(101, "YAPC", 39, 0.07692308, clinical_trial_PAAD)
```

```{r}
limma_CT_test_res
```


#### Transfer Learning

```{r eval= FALSE}
recount3_plier_paad <- readRDS("~/data/recount3_plier_paad.rds")
```
```{r eval= FALSE}
source("~/script/plier_util.R")
```

```{r eval= FALSE}
#There is a issue with handling genes with zero expression. Best thing to do is to remove the genes
test <- GetOrderedRowNorm(as.matrix(tpm_table),recount3_plier_paad )
zeros<- rownames(test)[!complete.cases(test)]
tpm_table_v2<- tpm_table[!rownames(tpm_table) %in% zeros,]
```

create the b.matrix 
```{r eval= FALSE}
PAAD.GTEx.b.matrix <- GetNewDataB(as.matrix(tpm_table_v2), recount3_plier_paad)
```

```{r eval=FALSE}
saveRDS(PAAD.GTEx.b.matrix, file= "~/output/pancreas_cancer/TFL_res/PAAD_GTEX_B_MATRIX.rds")
```


```{r eval= FALSE}
TestLVDifferencesJLF <- function(b.matrix, phenotype, blocking,
                              use.bonferroni = FALSE) {
  # This function tests for differential expression of PLIER-derived latent
  # variables between groups specified by the phenotype argument
  # using limma. Examples include different disease groups or disease v. 
  # control. It takes the B matrix from a PLIER model and a factor vector with 
  # the group labels. It will reorder the phenotype vector if control.phenotype
  # is specified. The resulting p-values are Benjamini-Hochberg corrected by 
  # default or Bonferroni corrected if use.bonferroni = TRUE
  # 
  # Args:
  #   b.matrix: a B matrix (latent variables are rows, samples are columns) 
  #             from a PLIER model. Can be the B element of the list 
  #             returned by PLIER::PLIER or the output of GetNewDataB
  #   phenotype: a named factor vector that contains group labels to be used
  #              for contrasts
  #   blocking: a names facotor vector that contains group labels to be used for blocking
  #   use.bonferroni: logical - should bonferroni correction be used? if FALSE
  #                   (default), will use "BH"
  #   
  # Returns:
  #   A limma::topTable, where the first column is the latent variable name and
  #   all pathways are returned (without filtering or sorting)
  
  ## error-handling ##
  
  if (is.null(names(phenotype))) {
    stop("phenotype should be a named factor vector -- the names ensure that
         the vector is correctly ordered")
  }
  if (is.null(names(blocking))) {
    stop("blocking should be a named factor vector -- the names ensure that
         the vector is correctly ordered")
  }  
  # no names should be "missing"
  check.names <- all(colnames(b.matrix) %in% names(phenotype)) & 
    all(names(phenotype) %in% colnames(b.matrix)) 
  
  if (!check.names) {
    stop("Some sample(s) is missing from colnames(b.matrix) or 
         names(phenotype)")
  }
  
  # the phenotype labels should be in the same order as the b.matrix samples
  ordered.phenotype <- as.factor(phenotype[colnames(b.matrix)])
  
  # the blocking labels should be in the same order as the b.matrix samples
  ordered.blocking <- as.factor(blocking[colnames(b.matrix)])
  
  # get contrasts (all pairwise)  
  num.levels <- length(levels(ordered.phenotype))
  contrast.vector <- c()
  for (lvl in levels(ordered.phenotype)[1:(num.levels - 1)]) {
    for (lvl.2 in levels(ordered.phenotype)[2:num.levels]) {
      if (lvl != lvl.2) {
        contrast.vector <- append(contrast.vector, paste(lvl, lvl.2, sep = "-"))
      }
    }
  }
  contrast.vector <- paste(contrast.vector, collapse = ", ")
  
  # prep design matrix
  design <- model.matrix(~ 0+ ordered.phenotype+ ordered.blocking )
  colnames(design)[seq_len(nlevels(ordered.phenotype))] <- levels(ordered.phenotype)
  
  
  
  
  #colnames(design) <- levels(ordered.phenotype)
  
  # fit linear model
  fit <- limma::lmFit(b.matrix, design)
  contrast.matrix <-
    eval(parse(
      text = paste0(
        'limma::makeContrasts(', contrast.vector, ', levels = design)')))
  fit2 <- limma::contrasts.fit(fit, contrast.matrix)
  fit2 <- limma::eBayes(fit2)
  
  # extract results as a data.frame
  if (use.bonferroni) {  # if specified, use Bonferroni correction
    limma.result <- limma::topTable(fit2, number = nrow(b.matrix),
                                    adjust.method = "bonferroni", 
                                    sort.by = "none")
  } else {  # calculate FDR
    limma.result <- limma::topTable(fit2, number = nrow(b.matrix),
                                    adjust.method = "BH", sort.by = "none")
  }
  
  # want feature (latent variable) names as column
  limma.result <- tibble::rownames_to_column(limma.result, var = "LV")
  
  return(limma.result)
  
}
```



```{r}
LVTestWrapperJLF <- function(b.matrix,
                          sample.info.df,
                          phenotype.col,
                          blocking,
                          file.lead,
                          plot.dir = "plots",
                          results.dir = "results",
                          use.bonferroni = FALSE,
                          significant.only = FALSE,
                          sig.threshold = 0.05) {
  # A wrapper function for TestLVDifferences and BoxplotDiffLV; does the 
  # reshaping required for plotting. Produces the following files: 1) tsv of the
  # differential expression results 2) a long form of the B matrix joined with
  # the sample information (sample.info.df) and 3) a PDF of boxplots
  # 
  # Args:
  #   b.matrix: a B matrix (latent variables are rows, samples are columns) 
  #             from a PLIER model. Can be the B element of the list 
  #             returned by PLIER::PLIER or the output of GetNewDataB
  #   sample.info.df: a long form data.frame that contains sample information,
  #                   sample names that match the B matrix sample identifiers
  #                   must be in a "Sample" column & it also must contain
  #                   the factor to group by for testing differential expression
  #                   (DE) and plotting
  #   phenotype.col: the column name of the column in sample.info.df to be used
  #                  for DE and plotting; character
  #   file.lead: string that designates the "beginning" of filenames
  #   plot.dir: plot directory where the boxplots PDF should be saved
  #   results.dir: results directory for DE results and reshaped B data.frame
  #   use.bonferroni: logical - should bonferroni correction be used for DE? 
  #                   if FALSE (default), will use "BH"
  #   significant.only: logical - should only differentially expressed LVs be
  #                     plotted? if FALSE (default), all will be plotted
  #   sig.threshold: the adj. P cutoff to be used if only plotting significant 
  #                  results; default is 0.05
  #                  
  # Returns:
  #   A list with the following elements
  #       limma: the results from TestLVDifferences 
  #       b.df: sample.b.df, prior to any filtering for plotting (if applicable)
  # 
  #   the following files are written by this function (see above):
  #     1) <results.dir>/<file.lead>_LV_limma_results.tsv
  #     2) <results.dir>/<file.lead>_B_long_sample_info.tsv
  #     3) <plot.dir>/<file.lead>_LV_boxplots.pdf
  
  `%>%` <- dplyr::`%>%`
  
  # error-handling
  # we need to join by "Sample" column for boxplots
  if (!("Sample" %in% colnames(sample.info.df))) {
    stop("'Sample' must be a column in sample.info.df")
  }
  # phenotype.col needs to be in column names
  if (!(phenotype.col %in% colnames(sample.info.df))) {
    stop("phenotype.col must be a column name in sample.info.df")
  }
  
  # initialize list to hold results to be returned
  return.list <- list()
  
  #### Differential Expression ####
  # get the named vector to use as the phenotype for testing differential 
  # expression
  phenotype.vector <- as.factor(make.names(sample.info.df[[phenotype.col]]))
  names(phenotype.vector) <- sample.info.df$Sample
  # test itself
  limma.df <- TestLVDifferencesJLF(b.matrix = b.matrix,
                                phenotype = phenotype.vector,
                                blocking= blocking,
                                use.bonferroni = use.bonferroni)
  # write to file
  dlve.file <- file.path(results.dir, 
                         paste0(file.lead, "_LV_limma_results.tsv"))
  readr::write_tsv(limma.df, path = dlve.file)
  # add to list to be returned
  return.list[["limma"]] <- limma.df
  
  #### Reshape & join with sample information ####
  b.df <- reshape2::melt(b.matrix)
  colnames(b.df) <- c("LV", "Sample", "Value")
  sample.b.df <- dplyr::inner_join(b.df, sample.info.df, by = "Sample")
  long.file <- file.path(results.dir, 
                         paste0(file.lead, "_B_long_sample_info.tsv"))
  readr::write_tsv(sample.b.df, long.file)
  # add to list to be returned
  return.list[["b.df"]] <- sample.b.df
  
  #### Plotting ####
  plot.file <- file.path(plot.dir,
                         paste0(file.lead, "_LV_boxplots.pdf"))
  
  # if we only want significant LVs plotted, filter sample.b.df using the
  # adj.P.Val cutoff sig.threshold
  if (significant.only) {
    sig.lvs <- limma.df$LV[which(limma.df$adj.P.Val < sig.threshold)]
    sample.b.df <- sample.b.df %>%
      dplyr::filter(LV %in% sig.lvs)
  }
  
  BoxplotDiffLV(tidy.b.df = sample.b.df, 
                phenotype.column = phenotype.col,
                pdf.path = plot.file)
  
  
  return(return.list)
}
```

```{r eval= FALSE}
source("~/script/test_LV_differences.R")
library(dplyr)
```


LVTestWrapperJLF <- function(b.matrix,
                          sample.info.df,
                          phenotype.col,
                          blocking,
                          file.lead,
                          plot.dir = "plots",
                          results.dir = "results",
                          use.bonferroni = FALSE,
                          significant.only = FALSE,
                          sig.threshold = 0.05)
```{r eval= FALSE}
sampleinfo<- cbind(colnames(PAAD.GTEx.b.matrix), as.character(all_metadata_v3$status), as.character(all_metadata$database))
colnames(sampleinfo) <- c("Sample", "Tumor","database")
sampleinfo<- as.data.frame(sampleinfo)
database<- all_metadata_v3$database
names(database)<- colnames(PAAD.GTEx.b.matrix)

LV_test_TCGA_BH <- LVTestWrapperJLF(b.matrix=PAAD.GTEx.b.matrix , sample.info.df= sampleinfo, phenotype.col= "Tumor", blocking= database, file.lead= "LV_TCGA_GTEX_T_vs_NT_PAAD", plot.dir= "~/output/pancreas_cancer/TFL_res/", results.dir= "~/output/pancreas_cancer/TFL_res/", use.bonferroni= FALSE, sig.threshold = 0.05)
```

```{r eval=FALSE}
saveRDS(LV_test_TCGA_BH , file= "~/output/pancreas_cancer/TFL_res/PAAD_GTEX_limma_TFL_res.rds")
```
```{r eval=FALSE}
saveRDS(all_metadata_v3 , file= "~/output/pancreas_cancer/TFL_res/PAAD_GTEX_metadata.rds")
```

are genes and heatmaps and pathway analysis

```{r eval= FALSE}
sig_LVs <- LV_test_TCGA_BH$limma[LV_test_TCGA_BH$limma$adj.P.Val < 0.05,]
```
```{r}
hist(LV_test_TCGA_BH$limma$logFC)
```
going with .10 for this analysis 

```{r eval= FALSE}
sig_LVs <- LV_test_TCGA_BH$limma[LV_test_TCGA_BH$limma$adj.P.Val < 0.05 & abs(LV_test_TCGA_BH$limma$logFC) > .1 ,]
```

```{r}
SIG_LVs <- sig_LVs$LV
```

```{r}
SIG_LVs
```

plot latent variable heatmap 
Latent Variable heatmap 
```{r}
library(ComplexHeatmap)
library(dplyr)
library(gplots)
library(circlize)
```
```{r}
PAAD_GTEX_B_MATRIX <- readRDS("~/output/pancreas_cancer/TFL_res/PAAD_GTEX_B_MATRIX.rds")
```

```{r}
colSideColors<- ifelse(all_metadata_v3$status =="Primary Tumor","#440154FF","#228C8DFF" )
PAAD_GTEX_B_MATRIX_SIG<- PAAD_GTEX_B_MATRIX [rownames(PAAD_GTEX_B_MATRIX ) %in% SIG_LVs, ]
heatmap.2(x=PAAD_GTEX_B_MATRIX_SIG, hclustfun=function(d) hclust(d, method="ward.D2"), labCol = FALSE, trace="none",ColSideColors=colSideColors, col=colorRampPalette(colors=c("blue", "black", "yellow")),cexRow= .5, dendrogram="both", cexCol = 0.5,main = "Significant Latent Varibles")

```
```{r}
column_ha = HeatmapAnnotation(Sample=all_metadata_v3$status, col = list(Sample = c("Primary Tumor" = "#440154FF", "Solid Tissue Normal" = "#228C8DFF")))
col_fun = colorRamp2(c(-1, 0, 1), c("blue", "black", "yellow"))
Heatmap(PAAD_GTEX_B_MATRIX_SIG, nam= "LV Score",  col = col_fun, show_column_names = FALSE, clustering_distance_rows= "euclidean",
             clustering_distance_columns=  "euclidean",
             clustering_method_rows = "ward.D2" ,
             clustering_method_columns="ward.D2", top_annotation = column_ha, row_names_gp = gpar(fontsize = 8))
```



```{r}
sig_Z_mt <- recount3_plier_paad$Z[,LV_test_TCGA_BH$limma$adj.P.Val < 0.05 & abs(LV_test_TCGA_BH$limma$logFC)> .1 ]
colnames(sig_Z_mt) <- SIG_LVs
```


top 100 
```{r}
topgene_1 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,1])][1:30]
topgene_2 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,2])][1:30]
topgene_3 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,3])][1:30]
topgene_4 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,4])][1:30]
topgene_5 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,5])][1:30]
topgene_6 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,6])][1:30]
topgene_7 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,7])][1:30]
topgene_8 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,8])][1:30]
topgene_9 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,9])][1:30]
topgene_10 <- rownames(sig_Z_mt)[order(-sig_Z_mt[,10])][1:30]
```

```{r}
topgenes<- unique(c(topgene_1, topgene_2,topgene_3, topgene_4, topgene_5, topgene_6, topgene_7, topgene_8, topgene_9, topgene_10))
```


```{r}
deseq2_paad_tfl <- deseq2_paad_normal[deseq2_paad_normal$Symbol %in% topgenes,]
```


```{r}
downset<- deseq2_paad_tfl$Symbol[deseq2_paad_tfl$log2FoldChange < 0]
upset<- deseq2_paad_tfl$Symbol[deseq2_paad_tfl$log2FoldChange > 0]
```



```{r}
upset_v2<- c()
for (i in 1:length(upset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    upset_v2[i]<- gene_info_LINCS$gene_id[upset[i] == gene_info_LINCS$gene_symbol]
  }else{
    upset_v2[i]<- NA
  }
  
}
names(upset_v2)<- upset
```

```{r}
downset_v2<- c()
for (i in 1:length(downset)){
  possibleError <- tryCatch(
      gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol],
      error=function(e) e
  )
  if(length(possibleError)> 0){
    #REAL WORK
    downset_v2[i]<- gene_info_LINCS$gene_id[downset[i] == gene_info_LINCS$gene_symbol]
  }else{
    downset_v2[i]<- NA
  }
  
}
names(downset_v2)<- downset
```

```{r}
downset_v2<- downset_v2[complete.cases(downset_v2)]
upset_v2<- upset_v2[complete.cases(upset_v2)]
```

```{r}
#double check that they didn't overlap 
 intersect(downset_v2, upset_v2)
```

```{r}
length(downset_v2)
length(upset_v2)
```

```{r}
names(upset_v2)<- NULL
names(downset_v2)<- NULL
```

```{r}
tfl_paad_list<- list(up= upset_v2, down= downset_v2)
```

```{r}
saveRDS(tfl_paad_list,"~/output/pancreas_cancer/TFL_res/SR_gene_list_paad_tfl.rds")
```


```{r}
set.seed(101)
qsig_lincs_tfl_pancreas_res <- qSig(query=list(upset=as.character(upset_v2), downset=as.character(downset_v2)), 
                   gess_method="LINCS", refdb=db_path)
```


```{r}
set.seed(101)
library(parallel)
lincs_tfl_pancreas <- gess_lincs(qsig_lincs_tfl_pancreas_res, sortby="NCS", tau=FALSE)
#result(lincs)
```



```{r}
lincs_tfl_pancreas_res <- result(lincs_tfl_pancreas)
```

```{r}
write.csv(lincs_tfl_pancreas_res, file= "~/output/pancreas_cancer/220601_SR_LINCS_PANCREAS_TFL_RES.csv" )
```

```{r}
lincs_tfl_pancreas_res_YAPC <- lincs_tfl_pancreas_res[lincs_tfl_pancreas_res$cell == "YAPC",]
```
tau 


```{r}
tau_test<- tau_scores(lincs_tfl_pancreas_res_YAPC, YAPC_taudf)
```

```{r}
lincs_tfl_pancreas_res_YAPC$jlf_tau<- tau_test
```

```{r}
write.csv(lincs_tfl_pancreas_res_YAPC, file= "~/output/pancreas_cancer/TFL_res/220601_lincs_tfl_pancreas_res_YAPC_tau.csv" )
```

```{r}
lincs_tfl_pancreas_res_YAPC_top <- lincs_tfl_pancreas_res_YAPC[lincs_tfl_pancreas_res_YAPC$NCS < 0 & lincs_tfl_pancreas_res_YAPC$WTCS_FDR < 0.05 & lincs_tfl_pancreas_res_YAPC$jlf_tau< -80,]
```

clinical trials

```{r}
lincs_tfl_pancreas_res_YAPC_top<- lincs_tfl_pancreas_res_YAPC_top[complete.cases(lincs_tfl_pancreas_res_YAPC_top),]
lincs_tfl_pancreas_res_YAPC_top$fda_approved<- FDA_APPROVAL_CHECK(lincs_tfl_pancreas_res_YAPC_top$pert)
```


```{r}
lincs_tfl_pancreas_res_YAPC_top$clinical_trial_PAAD <- clinical_trial_check(lincs_tfl_pancreas_res_YAPC_top$pert, clinical_trial_PAAD)
```


```{r}
lincs_tfl_pancreas_res_YAPC_top_fda<- lincs_tfl_pancreas_res_YAPC_top[lincs_tfl_pancreas_res_YAPC_top$fda_approved== TRUE,]
#lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD<- ifelse(lincs_deseq_paad_res_YAPC_top_fda$clinical_trial_PAAD, "star", "")

lincs_tfl_pancreas_res_YAPC_top_fda_order <- lincs_tfl_pancreas_res_YAPC_top_fda[order(-lincs_tfl_pancreas_res_YAPC_top_fda$NCS),]
lincs_tfl_pancreas_res_YAPC_top_fda$pert <- factor(lincs_tfl_pancreas_res_YAPC_top_fda$pert, levels = lincs_tfl_pancreas_res_YAPC_top_fda_order$pert)
p<-ggplot(data=lincs_tfl_pancreas_res_YAPC_top_fda[1:30,], aes(x=pert, y=NCS, fill=jlf_tau, shape= clinical_trial_PAAD)) +
  geom_bar(stat="identity")+ scale_fill_viridis(direction=-1) + geom_point(aes(y = NCS - 0.15), position = position_dodge(0.9), size= 4, show.legend = TRUE)
p + coord_flip()  + ylab("Normalized Connectivity Score") + xlab("LINCS Small Molecules") +labs(fill = "Tau [-100,100]", shape= "Clinical Trials")

ggsave("~/output/pancreas_cancer/TFL_res/220421_ggplot_tfl_tau_paad_approved_candidates.png")
```

```{r}
#lincs_deseq_paad_res_YAPC_top 
write.csv(lincs_tfl_pancreas_res_YAPC_top , file= "~/output/pancreas_cancer/TFL_res/220602_SR_LINCS_PAAD_TFL_RES_tau.csv" )
```

pathways

```{r}

hyperG_k_res <- dsea_hyperG(drugs = lincs_tfl_pancreas_res_YAPC_top_fda$pert, type = "KEGG", pvalueCutoff = 1, qvalueCutoff = 1,  minGSSize = 10, maxGSSize = 2000)
hyperG_k_res_v2<- result(hyperG_k_res)
```

```{r}
#false discovery rate
hyperG_k_res_v2$logqvalue<- -log(hyperG_k_res_v2$qvalue)
```

```{r}
hyperG_k_res_v2$Description<- factor(hyperG_k_res_v2$Description, levels= hyperG_k_res_v2$Description)
```

```{r}
gbm.2<-ggplot(data=hyperG_k_res_v2[1:30,] , aes(x=Description, y=Count, fill=logqvalue )) +
  geom_bar(stat="identity") + scale_fill_viridis()
gbm.2 + coord_flip() + ylab("Number of Drugs") + xlab("KEGG Pathways") +labs(fill = "-log(q-value)")
```


```{r}
write.csv(hyperG_k_res_v2 , file= "~/output/pancreas_cancer/TFL_res/220602_SR_LINCS_PAAD_TFL_PATHWAY.csv" )
```




PRISM

```{r}
primary_paad_res_sub <-primary_paad_res[ primary_paad_res$Var2 %in% lincs_tfl_pancreas_res_YAPC_top_fda$pert,]
```


```{r}
write.csv(primary_paad_res_sub , file= "~/output/pancreas_cancer/TFL_res/220602_prism_tfl_candidates.csv" )
```

```{r}
#primary_paad_res_sub$Var2 <- factor(primary_paad_res_sub$Var2, levels=unique(primary_paad_res_sub$Var2))
primary_paad_res_sub$Var2 <- factor(primary_paad_res_sub$Var2, levels=unique(primary_paad_res_sub$Var2[order(primary_paad_res_sub$log_fold_change)]))
ggplot(primary_paad_res_sub, aes(x=log_fold_change, y= Var2))+ geom_violin() +geom_vline(xintercept = 0.3)  + ylab("Drug Candidates") + xlab("log fold change")
ggsave("~/output/pancreas_cancer/TFL_res/220602_ggplot_TFL_candidates_prism_screen1.png")
```

```{r}
drug_list <- as.vector(unique(primary_paad_res_sub$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res_sub$Sensitive[primary_paad_res_sub$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
drug_senstive_precentage_all_drugs$drug_list<- factor(drug_senstive_precentage_all_drugs$drug_list, levels= unique(drug_senstive_precentage_all_drugs$drug_list[order(drug_senstive_precentage_all_drugs$drug_fraction)]))
ggplot(drug_senstive_precentage_all_drugs, aes( drug_fraction, drug_list, fill= test ))+ geom_bar(stat="identity") + scale_fill_viridis_d() + ylab("Drug Candidates") + xlab("Fraction of Sensitive Cell Lines") +labs(fill = "75% of Cell line are Sensitive")
ggsave("~/output/pancreas_cancer/TFL_res/220602_ggplot_TFL_candidates_prism_screen1_sensitive_cell_lines.png")
```
LINCS pathway & Drug targets


```{r}
#drug_analysis(drug_name, target_list,  tpm_df, sample_vector, deseq_results, se, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/deseq2_res/220602_candidate_plot/")

drug_analysis( "dabrafenib", c("BRAF" , "RAF1", "SIK1", "NEK11", "LIMK1"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "toremifene", c("ESR1" , "SHBG"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "trametinib", c("MAP2K1" , "MAP2K2"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "atorvastatin", c("HMGCR" , "DPP4", "AHR", "HDAC2", "NR1I3"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "sirolimus", c("MTOR"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "trifluoperazine", c("DRD2", "CALY", "ADRA1A", "CALM1", "TNNC1", "S100A4"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "selumetinib", c("MAP2K1", "MAP2K2"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "simvastatin", c("HMGCR", "ITGAL", "HDAC2"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "itraconazole", c("ERG11", "CYP51A1"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")

drug_analysis( "erlotinib", c("NR1I2", "EGFR"),  tpm_df, all_metadata_v3$status , deseq2_paad_normal, se= se_asssay, cell_lincs= "__PAAD__trt_cp", "~/output/pancreas_cancer/TFL_res/220602_candidate_plot")
```


```{r}
drug_list <- as.vector(unique(primary_paad_res$Var2))
drug_fraction<- c()
for (i in 1:length(drug_list)){
  cells <-primary_paad_res$Sensitive[primary_paad_res$Var2 %in% drug_list[i]]
  cells<- cells[!is.na(cells)]
  if( length(cells) < 12){
    print(drug_list[i])
  }
  #x<- table(cells)
  drug_fraction[i] <- length(cells[cells== TRUE])/ length(cells)
}
test <- ifelse(drug_fraction > 0.75, TRUE, FALSE)
drug_senstive_precentage_all_drugs <- data.frame(drug_fraction, drug_list, test)
```

```{r}
tfl_PRISM_test<- PRISM_testing(101,"YAPC", lincs_tfl_pancreas_res_YAPC_top_fda$pert, drug_senstive_precentage_all_drugs)
```

```{r}
tfl_PRISM_test
```

```{r}
table(lincs_tfl_pancreas_res_YAPC_top_fda$clinical_trial_PAAD)
```

```{r}
tfl_CT_test_res <- clinical_trial_testing(101, "YAPC", 30, 0.2333333, clinical_trial_PAAD)
```

```{r}
tfl_CT_test_res
```


compare gene list across the different methods
```{r}
library(VennDiagram)
```
```{r}
# Prepare a palette of 3 colors with R colorbrewer:
myCol <- c("#440154FF" , "#31688EFF" ,"#35B779FF")
```
```{r}
venn_dia_methods <- function(limma_list, deseq2_list, tfl_list, file_name='~/output/liver_cancer/SR_liver_all_gene_venn_diagram.png' ){
venn.diagram(
        x = list(limma_list, deseq2_list, tfl_list),
        category.names = c("limma" , "DESeq2" , "Transfer Learning"),
        filename = file_name,
        output=TRUE,
        
        # Output features
        imagetype="png" ,
        height = 1000 , 
        width = 1000 , 
        resolution = 300,
        compression = "lzw",
        
        # Circles
        lwd = 2,
        lty = 'blank',
        fill = myCol,
        
        # Numbers
        cex = .4,
        fontface = "bold",
        fontfamily = "sans",
        
        # Set names
        cat.cex = 0.3,
        cat.fontface = "bold",
        #cat.default.pos = "outer",
        cat.pos = c(-27, 27, 135),
        cat.dist = c(0.04, 0.04, 0.04),
        cat.fontfamily = "sans",
        rotation = 1
)
}
```

```{r}
venn_dia_methods(limma_paad_list$up, deseq_paad_list$up, tfl_paad_list$up, file_name='~/output/pancreas_cancer/SR_up_genes_venn_diagram.png' )
```

```{r}
venn_dia_methods(limma_paad_list$down, deseq_paad_list$down, tfl_paad_list$down, file_name='~/output/pancreas_cancer/SR_down_genes_venn_diagram.png' )
```

```{r}
venn_dia_methods(unlist(limma_paad_list), unlist(deseq_paad_list), unlist(tfl_paad_list), file_name='~/output/pancreas_cancer/SR_all_genes_venn_diagram.png' )
```


```{r}
method_up_down_gene_set_analysis<- function(up, down,result_path, method, name){
  library(gprofiler2)
  downset_pathway_results <- gost(query = down, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  downset_pathway_results<- downset_pathway_results$result
  
  upset_pathway_results <- gost(query = up, 
                organism = "hsapiens", ordered_query = TRUE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
  upset_pathway_results<- upset_pathway_results$result
  
  pathway_results<- rbind(upset_pathway_results, downset_pathway_results)
  pathway_results$set<- c(rep("Up", nrow(upset_pathway_results)), rep("Down", nrow(downset_pathway_results)))
  file_name<- paste0(result_path, "/", method, "_pathways.csv")
  write.csv2(as.data.frame(pathway_results[,-14]), file_name )
  
  file_name<- paste0(result_path, "/", method, "_pathways.png")
  
  #making adjustments here
  #pathway_results$set <- factor(pathway_results$set, levels = c("up", "down"))
  if(nrow(pathway_results)<50){
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value))+geom_tile()+scale_fill_viridis(direction=-1)+theme_classic()+ labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
    
  }else{
    pathway_results<- pathway_results[pathway_results$source %in% c("KEGG","REAC","GO:MF" ),]
    ggplot(pathway_results, aes(x=set, y=term_name, fill=p_value)) + geom_tile()+ scale_fill_viridis(direction=-1)+ theme_classic() + labs(title=name,x="Drug Gene Sets", y = "g:Profiler Gene Sets", fill= "p-value")
  }
  ggsave(file_name, width = 12, height = 14)
  return(as.data.frame(pathway_results[,-14]))
}
```

```{r}
limma_paad_pathway_res <- method_up_down_gene_set_analysis(limma_paad_list$up, limma_paad_list$down, "~/output/pancreas_cancer/", "limma", "PAAD_cancer_limma_input_genes_SR")
```

```{r}
deseq2_paad_pathway_res<- method_up_down_gene_set_analysis(deseq_paad_list$up, deseq_paad_list$down, "~/output/pancreas_cancer/", "DESEq2", "PAAD_cancer_deseq2_input_genes_SR")
```

```{r}
tfl_paad_pathway_res<- method_up_down_gene_set_analysis(tfl_paad_list$up, tfl_paad_list$down, "~/output/pancreas_cancer/", "TFL", "PAAD_cancer_tfl_input_genes_SR")
```


```{r}
limma<- limma_paad_pathway_res$term_id[ limma_paad_pathway_res$set == "Up"]
deseq2<- deseq2_paad_pathway_res$term_id[ deseq2_paad_pathway_res$set == "Up"]
tfl<-tfl_paad_pathway_res$term_id[ tfl_paad_pathway_res$set == "Up"]
venn_dia_methods(limma, deseq2, tfl, file_name='~/output/pancreas_cancer/SR_PAAD_Up_pathway_venn_diagram.png' )
```

```{r}
limma<- limma_paad_pathway_res$term_id[ limma_paad_pathway_res$set == "Down"]
deseq2<- deseq2_paad_pathway_res$term_id[ deseq2_paad_pathway_res$set == "Down"]
tfl<-tfl_paad_pathway_res$term_id[ tfl_paad_pathway_res$set == "Down"]
venn_dia_methods(limma, deseq2, tfl, file_name='~/output/pancreas_cancer/SR_PAAD_Down_pathway_venn_diagram.png' )
```

```{r}
limma<- limma_paad_pathway_res$term_id
deseq2<- deseq2_paad_pathway_res$term_id
tfl<-tfl_paad_pathway_res$term_id
venn_dia_methods(limma, deseq2, tfl, file_name='~/output/pancreas_cancer/SR_PAAD_all_pathway_venn_diagram.png' )
```


```{r}

lincs_deseq_gbm_res_YAPC_fda_approved <- read_csv("~/output/pancreas_cancer/deseq2_res/220602_SR_LINCS_PAAD_DESEQ2_RES_tau.csv")
lincs_deseq_gbm_res_YAPC_fda_approved<- lincs_deseq_gbm_res_YAPC_fda_approved[lincs_deseq_gbm_res_YAPC_fda_approved$fda_approved == TRUE,]

lincs_limma_gbm_res_YAPC_fda_approved <- read_csv("~/output/pancreas_cancer/limma_res/220602_SR_LINCS_PAAD_limma_RES_tau.csv")
lincs_limma_gbm_res_YAPC_fda_approved<- lincs_limma_gbm_res_YAPC_fda_approved[lincs_limma_gbm_res_YAPC_fda_approved$fda_approved ==TRUE, ]

lincs_tfl_gbm_res_YAPC_fda_approved <- read_csv("~/output/pancreas_cancer/TFL_res/220602_SR_LINCS_PAAD_TFL_RES_tau.csv")
lincs_tfl_gbm_res_YAPC_fda_approved<- lincs_tfl_gbm_res_YAPC_fda_approved[ lincs_tfl_gbm_res_YAPC_fda_approved$fda_approved ==TRUE,]
```

```{r}
venn_dia_methods(lincs_limma_gbm_res_YAPC_fda_approved$pert, lincs_deseq_gbm_res_YAPC_fda_approved$pert, lincs_tfl_gbm_res_YAPC_fda_approved$pert, file_name='~/output/pancreas_cancer/SR_drug_candidates_venn_diagram.png' )
```








