---
title: "220728_plier_recount3_wo_gtex_tcga"
author: "Jennifer Fisher"
date: "7/28/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# START 
    Goal/Purpose of operations: 
    Conducting Dimension reduction for Transfer learning with PLIER without GTEx and TCGA data
    
    Finished psedocode on: Date
    220727
    
    System which operations were done on:
    my laptop(on cheaha)
    
    GitHub Repo:
    Transfer_Learning_R03
    
    Docker/Singularity: 
    rstudio_tf_dr_v3
    
    Directory of operations: 
    /data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03
    
    Scripts being edited for operations:
    NA
    
    Data being used:
    recount3- tpm normalized
    recount3 is an online resource consisting of RNA-seq gene, exon, and exon-exon junction counts as well as coverage bigWig files for 8,679 and 10,088 different studies for human and mouse respectively. It is the third generation of the ReCount project and part of recount.bio.
    http://rna.recount.bio/
    ./data/recount3
    
    Papers and tools: 
    recount3- see details above 
    PLIER and MultiPLIER wrapper functions for PLIER

# STEPS
### Set working directory 
/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03

### load in data
create a dataframe with all the tpm values. then remove the indidivudal groups of recount3 samples
```{r eval=FALSE}
recount3_group1_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group1_tpm.rds")
recount3_group2_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group2_tpm.rds")
recount3_group3_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group3_tpm.rds")
recount3_group4_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group4_tpm.rds")
recount3_group5_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group5_tpm.rds")
recount3_group6_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group6_tpm.rds")
recount3_group7_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group7_tpm.rds")
recount3_group8_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group8_tpm.rds")
recount3_group9_tpm <- readRDS("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_group9_tpm.rds")
```

```{r eval=FALSE}
recount3_tpm <- cbind(recount3_group1_tpm, recount3_group2_tpm, recount3_group3_tpm, recount3_group4_tpm, recount3_group5_tpm, recount3_group6_tpm, recount3_group7_tpm, recount3_group8_tpm, recount3_group9_tpm)
```

```{r eval=FALSE}
rm(recount3_group1_tpm, recount3_group2_tpm, recount3_group3_tpm, recount3_group4_tpm, recount3_group5_tpm, recount3_group6_tpm, recount3_group7_tpm, recount3_group8_tpm, recount3_group9_tpm)
gc()
```

remove Na from data

```{r eval=FALSE}
dim(recount3_tpm[1:4,is.na(recount3_tpm[1,])])
```
[1]   4 262
```{r eval=FALSE}
recount3_tpm<- recount3_tpm[,! is.na(recount3_tpm[1,])]
```


```{r}
#recount3_tpm<- as.data.frame(recount3_tpm)
#gc()
```

### Analysis
```{r}
library(PLIER)
library(recount3)
```
load in the functions for dimension reduction step of transfer learning  
```{r}
source("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/script/plier_util.R")
source("/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/script/functions_cancer_signature_reversion_JLF.R")
```


```{r eval=FALSE}
human_samples<- available_samples()
```
```{r eval=FALSE}
human_projects<- available_projects()
```
```{r eval=FALSE}
#SRP118922
test<- create_rse(human_projects[(human_projects$project == "DRP000987"),])
```
```{r eval=FALSE}
gene_info <- test@rowRanges
rm(test)
```


```{r eval=FALSE}
table(human_samples$project_home)
```
data_sources/gtex  data_sources/sra data_sources/tcga 
            19214            316443             11348 

262 was removed for NAs; 316181 should be the total


```{r eval=FALSE}
human_samples_not_gtex_tcga <- human_samples$external_id[ human_samples$project_home == "data_sources/sra" ]

```


```{r eval=FALSE}
recount3_wo_tpm <- recount3_tpm[, colnames(recount3_tpm) %in% human_samples_not_gtex_tcga]
```

```{r eval=FALSE}
dim(recount3_wo_tpm )
```
[1]  63856 316181

```{r eval=FALSE}
rm(human_samples, human_samples_not_gtex_tcga, recount3_tpm)
gc()
```

add gene names from recount3 and make the data frame into a matrix 
```{r eval=FALSE}
recount3_wo_tpm<- as.matrix(recount3_wo_tpm)
rownames(recount3_wo_tpm) <- gene_info$gene_name
```

Apply the PLIERNewData from multiplier but with the adjustments from Jen
```{r eval=FALSE}
recount3_plier_wo <- PLIERNewData_JLF(recount3_wo_tpm)

saveRDS(recount3_plier_wo, "/data/project/lasseigne_lab/JLF_scratch/Transfer_Learning_R03/data/recount3/recount3_plier_wo.rds")
```
## Output from PLIER
[1] "combine the pathway data from PLIER"

[1] " row normalize"

[1] "num.pc"

[1] "matrix" "array" 

[1]   6379 316181

Warning in if ((class(data) != "list") & (class(data) != "rsvd")) { :
  the condition has length > 1 and only the first element will be used

Computing svd

[1] "PLIER main function"

Selecting common genes: 6379

Removing 5 pathways with too few genes

Computing SVD

Using rsvd

Done

[1] 854.637

[1] "L2 is set to 854.636965350575"

[1] "L1 is set to 427.318482675288"

errorY (SVD based:best possible) = 0.8243

iter1 errorY= 0.9986, Bdiff= 418600, Bkappa=47.66

iter2 errorY= 0.9217, Bdiff= 0.8404, Bkappa=192.8

iter3 errorY= 0.8505, Bdiff= 0.2483, Bkappa=144

iter4 errorY= 0.8187, Bdiff= 0.08981, Bkappa=84.92

iter5 errorY= 0.7975, Bdiff= 0.04308, Bkappa=59.25

iter6 errorY= 0.7841, Bdiff= 0.02169, Bkappa=49.93

iter7 errorY= 0.7765, Bdiff= 0.01177, Bkappa=41.33

iter8 errorY= 0.7722, Bdiff= 0.007461, Bkappa=37.8

iter9 errorY= 0.7695, Bdiff= 0.005535, Bkappa=33.96

iter10 errorY= 0.7675, Bdiff= 0.004499, Bkappa=32.64

iter11 errorY= 0.7659, Bdiff= 0.003853, Bkappa=29.26

iter12 errorY= 0.7645, Bdiff= 0.003407, Bkappa=29.84

iter13 errorY= 0.7632, Bdiff= 0.003095, Bkappa=28.48

iter14 errorY= 0.762, Bdiff= 0.002878, Bkappa=26.68

iter15 errorY= 0.7609, Bdiff= 0.002725, Bkappa=26.4

iter16 errorY= 0.7598, Bdiff= 0.002607, Bkappa=27.73

iter17 errorY= 0.7588, Bdiff= 0.002508, Bkappa=27.36

iter18 errorY= 0.7578, Bdiff= 0.002414, Bkappa=27.72

iter19 errorY= 0.7568, Bdiff= 0.002311, Bkappa=26.78

New L3 is 0.00193045413622771

ter20 errorY= 0.7549, prior information ratio= 0.05, Bdiff= 0.002872, Bkappa=25.27;pos. col. U=285

iter21 errorY= 0.7538, prior information ratio= 0.06, Bdiff= 0.002511, Bkappa=25.74;pos. col. U=277

iter22 errorY= 0.7529, prior information ratio= 0.07, Bdiff= 0.002228, Bkappa=26.06;pos. col. U=265

iter23 errorY= 0.7521, prior information ratio= 0.08, Bdiff= 0.00199, Bkappa=26.19;pos. col. U=263

iter24 errorY= 0.7514, prior information ratio= 0.08, Bdiff= 0.001785, Bkappa=26.71;pos. col. U=261

iter25 errorY= 0.7508, prior information ratio= 0.09, Bdiff= 0.001611, Bkappa=26.36;pos. col. U=261

iter26 errorY= 0.7502, prior information ratio= 0.09, Bdiff= 0.001469, Bkappa=25.2;pos. col. U=258

iter27 errorY= 0.7497, prior information ratio= 0.1, Bdiff= 0.001358, Bkappa=24.74;pos. col. U=256

iter28 errorY= 0.7491, prior information ratio= 0.1, Bdiff= 0.001269, Bkappa=23.7;pos. col. U=257

iter29 errorY= 0.7486, prior information ratio= 0.1, Bdiff= 0.001198, Bkappa=22.92;pos. col. U=260

iter30 errorY= 0.7482, prior information ratio= 0.11, Bdiff= 0.001146, Bkappa=22.61;pos. col. U=261

iter31 errorY= 0.7477, prior information ratio= 0.11, Bdiff= 0.001107, Bkappa=23.72;pos. col. U=259

iter32 errorY= 0.7472, prior information ratio= 0.11, Bdiff= 0.001075, Bkappa=23.47;pos. col. U=260

iter33 errorY= 0.7467, prior information ratio= 0.11, Bdiff= 0.001046, Bkappa=23.34;pos. col. U=262

iter34 errorY= 0.7463, prior information ratio= 0.12, Bdiff= 0.001015, Bkappa=23.09;pos. col. U=261

iter35 errorY= 0.7458, prior information ratio= 0.12, Bdiff= 0.0009785, Bkappa=23.03;pos. col. U=266

iter36 errorY= 0.7454, prior information ratio= 0.12, Bdiff= 0.000936, Bkappa=22.54;pos. col. U=270

iter37 errorY= 0.745, prior information ratio= 0.12, Bdiff= 0.0008886, Bkappa=22.15;pos. col. U=272

iter38 errorY= 0.7446, prior information ratio= 0.12, Bdiff= 0.0008408, Bkappa=22.12;pos. col. U=275

iter39 errorY= 0.7442, prior information ratio= 0.12, Bdiff= 0.0007957, Bkappa=21.87;pos. col. U=275

New L3 is 0.00193045413622771

iter40 errorY= 0.7438, prior information ratio= 0.13, Bdiff= 0.0007514, Bkappa=21.8;pos. col. U=278

iter41 errorY= 0.7435, prior information ratio= 0.13, Bdiff= 0.0007077, Bkappa=21.32;pos. col. U=281

iter42 errorY= 0.7431, prior information ratio= 0.13, Bdiff= 0.0006657, Bkappa=20.74;pos. col. U=281

iter43 errorY= 0.7428, prior information ratio= 0.13, Bdiff= 0.0006259, Bkappa=20.69;pos. col. U=282

iter44 errorY= 0.7425, prior information ratio= 0.13, Bdiff= 0.0005866, Bkappa=20.41;pos. col. U=282

iter45 errorY= 0.7423, prior information ratio= 0.13, Bdiff= 0.0005467, Bkappa=20.12;pos. col. U=284

iter46 errorY= 0.742, prior information ratio= 0.13, Bdiff= 0.000505, Bkappa=20.17;pos. col. U=286

iter47 errorY= 0.7418, prior information ratio= 0.13, Bdiff= 0.000462, Bkappa=20.37;pos. col. U=291

iter48 errorY= 0.7416, prior information ratio= 0.13, Bdiff= 0.0004181, Bkappa=20.44;pos. col. U=290

iter49 errorY= 0.7414, prior information ratio= 0.13, Bdiff= 0.0003755, Bkappa=19.62;pos. col. U=291

iter50 errorY= 0.7413, prior information ratio= 0.13, Bdiff= 0.0003386, Bkappa=19.86;pos. col. U=292

iter51 errorY= 0.7411, prior information ratio= 0.13, Bdiff= 0.0003085, Bkappa=20.07;pos. col. U=290

iter52 errorY= 0.741, prior information ratio= 0.13, Bdiff= 0.0002841, Bkappa=20.33;pos. col. U=290

iter53 errorY= 0.7409, prior information ratio= 0.13, Bdiff= 0.0002657, Bkappa=20.07;pos. col. U=288

iter54 errorY= 0.7408, prior information ratio= 0.13, Bdiff= 0.0002507, Bkappa=20.29;pos. col. U=290

iter55 errorY= 0.7407, prior information ratio= 0.13, Bdiff= 0.0002388, Bkappa=20.26;pos. col. U=292

iter56 errorY= 0.7406, prior information ratio= 0.13, Bdiff= 0.000228, Bkappa=20.29;pos. col. U=291

iter57 errorY= 0.7405, prior information ratio= 0.13, Bdiff= 0.0002184, Bkappa=20.56;pos. col. U=290

iter58 errorY= 0.7404, prior information ratio= 0.13, Bdiff= 0.0002079, Bkappa=20.69;pos. col. U=291

iter59 errorY= 0.7403, prior information ratio= 0.13, Bdiff= 0.0001973, Bkappa=20.87;pos. col. U=292

New L3 is 0.00218749111818289

iter60 errorY= 0.7403, prior information ratio= 0.12, Bdiff= 0.0001904, Bkappa=21.07;pos. col. U=261

iter61 errorY= 0.7403, prior information ratio= 0.13, Bdiff= 0.0001758, Bkappa=21.21;pos. col. U=244

iter62 errorY= 0.7402, prior information ratio= 0.12, Bdiff= 0.0001632, Bkappa=21.37;pos. col. U=240

iter63 errorY= 0.7402, prior information ratio= 0.12, Bdiff= 0.0001499, Bkappa=21.47;pos. col. U=236

iter64 errorY= 0.7401, prior information ratio= 0.12, Bdiff= 0.0001371, Bkappa=21.56;pos. col. U=236

iter65 errorY= 0.7401, prior information ratio= 0.12, Bdiff= 0.0001248, Bkappa=21.65;pos. col. U=235

iter66 errorY= 0.74, prior information ratio= 0.12, Bdiff= 0.0001131, Bkappa=21.93;pos. col. U=235

iter67 errorY= 0.74, prior information ratio= 0.12, Bdiff= 0.000103, Bkappa=21.98;pos. col. U=235

iter68 errorY= 0.74, prior information ratio= 0.12, Bdiff= 9.39e-05, Bkappa=21.97;pos. col. U=233

iter69 errorY= 0.7399, prior information ratio= 0.12, Bdiff= 8.599e-05, Bkappa=22.14;pos. col. U=232

iter70 errorY= 0.7399, prior information ratio= 0.12, Bdiff= 7.89e-05, Bkappa=21.96;pos. col. U=232

iter71 errorY= 0.7399, prior information ratio= 0.12, Bdiff= 7.289e-05, Bkappa=21.98;pos. col. U=232

iter72 errorY= 0.7399, prior information ratio= 0.12, Bdiff= 6.771e-05, Bkappa=21.91;pos. col. U=232

iter73 errorY= 0.7399, prior information ratio= 0.12, Bdiff= 6.312e-05, Bkappa=21.97;pos. col. U=232

iter74 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 5.905e-05, Bkappa=21.99;pos. col. U=232

iter75 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 5.523e-05, Bkappa=22.13;pos. col. U=232

iter76 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 5.227e-05, Bkappa=22.2;pos. col. U=233

iter77 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 4.874e-05, Bkappa=22.25;pos. col. U=234

iter78 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 4.576e-05, Bkappa=22.33;pos. col. U=235

iter79 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 4.309e-05, Bkappa=22.25;pos. col. U=235

New L3 is 0.00193045413622771

iter80 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 4.523e-05, Bkappa=22.49;pos. col. U=297

iter81 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 4.152e-05, Bkappa=22.64;pos. col. U=298

iter82 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 3.855e-05, Bkappa=22.67;pos. col. U=298

iter83 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 3.61e-05, Bkappa=22.72;pos. col. U=298

iter84 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 3.401e-05, Bkappa=22.71;pos. col. U=297

iter85 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 3.225e-05, Bkappa=22.78;pos. col. U=297

iter86 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 3.062e-05, Bkappa=22.83;pos. col. U=296

iter87 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.924e-05, Bkappa=22.91;pos. col. U=296

iter88 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.806e-05, Bkappa=23.24;pos. col. U=297

iter89 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.701e-05, Bkappa=23.37;pos. col. U=297

iter90 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.61e-05, Bkappa=23.39;pos. col. U=297

iter91 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.536e-05, Bkappa=23.37;pos. col. U=297

iter92 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.474e-05, Bkappa=23.4;pos. col. U=297

iter93 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.424e-05, Bkappa=23.48;pos. col. U=296

iter94 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.382e-05, Bkappa=23.56;pos. col. U=297

iter95 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.351e-05, Bkappa=23.57;pos. col. U=297

iter96 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.328e-05, Bkappa=23.64;pos. col. U=296

iter97 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.314e-05, Bkappa=23.91;pos. col. U=296

iter98 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.302e-05, Bkappa=24;pos. col. U=296

iter99 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.291e-05, Bkappa=24.13;pos. col. U=296

New L3 is 0.00218749111818289

iter100 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.694e-05, Bkappa=24.14;pos. col. U=264

iter101 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 2.44e-05, Bkappa=24.16;pos. col. U=251

iter102 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.326e-05, Bkappa=24.35;pos. col. U=246

iter103 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.268e-05, Bkappa=24.35;pos. col. U=240

iter104 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.243e-05, Bkappa=24.43;pos. col. U=240

iter105 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.236e-05, Bkappa=24.4;pos. col. U=238

iter106 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.244e-05, Bkappa=24.52;pos. col. U=237

iter107 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.266e-05, Bkappa=24.63;pos. col. U=234

iter108 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.298e-05, Bkappa=24.77;pos. col. U=233

iter109 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.335e-05, Bkappa=24.65;pos. col. U=233

iter110 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.386e-05, Bkappa=24.68;pos. col. U=232

iter111 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.434e-05, Bkappa=24.8;pos. col. U=232

iter112 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.488e-05, Bkappa=24.89;pos. col. U=232

iter113 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.54e-05, Bkappa=24.64;pos. col. U=232

iter114 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.596e-05, Bkappa=24.77;pos. col. U=233

iter115 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.644e-05, Bkappa=24.77;pos. col. U=233

iter116 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.693e-05, Bkappa=24.68;pos. col. U=233

iter117 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.736e-05, Bkappa=24.81;pos. col. U=234

iter118 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.769e-05, Bkappa=24.81;pos. col. U=234

iter119 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 2.79e-05, Bkappa=24.57;pos. col. U=234

New L3 is 0.00193045413622771

iter120 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 3.262e-05, Bkappa=24.84;pos. col. U=298

iter121 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 3.126e-05, Bkappa=24.83;pos. col. U=298

iter122 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 3.035e-05, Bkappa=24.74;pos. col. U=299

iter123 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 2.955e-05, Bkappa=24.77;pos. col. U=299

iter124 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 2.876e-05, Bkappa=24.67;pos. col. U=299

iter125 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 2.788e-05, Bkappa=24.67;pos. col. U=298

iter126 errorY= 0.7396, prior information ratio= 0.13, Bdiff= 2.695e-05, Bkappa=24.55;pos. col. U=298

iter127 errorY= 0.7396, prior information ratio= 0.13, Bdiff= 2.601e-05, Bkappa=24.55;pos. col. U=298

iter128 errorY= 0.7396, prior information ratio= 0.13, Bdiff= 2.513e-05, Bkappa=24.54;pos. col. U=298

iter129 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.436e-05, Bkappa=24.44;pos. col. U=298

iter130 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.37e-05, Bkappa=24.64;pos. col. U=298

iter131 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.316e-05, Bkappa=24.58;pos. col. U=299

iter132 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.272e-05, Bkappa=24.54;pos. col. U=299

iter133 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.238e-05, Bkappa=24.53;pos. col. U=299

iter134 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.206e-05, Bkappa=24.71;pos. col. U=298

iter135 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.182e-05, Bkappa=24.52;pos. col. U=298

iter136 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.165e-05, Bkappa=24.51;pos. col. U=298

iter137 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.15e-05, Bkappa=24.54;pos. col. U=298

iter138 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.138e-05, Bkappa=24.54;pos. col. U=297

iter139 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.125e-05, Bkappa=24.48;pos. col. U=297

New L3 is 0.00218749111818289

iter140 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.532e-05, Bkappa=24.52;pos. col. U=262

iter141 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.257e-05, Bkappa=24.49;pos. col. U=248

iter142 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.118e-05, Bkappa=24.81;pos. col. U=243

iter143 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.005e-05, Bkappa=24.71;pos. col. U=236

iter144 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.916e-05, Bkappa=24.68;pos. col. U=235

iter145 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.84e-05, Bkappa=24.49;pos. col. U=234

iter146 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.799e-05, Bkappa=24.46;pos. col. U=235

iter147 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.703e-05, Bkappa=24.46;pos. col. U=234

iter148 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.66e-05, Bkappa=24.25;pos. col. U=233

iter149 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.606e-05, Bkappa=24.2;pos. col. U=233

iter150 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.565e-05, Bkappa=24.17;pos. col. U=233

iter151 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.533e-05, Bkappa=24.16;pos. col. U=233

iter152 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.505e-05, Bkappa=24.16;pos. col. U=233

iter153 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.474e-05, Bkappa=24.16;pos. col. U=233

iter154 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.446e-05, Bkappa=24.16;pos. col. U=233

iter155 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.417e-05, Bkappa=24.2;pos. col. U=232

iter156 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.387e-05, Bkappa=24.2;pos. col. U=232

iter157 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.354e-05, Bkappa=24.21;pos. col. U=232

iter158 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.319e-05, Bkappa=24.22;pos. col. U=230

iter159 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.283e-05, Bkappa=24.24;pos. col. U=230

New L3 is 0.00193045413622771

iter160 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.672e-05, Bkappa=24.24;pos. col. U=300

iter161 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.486e-05, Bkappa=24.25;pos. col. U=299

iter162 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.373e-05, Bkappa=24.17;pos. col. U=296

iter163 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.289e-05, Bkappa=24.26;pos. col. U=296

iter164 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.22e-05, Bkappa=24.3;pos. col. U=296

iter165 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.167e-05, Bkappa=24.28;pos. col. U=295

iter166 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.124e-05, Bkappa=24.42;pos. col. U=295

iter167 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.087e-05, Bkappa=24.37;pos. col. U=296

iter168 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.058e-05, Bkappa=24.39;pos. col. U=297

iter169 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.034e-05, Bkappa=24.22;pos. col. U=297

iter170 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.016e-05, Bkappa=24.34;pos. col. U=297

iter171 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.002e-05, Bkappa=24.2;pos. col. U=297

iter172 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.929e-06, Bkappa=24.35;pos. col. U=298

iter173 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.889e-06, Bkappa=24.37;pos. col. U=298

iter174 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.905e-06, Bkappa=24.24;pos. col. U=298

iter175 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.977e-06, Bkappa=24.37;pos. col. U=298

iter176 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.011e-05, Bkappa=24.39;pos. col. U=298

iter177 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.029e-05, Bkappa=24.41;pos. col. U=298

iter178 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.051e-05, Bkappa=24.43;pos. col. U=298

iter179 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.078e-05, Bkappa=24.44;pos. col. U=298

New L3 is 0.00218749111818289

iter138 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.138e-05, Bkappa=24.54;pos. col. U=297

iter139 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 2.125e-05, Bkappa=24.48;pos. col. U=297

New L3 is 0.00218749111818289

iter140 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.532e-05, Bkappa=24.52;pos. col. U=262

iter141 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.257e-05, Bkappa=24.49;pos. col. U=248

iter142 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.118e-05, Bkappa=24.81;pos. col. U=243

iter143 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 2.005e-05, Bkappa=24.71;pos. col. U=236

iter144 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.916e-05, Bkappa=24.68;pos. col. U=235

iter145 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.84e-05, Bkappa=24.49;pos. col. U=234

iter146 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.799e-05, Bkappa=24.46;pos. col. U=235

iter147 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.703e-05, Bkappa=24.46;pos. col. U=234

iter148 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.66e-05, Bkappa=24.25;pos. col. U=233

iter149 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.606e-05, Bkappa=24.2;pos. col. U=233

iter150 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.565e-05, Bkappa=24.17;pos. col. U=233

iter151 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.533e-05, Bkappa=24.16;pos. col. U=233

iter152 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.505e-05, Bkappa=24.16;pos. col. U=233

iter153 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.474e-05, Bkappa=24.16;pos. col. U=233

iter154 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.446e-05, Bkappa=24.16;pos. col. U=233

iter155 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.417e-05, Bkappa=24.2;pos. col. U=232

iter156 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.387e-05, Bkappa=24.2;pos. col. U=232

iter157 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.354e-05, Bkappa=24.21;pos. col. U=232

iter158 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.319e-05, Bkappa=24.22;pos. col. U=230

iter159 errorY= 0.7398, prior information ratio= 0.12, Bdiff= 1.283e-05, Bkappa=24.24;pos. col. U=230

New L3 is 0.00193045413622771

iter160 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.672e-05, Bkappa=24.24;pos. col. U=300

iter161 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.486e-05, Bkappa=24.25;pos. col. U=299

iter162 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.373e-05, Bkappa=24.17;pos. col. U=296

iter163 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.289e-05, Bkappa=24.26;pos. col. U=296

iter164 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.22e-05, Bkappa=24.3;pos. col. U=296

iter165 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.167e-05, Bkappa=24.28;pos. col. U=295

iter166 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.124e-05, Bkappa=24.42;pos. col. U=295

iter167 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.087e-05, Bkappa=24.37;pos. col. U=296

iter168 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.058e-05, Bkappa=24.39;pos. col. U=297

iter169 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.034e-05, Bkappa=24.22;pos. col. U=297

iter170 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.016e-05, Bkappa=24.34;pos. col. U=297

iter171 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.002e-05, Bkappa=24.2;pos. col. U=297

iter172 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.929e-06, Bkappa=24.35;pos. col. U=298

iter173 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.889e-06, Bkappa=24.37;pos. col. U=298

iter174 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.905e-06, Bkappa=24.24;pos. col. U=298

iter175 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 9.977e-06, Bkappa=24.37;pos. col. U=298

iter176 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.011e-05, Bkappa=24.39;pos. col. U=298

iter177 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.029e-05, Bkappa=24.41;pos. col. U=298

iter178 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.051e-05, Bkappa=24.43;pos. col. U=298

iter179 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.078e-05, Bkappa=24.44;pos. col. U=298

New L3 is 0.00218749111818289

iter180 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.564e-05, Bkappa=24.51;pos. col. U=262

iter181 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.373e-05, Bkappa=24.56;pos. col. U=249

iter182 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.301e-05, Bkappa=24.45;pos. col. U=240

iter183 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.283e-05, Bkappa=24.41;pos. col. U=237

iter184 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.292e-05, Bkappa=24.41;pos. col. U=234

iter185 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.313e-05, Bkappa=24.4;pos. col. U=233

iter186 errorY= 0.7398, prior information ratio= 0.13, Bdiff= 1.342e-05, Bkappa=24.33;pos. col. U=232

iter187 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.372e-05, Bkappa=24.37;pos. col. U=232

iter188 errorY= 0.7397, prior information ratio= 0.13, Bdiff= 1.471e-05, Bkappa=24.33;pos. col. U=232

iter189 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.457e-05, Bkappa=24.43;pos. col. U=233

iter190 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.475e-05, Bkappa=24.37;pos. col. U=233

iter191 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 1.495e-05, Bkappa=24.45;pos. col. U=232

iter192 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.605e-05, Bkappa=24.45;pos. col. U=235

iter193 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.549e-05, Bkappa=24.38;pos. col. U=235

iter194 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.532e-05, Bkappa=24.43;pos. col. U=235

iter195 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.518e-05, Bkappa=24.43;pos. col. U=236

iter196 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.604e-05, Bkappa=24.4;pos. col. U=235

iter197 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.495e-05, Bkappa=24.29;pos. col. U=235

iter198 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.456e-05, Bkappa=24.83;pos. col. U=235

iter199 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 1.417e-05, Bkappa=24.84;pos. col. U=235
New L3 is 0.00193045413622771

iter200 errorY= 0.7396, prior information ratio= 0.1, Bdiff= 1.826e-05, Bkappa=24.84;pos. col. U=303

Bdiff is not decreasing

iter201 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.648e-05, Bkappa=24.85;pos. col. U=303

Bdiff is not decreasing

iter202 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.531e-05, Bkappa=24.91;pos. col. U=303

Bdiff is not decreasing

iter203 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.442e-05, Bkappa=24.92;pos. col. U=303

iter204 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.365e-05, Bkappa=25.1;pos. col. U=303

iter205 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.294e-05, Bkappa=25.12;pos. col. U=303

iter206 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.231e-05, Bkappa=25.13;pos. col. U=303

iter207 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.173e-05, Bkappa=25.15;pos. col. U=303

iter208 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.118e-05, Bkappa=25.14;pos. col. U=302

iter209 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.068e-05, Bkappa=25.15;pos. col. U=302

iter210 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.026e-05, Bkappa=25.16;pos. col. U=302

iter211 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 9.875e-06, Bkappa=25.19;pos. col. U=302

iter212 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 9.535e-06, Bkappa=24.95;pos. col. U=303

iter213 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 9.221e-06, Bkappa=24.96;pos. col. U=303

iter214 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 8.887e-06, Bkappa=24.97;pos. col. U=303

iter215 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 8.516e-06, Bkappa=24.98;pos. col. U=304

iter216 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 8.261e-06, Bkappa=24.99;pos. col. U=304

iter217 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 8.016e-06, Bkappa=25;pos. col. U=304

iter218 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 7.777e-06, Bkappa=25.2;pos. col. U=304

iter219 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 7.522e-06, Bkappa=25.16;pos. col. U=304

New L3 is 0.00218749111818289

ter220 errorY= 0.7396, prior information ratio= 0.12, Bdiff= 1.178e-05, Bkappa=25.1;pos. col. U=269

Bdiff is not decreasing

iter221 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 9.278e-06, Bkappa=25.12;pos. col. U=252

iter222 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 7.891e-06, Bkappa=25.15;pos. col. U=246

iter223 errorY= 0.7397, prior information ratio= 0.12, Bdiff= 6.933e-06, Bkappa=25.09;pos. col. U=242

iter224 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 6.187e-06, Bkappa=25.09;pos. col. U=241

iter225 errorY= 0.7397, prior information ratio= 0.11, Bdiff= 5.632e-06, Bkappa=24.57;pos. col. U=238

iter226 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 5.206e-06, Bkappa=24.58;pos. col. U=237

iter227 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.853e-06, Bkappa=24.59;pos. col. U=236

iter228 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.556e-06, Bkappa=24.59;pos. col. U=235

iter229 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.309e-06, Bkappa=24.6;pos. col. U=235

iter230 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.113e-06, Bkappa=24.62;pos. col. U=236

iter231 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 3.972e-06, Bkappa=24.8;pos. col. U=236

iter232 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 3.898e-06, Bkappa=24.77;pos. col. U=236

iter233 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 3.883e-06, Bkappa=24.8;pos. col. U=235

iter234 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 3.934e-06, Bkappa=24.81;pos. col. U=235

iter235 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.061e-06, Bkappa=24.81;pos. col. U=235

iter236 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.281e-06, Bkappa=24.81;pos. col. U=235

iter237 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 4.635e-06, Bkappa=24.82;pos. col. U=235

iter238 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 5.141e-06, Bkappa=24.83;pos. col. U=235

iter239 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 5.828e-06, Bkappa=24.85;pos. col. U=235

New L3 is 0.00218749111818289

iter240 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 6.75e-06, Bkappa=24.69;pos. col. U=235

iter241 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 7.93e-06, Bkappa=24.56;pos. col. U=235

iter242 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 9.379e-06, Bkappa=24.74;pos. col. U=235

iter243 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.105e-05, Bkappa=24.77;pos. col. U=235

iter244 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.28e-05, Bkappa=25.06;pos. col. U=235

iter245 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.445e-05, Bkappa=25.07;pos. col. U=235

iter246 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.571e-05, Bkappa=25.01;pos. col. U=235

iter247 errorY= 0.7396, prior information ratio= 0.11, Bdiff= 1.622e-05, Bkappa=25.03;pos. col. U=235

Bdiff is not decreasing

iter248 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 1.574e-05, Bkappa=25.15;pos. col. U=235

Bdiff is not decreasing

iter249 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 1.456e-05, Bkappa=25.23;pos. col. U=235

Bdiff is not decreasing

iter250 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 1.284e-05, Bkappa=25.34;pos. col. U=236

iter251 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 1.098e-05, Bkappa=25.35;pos. col. U=236

iter252 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 9.222e-06, Bkappa=25.08;pos. col. U=236

iter253 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 7.775e-06, Bkappa=25.08;pos. col. U=236

iter254 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 6.551e-06, Bkappa=25.09;pos. col. U=236

iter255 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 5.662e-06, Bkappa=25.1;pos. col. U=236

iter256 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 5.007e-06, Bkappa=25.11;pos. col. U=236

iter257 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 4.514e-06, Bkappa=25.11;pos. col. U=236

iter258 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 4.144e-06, Bkappa=25.12;pos. col. U=236

iter259 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.873e-06, Bkappa=25.13;pos. col. U=236

New L3 is 0.00218749111818289

iter260 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.667e-06, Bkappa=25.14;pos. col. U=235

iter261 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.534e-06, Bkappa=25.15;pos. col. U=235

iter262 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.434e-06, Bkappa=25.16;pos. col. U=235

iter263 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.35e-06, Bkappa=25.18;pos. col. U=235

iter264 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.276e-06, Bkappa=25.19;pos. col. U=235

iter265 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.226e-06, Bkappa=25.19;pos. col. U=235

iter266 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.189e-06, Bkappa=25.37;pos. col. U=235

iter267 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.158e-06, Bkappa=25.41;pos. col. U=235

iter268 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.131e-06, Bkappa=25.36;pos. col. U=235

iter269 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.11e-06, Bkappa=25.37;pos. col. U=235

iter270 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.088e-06, Bkappa=25.37;pos. col. U=235

iter271 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.067e-06, Bkappa=25.38;pos. col. U=235

iter272 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.053e-06, Bkappa=25.37;pos. col. U=235

iter273 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.049e-06, Bkappa=25.37;pos. col. U=235

iter274 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.052e-06, Bkappa=25.38;pos. col. U=235

iter275 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.058e-06, Bkappa=25.38;pos. col. U=235

iter276 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.053e-06, Bkappa=25.41;pos. col. U=235

iter277 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.053e-06, Bkappa=25.41;pos. col. U=235

iter278 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.06e-06, Bkappa=25.4;pos. col. U=235

iter279 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.071e-06, Bkappa=25.41;pos. col. U=236

New L3 is 0.00218749111818289

iter280 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.084e-06, Bkappa=25.41;pos. col. U=236

iter281 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.096e-06, Bkappa=25.43;pos. col. U=236

iter282 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.105e-06, Bkappa=25.44;pos. col. U=237

iter283 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.108e-06, Bkappa=25.44;pos. col. U=237

iter284 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.111e-06, Bkappa=25.45;pos. col. U=237

iter285 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.114e-06, Bkappa=25.45;pos. col. U=237

iter286 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.112e-06, Bkappa=25.7;pos. col. U=236

iter287 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.105e-06, Bkappa=25.71;pos. col. U=237

iter288 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.099e-06, Bkappa=25.71;pos. col. U=237

iter289 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.085e-06, Bkappa=25.62;pos. col. U=237

iter290 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.069e-06, Bkappa=25.72;pos. col. U=237

iter291 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.047e-06, Bkappa=25.72;pos. col. U=237

iter292 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.023e-06, Bkappa=25.32;pos. col. U=237

iter293 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.998e-06, Bkappa=25.64;pos. col. U=237

iter294 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.972e-06, Bkappa=25.64;pos. col. U=237

iter295 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.947e-06, Bkappa=25.65;pos. col. U=237
iter296 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.919e-06, Bkappa=25.66;pos. col. U=237

iter297 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.895e-06, Bkappa=25.67;pos. col. U=237

iter298 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.873e-06, Bkappa=25.68;pos. col. U=238

iter299 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.859e-06, Bkappa=25.68;pos. col. U=238

New L3 is 0.00218749111818289

iter300 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.855e-06, Bkappa=25.69;pos. col. U=238

iter301 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.86e-06, Bkappa=25.73;pos. col. U=238

iter302 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.872e-06, Bkappa=25.74;pos. col. U=239

iter303 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.887e-06, Bkappa=25.74;pos. col. U=239

iter304 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.912e-06, Bkappa=25.72;pos. col. U=239

iter305 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.942e-06, Bkappa=25.54;pos. col. U=239

iter306 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 2.977e-06, Bkappa=25.54;pos. col. U=239

iter307 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.021e-06, Bkappa=25.55;pos. col. U=239

iter308 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.068e-06, Bkappa=25.56;pos. col. U=239

iter309 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.124e-06, Bkappa=25.56;pos. col. U=239

iter310 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.195e-06, Bkappa=25.57;pos. col. U=239

iter311 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.282e-06, Bkappa=25.57;pos. col. U=240

iter312 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.379e-06, Bkappa=25.57;pos. col. U=240

iter313 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.494e-06, Bkappa=25.58;pos. col. U=240

Bdiff is not decreasing

iter314 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.627e-06, Bkappa=25.58;pos. col. U=240

Bdiff is not decreasing

iter315 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.781e-06, Bkappa=25.58;pos. col. U=241

Bdiff is not decreasing

iter316 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 3.968e-06, Bkappa=25.58;pos. col. U=241

Bdiff is not decreasing

iter317 errorY= 0.7395, prior information ratio= 0.11, Bdiff= 4.18e-06, Bkappa=25.79;pos. col. U=241

Bdiff is not decreasing

converged at  iteration 317 Bdiff is not decreasing

There are 114  LVs with AUC>0.70

2022-08-04T20:12:25.030070Z [rsession-jfisher7] WARNING Abort requested; LOGGED FROM: bool 
rstudio::session::connection::checkForAbort(rstudio_boost::shared_ptr<rstudio::session::HttpConnection>, 

### Save Data
Done in analysis 

    
# END
    Location of final scripts:
    ./scripts
    
    Location of data produced:
    ./data/recount3
    
    Dates when operations were done:
    220725
    
## Versions
```{r}
sessionInfo()
```
